### 2007-04-26 article/Article.tex
begin the article
darcs-hash:20070426143757-2fc9d-8194597a17d6ca0ed27e1e25fa5c4a6bcb2f7dcc.gz

%
% Complete documentation on the extended LaTeX markup used for Insight
% documentation is available in ``Documenting Insight'', which is part
% of the standard documentation for Insight.  It may be found online
% at:
%
%     http://www.itk.org/

\documentclass{InsightArticle}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  hyperref should be the last package to be loaded.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[dvips,
bookmarks,
bookmarksopen,
backref,
colorlinks,linkcolor={blue},citecolor={blue},urlcolor={blue},
]{hyperref}
% to be able to use options in graphics
\usepackage{graphicx}
% for pseudo code
\usepackage{listings}
% subfigures
\usepackage{subfigure}

%  This is a template for Papers to the Insight Journal. 
%  It is comparable to a technical report format.

% The title should be descriptive enough for people to be able to find
% the relevant document. 
\title{Labeled object representation and manipulation with ITK}

% Increment the release number whenever significant changes are made.
% The author and/or editor can define 'significant' however they like.
%\release{0.00}

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Ga\"etan Lehmann{$^2$}}
\authoraddress{{$^1$}INRA, UMR 1198; ENVA; CNRS, FRE 2857, Biologie du D\'eveloppement et 
Reproduction, Jouy en Josas, F-78350, France.}

\begin{document}
\maketitle

\ifhtml
\chapter*{Front Matter\label{front}}
\fi

\begin{abstract}
\noindent
Labelizing the objects in an image is a very common task in image analysis. It can be done manually,
after a binarization, or can be produced directly by some algorithms, like the watershed transform.
Manipulating those objects can be very useful, to get some informations about them for example, or
to remove some of them according to those informations.
This article describes some new classes made to represent and manipulate the labeled objects within
ITK.
\end{abstract}

\tableofcontents

\section{Introduction}

\section{Existing naming conventions for binary images and label images}

\section{Data representation}

\section{Data generation and object information computation}

\section{Using new object information}

\section{Future work}

\section{Conclusion}

% \url{http://www.itk.org}
% \code{Insight/Documentation/Style.pdf}
% \section{Principles of Solar Spot Detection}
% \cite{ITKSoftwareGuide}.
% \doxygen{ImageToImageFilter}

% \small \begin{verbatim}
% \end{verbatim} \normalsize

% The {itemize} environment uses a bullet for each \item.  If you want the 
% \item's numbered, use the {enumerate} environment instead.
% \begin{itemize}
%   \item  Insight Toolkit 2.4.
%   \item  CMake 2.2
% \end{itemize}

% \ref{cthead1}

\begin{figure}[htbp]
\centering
\includegraphics{cthead1}
\caption{The input image.\label{cthead1}}
\end{figure}

\appendix

\bibliographystyle{plain}
\bibliography{InsightJournal}
\nocite{ITKSoftwareGuide}

\end{document}

### 2007-04-27 article/Article.tex
article continued
darcs-hash:20070427102646-2fc9d-1529996bd6338f6e66f27e31a99b678a42e8d054.gz

@@
 \noindent
-Labelizing the objects in an image is a very common task in image analysis. It can be done manually,
-after a binarization, or can be produced directly by some algorithms, like the watershed transform.
-Manipulating those objects can be very useful, to get some informations about them for example, or
-to remove some of them according to those informations.
-This article describes some new classes made to represent and manipulate the labeled objects within
-ITK.
+
+Richard Beare has recently introduced a new filter to efficiently labelize the connected component with ITK, and has also proposed to use the run-length encoding used in that filter to implement some of the most useful binary mathematical morphology operators: the opening by attribute.
+Following that idea, and after have searched a way to use the ITK's spatial objects for this task, a new set of classes have been developed to represent and manipulate the labeled images and the objects within them in ITK.
+Those new classes have been used to implement several labeled images manipulation based on object attributes, as well as the binary specialization of some mathematical morphology filter already include in ITK, and not related to the attribute of the objects.
+
+All the source codes are provided, as well as a full set of test and several usage example of the new classes.
+
 \end{abstract}
@@
 
-\section{Existing naming conventions for binary images and label images}
+Identifying the objects in an image is a very common task, often realized by producing an image of the same size with a single pixel value per object.
+This image is called a labeled image.
+There are several way to create this image.
+It can be done by searching the connected components in a binary image, it can be produced directly by some algorithms, like the watershed transform, it can even be simply done by hand, etc.
+
+\section{Definitions}
+
+In that article, some terms will be cited very frequently. I will try to define them, in the context of the image analysis.
+
+\subsection{Label}
+
+A label is an identifier of something with the same caracteristics in the image.
+Those caracteristics can be whatever you want, for example, the range of pixel values, the same object in sense of connected component, etc.
+A label can be represented by anything and only need to be unique in the image.
+It doesn't even require to be ordered.
+In practice, we choose to use the integral number types, for several reasons: they are commonly used in image analysis, they efficiently reprensent the label in memory, and its easy to find the next label by adding 1.
+
+\subsection{Labeled image}
+
+A label image is an image which contains several labeled pixels.
+Often, the labels are representing some objects placed on a background, and so the label image may use a particular label for the background.
+
+\subsection{Binary image}
+
+A binary image is an image with two labels: a foreground label and a background label.
+In practice, the binary images are using a pixel type able to store more than those two values.
+The foreground is thus defined with a particular label, and the other label in the image are considered as the background.
+A side effect of that is that a labeled image can be considered as a binary image, and so, it let us manipulate a single object in a labeled image.
+
+\subsection{Attribute}
+
+An attribute is a value of any type associated with a label. It can be for example the size of an object, the mean of its pixels intensities, etc.
+
+\section{Existing classes and naming convention in ITK}
+
+In ITK, the labeled and the binary images are implemented as a simple {\em itk::Image}. The pixel types used are most of the time integral, signed or unsigned, but may be of other types.
+Several definitions of a binary image or used in ITK. Depending of the class which implement it, a binary image can be:
+\begin{itemize}
+  \item All the pixels with a given value are in the foreground. The others are in the background. That's the definition proposed in that article.
+  \item All the pixels with a given value are in the background. The others are in the foreground.
+  \item All the pixels greater than the mean of the maximum value in the image and the minimum value in the image are in the image are in the foreground. The other are in the background.
+\end{itemize}
+All those definitions should be uniformised. In that article (and all the others from the same author), the first one is the only one used.
+
+The filter which are mainpulating binary images are often prefixed with the word "Binary", to differenciate the grayscale version which don't have a prefix.
+It seem to be a quite good practice which have been kept in that article.
+
+The filter dedicated to the manipulation of labeled images have the word "Label" somewhere in there name. Again, it seem to be a good practice which have been kept in that article.
 
 \section{Data representation}
+
+A labeled image is can be seen as two things:
+\begin{itemize}
+  \item  an image
+  \item  a set of objects.
+\end{itemize}
+
+The new classes provided in that contribution fit those two point of view.
+
+\subsection{LabelCollectionImage}
+
+The {\em itk::LabelCollectionImage} is in charge of managing the collection of labeled
+objects of the image, as well as storing the metadata associated with the image like
+the spacing, the physical position, etc.
+
+The labeled objects are referenced in a {\em std::map} object to ensure that only one
+
+The {\em itk::LabelCollectionImage} provide most of the API of the {\em itk::Image} class,
+like the spacing support, the physical position, etc, and so can be manipulated as an
+image\footnote{It doesn't support the itk::Image iterators though}.
+
+\subsection{LabelObject and its specializations}
+
+\subsection{LabelObjectLine}
 
@@
 \section{Using new object information}
+
+\section{Binary specialization of mathematical morphology filters}
 

### 2007-04-27 article/Article.tex
more of the article
darcs-hash:20070427131457-2fc9d-59c791c7f94305f44b947e5e74b101e91b6683f5.gz

@@
   \item All the pixels with a given value are in the background. The others are in the foreground.
-  \item All the pixels greater than the mean of the maximum value in the image and the minimum value in the image are in the image are in the foreground. The other are in the background.
+  \item All the pixels greater than the mean of the maximum value in the image and the minimum value in the image are in the foreground. The other are in the background.
 \end{itemize}
-All those definitions should be uniformised. In that article (and all the others from the same author), the first one is the only one used.
+All those definitions should be uniformized to enhance user experience with ITK. In that article (and all the others from the same author), the first one is the only one used.
 
@@
 
-A labeled image is can be seen as two things:
-\begin{itemize}
-  \item  an image
-  \item  a set of objects.
-\end{itemize}
+The labeled images are often used the represent the connected components of an image.
+As connected component, they can be efficiently store in memory as a set of lines, using the run-length encoding: a starting point for each line, and the length of the line on a given dimension (by convention, the dimension 0).
+The image the can be seen as a collection of objects.
 
-The new classes provided in that contribution fit those two point of view.
+\subsection{itk::LabelCollectionImage}
 
-\subsection{LabelCollectionImage}
-
-The {\em itk::LabelCollectionImage} is in charge of managing the collection of labeled
+The {\em itk::LabelCollectionImage} class is in charge of managing the collection of labeled
 objects of the image, as well as storing the metadata associated with the image like
@@
 
-The labeled objects are referenced in a {\em std::map} object to ensure that only one
+The {\em itk::LabelCollectionImage} provide a part of the API of the {\em itk::Image} class,
+and so can be manipulated as an image\footnote{It doesn't support the itk::Image iterators though}
+in may cases. The performance can be very different however.
 
-The {\em itk::LabelCollectionImage} provide most of the API of the {\em itk::Image} class,
-like the spacing support, the physical position, etc, and so can be manipulated as an
-image\footnote{It doesn't support the itk::Image iterators though}.
+\subsection{itk::LabelObject and its specializations}
 
-\subsection{LabelObject and its specializations}
+The {\em itk::LabelObject} class represent the label obejcts. It has two main features:
+\begin{itemize}
+  \item It manage the set pixels which compose the object. The pixels are stored using the run-length encoding.
+  \item It has a label.
+\end{itemize}
 
-\subsection{LabelObjectLine}
+No attribute are stored in this class, which can thus be see as the base class for the abjects with some attributes, or which can be used when no attributes are required.
 
-\section{Data generation and object information computation}
+Several subclasses are provided with that article:
+\begin{itemize}
+  \item {\em itk::AttributeLabelObject} is able to store a generic attribute. It is generic in the sense that its type is given in template parameter.
+  \item {\em itk::ShapeLabelObject} contains numerous attribute related to the shape of the labeled object.
+  \item {\em itk::StatisticsLabelObject} contains numerous statistics about the grey values of a feature image in the same place than the labeled object.
+\end{itemize}
 
-\section{Using new object information}
+\subsection{itk::LabelObjectLine}
+
+{\em itk::LabelObjectLine} is the object used to store the position and the size of a single line.
+
+\section{General view of the usage}
+
+\subsection{Generating the itk::LabelCollectionImage}
+
+The {\em itk::LabelCollectionImage} class provide some methods to fill the image.
+However, the most efficient way is to convert a labeled image or a binary image stored in an {\em itk::Image} to a {\em itk::LabelCollectionImage}, by using {\em itk::BinaryImageToLabelCollectionImageFilter} or {\em itk::LabelImageToLabelCollectionImageFilter}.
+
+\subsection{Valuating the attributes}
+
+The label objects produced by those filters have no attribute value set, and thus the attributes must be valuated.
+Some filters are provided for the most common used one: {\em itk::ShapeLabelCollectionImageFilter} to fill the attributes of the {\em itk::ShapeLabelObject}s, and {\em itk::ShapeLabelCollectionImageFilter} to fill the attributes of the {\em itk::StatisticsLabelObject}s.
+For the {\em itk::AttributeLabelObject} class or other classes, the user must set the value by himself, for example by implementing a subclass of {\em itk::InPlaceLabelCollectionImageFilter}.
+
+\subsection{Manipulating the itk::LabelCollectionImage}
+
+Once created and, optionally, valued, several filters are provided to manipulate the {\em itk::LabelCollectionImage}:
+
+\begin{itemize}
+  \item An opening can be performed with the {\em OpeningLabelCollectionImageFilter} classes.
+Those classes will remove all the objects with an attribute value lower or greater than a given value.
+It's a very convenient way to enhance a segmentation for example, because we often can use that way some criteria  which have not been used during the segmentation procedure, like the size of the object, the mean value of its pixels, etc.
+  \item A fixed number of objects can be kept, with the {\em KeepNObjectsLabelCollectionImageFilter} classes.
+They are chosen according to the value of their attribute.
+The user can choose to keep the ones with the highest, or with the lowest attribute values.
+  \item The objects can be relabel, with the {\em RelabelLabelCollectionImageFilter} classes.
+The order of the label is dependant of the value of the attribute.
+Again, the user can choose to have the objects with the highest attribute value in the first labels, or to have the objects with the lowest attribute values in the first labels.
+\end{itemize}
+
+It can also be useful to simply get the attribute values associated with the objects.
+In that case, the classes provided in with that article can be used in place of {\em itk::LabelStatisticsImageFilter}, or to get some data about the shape or the position of the object.
+
+\subsection{Generating an itk::Image from the itk::LabelCollectionImage}
+
+\section{Prebuilt mini-pipeline filters}
+
+\subsection{Binary filters}
+
+\subsection{Label filters}
 
 \section{Binary specialization of mathematical morphology filters}
+
+\section{Usage examples}
+
+\subsection{...}
 

### 2007-04-27 article/Article.tex
more and more of the article
darcs-hash:20070427140655-2fc9d-c12abd5e7f427a2f5afdd2e11cdab5dd38fc8b3f.gz

@@
 \author{Ga\"etan Lehmann{$^2$}}
-\authoraddress{{$^1$}INRA, UMR 1198; ENVA; CNRS, FRE 2857, Biologie du D\'eveloppement et 
+\authoraddress{{$^1$}INRA, UMR 1198; ENVA; CNRS, FRE 2857, Biologie du
+D\'eveloppement et 
 Reproduction, Jouy en Josas, F-78350, France.}
@@
 
-Richard Beare has recently introduced a new filter to efficiently labelize the connected component with ITK, and has also proposed to use the run-length encoding used in that filter to implement some of the most useful binary mathematical morphology operators: the opening by attribute.
-Following that idea, and after have searched a way to use the ITK's spatial objects for this task, a new set of classes have been developed to represent and manipulate the labeled images and the objects within them in ITK.
-Those new classes have been used to implement several labeled images manipulation based on object attributes, as well as the binary specialization of some mathematical morphology filter already include in ITK, and not related to the attribute of the objects.
+Richard Beare has recently introduced a new filter to efficiently labelize the
+connected component with ITK, and has also proposed to use the run-length
+encoding used in that filter to implement some of the most useful binary
+mathematical morphology operators: the opening by attribute.
+Following that idea, and after have searched a way to use the ITK's spatial
+objects for this task, a new set of classes have been developed to represent and
+manipulate the labeled images and the objects within them in ITK.
+Those new classes have been used to implement several labeled images
+manipulation based on object attributes, as well as the binary specialization of
+some mathematical morphology filter already include in ITK, and not related to
+the attribute of the objects. With those last filters, this contribution comes
+with 49 new classes, and should greatly enhance the binary mathematical
+morphology in ITK.
 
-All the source codes are provided, as well as a full set of test and several usage example of the new classes.
+All the source codes are provided, as well as a full set of test and several
+usage examples of the new classes.
 
@@
 
-Identifying the objects in an image is a very common task, often realized by producing an image of the same size with a single pixel value per object.
-This image is called a labeled image.
-There are several way to create this image.
-It can be done by searching the connected components in a binary image, it can be produced directly by some algorithms, like the watershed transform, it can even be simply done by hand, etc.
+Identifying the objects in an image is a very common task, often realized by
+producing an image of the same size with a single pixel value per object. This
+image is called a labeled image. There are several way to create this image. It
+can be done by searching the connected components in a binary image, it can be
+produced directly by some algorithms, like the watershed transform, it can even
+be simply done by hand, etc.
 
@@
 
-In that article, some terms will be cited very frequently. I will try to define them, in the context of the image analysis.
+In that article, some terms will be cited very frequently. I will try to define
+them, in the context of the image analysis.
 
@@
 A label is an identifier of something with the same caracteristics in the image.
-Those caracteristics can be whatever you want, for example, the range of pixel values, the same object in sense of connected component, etc.
+Those caracteristics can be whatever you want, for example, the range of pixel
+values, the same object in sense of connected component, etc.
 A label can be represented by anything and only need to be unique in the image.
-It doesn't even require to be ordered.
-In practice, we choose to use the integral number types, for several reasons: they are commonly used in image analysis, they efficiently reprensent the label in memory, and its easy to find the next label by adding 1.
+It doesn't even require to be ordered. In practice, we choose to use the
+integral number types, for several reasons: they are commonly used in image
+analysis, they efficiently reprensent the label in memory, and its easy to find
+the next label by adding 1.
 
@@
 
-A label image is an image which contains several labeled pixels.
-Often, the labels are representing some objects placed on a background, and so the label image may use a particular label for the background.
+A label image is an image which contains several labeled pixels. Often, the
+labels are representing some objects placed on a background, and so the label
+image may use a particular label for the background.
 
@@
 
-A binary image is an image with two labels: a foreground label and a background label.
-In practice, the binary images are using a pixel type able to store more than those two values.
-The foreground is thus defined with a particular label, and the other label in the image are considered as the background.
-A side effect of that is that a labeled image can be considered as a binary image, and so, it let us manipulate a single object in a labeled image.
+A binary image is an image with two labels: a foreground label and a background
+label. In practice, the binary images are using a pixel type able to store more
+than those two values. The foreground is thus defined with a particular label,
+and the other label in the image are considered as the background. A side effect
+of that is that a labeled image can be considered as a binary image, and so, it
+let us manipulate a single object in a labeled image.
 
@@
 
-An attribute is a value of any type associated with a label. It can be for example the size of an object, the mean of its pixels intensities, etc.
+An attribute is a value of any type associated with a label. It can be for
+example the size of an object, the mean of its pixels intensities, etc.
 
@@
 
-In ITK, the labeled and the binary images are implemented as a simple {\em itk::Image}. The pixel types used are most of the time integral, signed or unsigned, but may be of other types.
-Several definitions of a binary image or used in ITK. Depending of the class which implement it, a binary image can be:
+In ITK, the labeled and the binary images are implemented as a simple {\em
+itk::Image}. The pixel types used are most of the time integral, signed or
+unsigned, but may be of other types.
+Several definitions of a binary image or used in ITK. Depending of the class
+which implement it, a binary image can be:
 \begin{itemize}
-  \item All the pixels with a given value are in the foreground. The others are in the background. That's the definition proposed in that article.
-  \item All the pixels with a given value are in the background. The others are in the foreground.
-  \item All the pixels greater than the mean of the maximum value in the image and the minimum value in the image are in the foreground. The other are in the background.
+  \item All the pixels with a given value are in the foreground. The others are
+in the background. That's the definition proposed in that article.
+  \item All the pixels with a given value are in the background. The others are
+in the foreground.
+  \item All the pixels greater than the mean of the maximum value in the image
+and the minimum value in the image are in the foreground. The other are in the
+background.
 \end{itemize}
-All those definitions should be uniformized to enhance user experience with ITK. In that article (and all the others from the same author), the first one is the only one used.
+All those definitions should be uniformized to enhance user experience with ITK.
+In that article (and all the others from the same author), the first one is the
+only one used.
 
-The filter which are mainpulating binary images are often prefixed with the word "Binary", to differenciate the grayscale version which don't have a prefix.
-It seem to be a quite good practice which have been kept in that article.
+The filter which are mainpulating binary images are often prefixed with the word
+"Binary", to differenciate the grayscale version which don't have a prefix. It
+seem to be a quite good practice which have been kept in that article.
 
-The filter dedicated to the manipulation of labeled images have the word "Label" somewhere in there name. Again, it seem to be a good practice which have been kept in that article.
+The filter dedicated to the manipulation of labeled images have the word "Label"
+somewhere in there name. Again, it seem to be a good practice which have been
+kept in that article.
 
@@
 
-The labeled images are often used the represent the connected components of an image.
-As connected component, they can be efficiently store in memory as a set of lines, using the run-length encoding: a starting point for each line, and the length of the line on a given dimension (by convention, the dimension 0).
-The image the can be seen as a collection of objects.
+The labeled images are often used the represent the connected components of an
+image. As connected component, they can be efficiently store in memory as a set
+of lines, using the run-length encoding: a starting point for each line, and the
+length of the line on a given dimension (by convention, the dimension 0). The
+image the can be seen as a collection of objects.
 
@@
 
-The {\em itk::LabelCollectionImage} class is in charge of managing the collection of labeled
-objects of the image, as well as storing the metadata associated with the image like
+The {\em itk::LabelCollectionImage} class is in charge of managing the
+collection of labeled
+objects of the image, as well as storing the metadata associated with the image
+like
 the spacing, the physical position, etc.
 
-The {\em itk::LabelCollectionImage} provide a part of the API of the {\em itk::Image} class,
-and so can be manipulated as an image\footnote{It doesn't support the itk::Image iterators though}
+The {\em itk::LabelCollectionImage} provide a part of the API of the {\em
+itk::Image} class,
+and so can be manipulated as an image\footnote{It doesn't support the itk::Image
+iterators though}
 in may cases. The performance can be very different however.
@@
 
-The {\em itk::LabelObject} class represent the label obejcts. It has two main features:
+The {\em itk::LabelObject} class represent the label obejcts. It has two main
+features:
 \begin{itemize}
-  \item It manage the set pixels which compose the object. The pixels are stored using the run-length encoding.
+  \item It manage the set pixels which compose the object. The pixels are stored
+using the run-length encoding.
   \item It has a label.
@@
 
-No attribute are stored in this class, which can thus be see as the base class for the abjects with some attributes, or which can be used when no attributes are required.
+No attribute are stored in this class, which can thus be see as the base class
+for the abjects with some attributes, or which can be used when no attributes
+are required.
 
@@
 \begin{itemize}
-  \item {\em itk::AttributeLabelObject} is able to store a generic attribute. It is generic in the sense that its type is given in template parameter.
-  \item {\em itk::ShapeLabelObject} contains numerous attribute related to the shape of the labeled object.
-  \item {\em itk::StatisticsLabelObject} contains numerous statistics about the grey values of a feature image in the same place than the labeled object.
+  \item {\em itk::AttributeLabelObject} is able to store a generic attribute. It
+is generic in the sense that its type is given in template parameter.
+  \item {\em itk::ShapeLabelObject} contains numerous attribute related to the
+shape of the labeled object.
+  \item {\em itk::StatisticsLabelObject} contains numerous statistics about the
+grey values of a feature image in the same place than the labeled object.
 \end{itemize}
@@
 
-{\em itk::LabelObjectLine} is the object used to store the position and the size of a single line.
+{\em itk::LabelObjectLine} is the object used to store the position and the size
+of a single line.
 
@@
 
-The {\em itk::LabelCollectionImage} class provide some methods to fill the image.
-However, the most efficient way is to convert a labeled image or a binary image stored in an {\em itk::Image} to a {\em itk::LabelCollectionImage}, by using {\em itk::BinaryImageToLabelCollectionImageFilter} or {\em itk::LabelImageToLabelCollectionImageFilter}.
+The {\em itk::LabelCollectionImage} class provide some methods to fill the
+image. However, the most efficient way is to convert a labeled image or a binary
+image stored in an {\em itk::Image} to a {\em itk::LabelCollectionImage}, by
+using {\em itk::BinaryImageToLabelCollectionImageFilter} or {\em
+itk::LabelImageToLabelCollectionImageFilter}.
 
@@
 
-The label objects produced by those filters have no attribute value set, and thus the attributes must be valuated.
-Some filters are provided for the most common used one: {\em itk::ShapeLabelCollectionImageFilter} to fill the attributes of the {\em itk::ShapeLabelObject}s, and {\em itk::ShapeLabelCollectionImageFilter} to fill the attributes of the {\em itk::StatisticsLabelObject}s.
-For the {\em itk::AttributeLabelObject} class or other classes, the user must set the value by himself, for example by implementing a subclass of {\em itk::InPlaceLabelCollectionImageFilter}.
+The label objects produced by those filters have no attribute value set, and
+thus the attributes must be valuated. Some filters are provided for the most
+common used one: {\em itk::ShapeLabelCollectionImageFilter} to fill the
+attributes of the {\em itk::ShapeLabelObject}s, and {\em
+itk::ShapeLabelCollectionImageFilter} to fill the attributes of the {\em
+itk::StatisticsLabelObject}s. For the {\em itk::AttributeLabelObject} class or
+other classes, the user must set the value by himself, for example by
+implementing a subclass of {\em itk::InPlaceLabelCollectionImageFilter}.
 
@@
 
-Once created and, optionally, valued, several filters are provided to manipulate the {\em itk::LabelCollectionImage}:
+Once created and, optionally, valued, several filters are provided to manipulate
+the {\em itk::LabelCollectionImage}:
 
 \begin{itemize}
-  \item An opening can be performed with the {\em OpeningLabelCollectionImageFilter} classes.
-Those classes will remove all the objects with an attribute value lower or greater than a given value.
-It's a very convenient way to enhance a segmentation for example, because we often can use that way some criteria  which have not been used during the segmentation procedure, like the size of the object, the mean value of its pixels, etc.
-  \item A fixed number of objects can be kept, with the {\em KeepNObjectsLabelCollectionImageFilter} classes.
-They are chosen according to the value of their attribute.
-The user can choose to keep the ones with the highest, or with the lowest attribute values.
-  \item The objects can be relabel, with the {\em RelabelLabelCollectionImageFilter} classes.
-The order of the label is dependant of the value of the attribute.
-Again, the user can choose to have the objects with the highest attribute value in the first labels, or to have the objects with the lowest attribute values in the first labels.
+  \item An opening can be performed with the {\em
+OpeningLabelCollectionImageFilter} classes. Those classes will remove all the
+objects with an attribute value lower or greater than a given value. It's a very
+convenient way to enhance a segmentation for example, because we often can use
+that way some criteria  which have not been used during the segmentation
+procedure, like the size of the object, the mean value of its pixels, etc.
+  \item A fixed number of objects can be kept, with the {\em
+KeepNObjectsLabelCollectionImageFilter} classes. They are chosen according to
+the value of their attribute. The user can choose to keep the ones with the
+highest, or with the lowest attribute values.
+  \item The objects can be relabel, with the {\em
+RelabelLabelCollectionImageFilter} classes. The order of the label is dependant
+of the value of the attribute. Again, the user can choose to have the objects
+with the highest attribute value in the first labels, or to have the objects
+with the lowest attribute values in the first labels.
 \end{itemize}
 
-It can also be useful to simply get the attribute values associated with the objects.
-In that case, the classes provided in with that article can be used in place of {\em itk::LabelStatisticsImageFilter}, or to get some data about the shape or the position of the object.
+It can also be useful to simply get the attribute values associated with the
+objects. In that case, the classes provided in with that article can be used in
+place of {\em itk::LabelStatisticsImageFilter}, or to get some data about the
+shape or the position of the object.
 
@@
 
+Once the manipulation of the objects is done, it can be useful to go back to a
+more classic {\em itk::Image}. Several classes are provided to do that:
+\begin{itemize}
+  \item The {\em itk::LabelCollectionImageToLabelImageFilter} class simply
+convert a {\em itk::LabelCollectionImage} to a labeled image stored in a {\em
+itk::Image}.
+  \item The {\em itk::LabelCollectionImageToBinaryImageFilter} put all the
+objects in the foreground of a binary image stored in a {itk::Image}. It is
+intended to be used with an image produced by the {\em
+itk::BinaryImageToLabelCollectionImageFilter}. The background values of the
+original image can also be restored by this filter.
+  \item The {\em itk::LabelCollectionImageToMaskImageFilter} class can be used
+to mask an image with the objects of the {\em itk::LabelCollectionImage}.
+  \item Finally, {\em itk::LabelCollectionImageToAttributeImageFilter} produce
+an {\em itk::Image} with the value of the attribute of the objects of the {\em
+itk::LabelCollectionImage}. This filter is mostly useful to have a global view
+of the attribute values in the image.
+\end{itemize}
+
+\section{Available attributes}
+
+\subsection{Shape}
+
+\begin{itemize}
+  \item {\em Size}
+  \item {\em PhysicalSize}
+  \item {\em Centroid}
+  \item {\em Region}
+  \item {\em RegionElongation}
+  \item {\em SizeRegionRatio}
+  \item {\em SizeOnBorder}
+  \item {\em FeretDiameter}
+%   \item {\em Perimeter}
+\end{itemize}
+
+\subsection{Statistics}
+
+\begin{itemize}
+  \item {\em Minimum}
+  \item {\em Maximum}
+  \item {\em Mean}
+  \item {\em Sum}
+  \item {\em Sigma}
+  \item {\em Variance}
+  \item {\em Median}
+  \item {\em MaximumIndex}
+  \item {\em MinimumIndex}
+  \item {\em CenterOfGravity}
+%   \item {\em CentralMoments}
+%   \item {\em PrincipalMoments}
+%   \item {\em PrincipalAxes}
+  \item {\em Kurtosis}
+  \item {\em Skewness}
+\end{itemize}
+
 \section{Prebuilt mini-pipeline filters}
+
+The general view of the previous section show a very common way to use those
+classes. To make easier to use, some prebuilt classes have been made, to perform
+the mini-pipeline:
+\begin{itemize}
+  \item creation of the {\em itk::LabelCollectionImage} from an {\em
+itk::Image},
+  \item filtering of the {\em itk::LabelCollectionImage},
+  \item creation of an {\em itk::Image} from the filtered {\em
+itk::LabelCollectionImage},
+\end{itemize}
+with a specific attribute.
+
+Those filters have been made for binary, and labeled images.
 
@@
 
+\begin{itemize}
+  \item {\em itk::BinaryAttributeKeepNObjectsImageFilter}
+  \item {\em itk::BinaryAttributeOpeningImageFilter}
+  \item {\em itk::BinaryShapeKeepNObjectsImageFilter}
+  \item {\em itk::BinaryShapeOpeningImageFilter}
+  \item {\em itk::BinaryStatisticsKeepNObjectsImageFilter}
+  \item {\em itk::BinaryStatisticsOpeningImageFilter}
+\end{itemize}
+
 \subsection{Label filters}
 
+\begin{itemize}
+  \item {\em itk::LabelAttributeKeepNObjectsImageFilter}
+  \item {\em itk::LabelAttributeOpeningImageFilter}
+  \item {\em itk::LabelShapeKeepNObjectsImageFilter}
+  \item {\em itk::LabelShapeOpeningImageFilter}
+  \item {\em itk::LabelStatisticsKeepNObjectsImageFilter}
+  \item {\em itk::LabelStatisticsOpeningImageFilter}
+  \item {\em itk::ShapeRelabelImageFilter}
+  \item {\em itk::StatisticsRelabelImageFilter}
+\end{itemize}
+
 \section{Binary specialization of mathematical morphology filters}
+
+\begin{itemize}
+  \item {\em itk::BinaryClosingByReconstructionImageFilter}
+  \item {\em itk::BinaryFillholeImageFilter}
+  \item {\em itk::BinaryGrindPeakImageFilter}
+  \item {\em itk::BinaryOpeningByReconstructionImageFilter}
+  \item {\em itk::BinaryReconstructionByDilationImageFilter}
+  \item {\em itk::BinaryReconstructionByErosionImageFilter}
+\end{itemize}
 
@@
 \subsection{...}
+
+\section{Wrappers support}
+
+All the classes provided with that article, excepted the most generic ones made
+to help the developer to implement some new features, can be used with WrapITK,
+and have been fully tested with python.
 

### 2007-05-03 article/Article.tex
article continued
darcs-hash:20070503091807-2fc9d-a2aa97bed59431f692e226d3a7610999dc0f707c.gz

@@
   \item {\em itk::ShapeLabelObject} contains numerous attribute related to the
-shape of the labeled object.
+shape of the labeled object. Computing the values of those attributes does not
+require a feaure image.
   \item {\em itk::StatisticsLabelObject} contains numerous statistics about the
 grey values of a feature image in the same place than the labeled object.
+Computing the values of those attributes does require a feature image.
+\end{itemize}
+
+The scalar values of the attributes of the {\em itk::ShapeLabelObject} and the
+{\em itk::StatisticsLabelObject} classes are often given both in pixel and in physical units,
+in order to be able to give some parameter independant of the image spacing.
+
+\subsubsection{itk::ShapeLabelObject attributes}
+
+\begin{itemize}
+  \item {\em Size} is the size of the object in number of pixels. Its type is
+{\em unsigned long}.
+  \item {\em PhysicalSize} is the size of the object in physical unit. It is equal
+to the {\em Size} multiplicated by the physical pixel size. Its type is {\em double}.
+  \item {\em Centroid} is the position of the center of the shape. It is not
+constrained to be in the object, and thus can be outside if the object is convex.
+Its type is {\em Point< double, ImageDimension >}. 
+  \item {\em Region} is the bounding box of the object given in the pixel coordinates.
+The physical coordinate can easily be computed from it. Its type is
+{\em ImageRegion< ImageDimension >}.
+  \item {\em RegionElongation} is the ratio of the longest physical size of the region
+on one dimension and its smallest physical size. This descriptor is not robust, and in
+particular is sensitive to rotation. Its type is {\em double}.
+  \item {\em SizeRegionRatio} is the ratio of the size of the object region (the
+bounding box) and the real size of the object. Its type is {\em double}.
+  \item {\em SizeOnBorder} is the number of pixels in the objects which are on the border
+of the image. This attribute is particulary useful to remove the objects which are touching
+too much the border. Its type is {\em unsigned long}.
+  \item {\em FeretDiameter} is the diameter in physical units of the sphere which include
+all the object. The feret diameter is computed by default only if the dimension of the image
+is $2$, because of its high computation cost for higher dimensions. Its type is {\em double}.
+%   \item {\em Perimeter}
+\end{itemize}
+
+\subsubsection{itk::StatisticsLabelObject attributes}
+
+\begin{itemize}
+  \item {\em Minimum} is the minimum value in the feature image for the object. Its type is
+the feature image pixel type.
+  \item {\em MinimumIndex} is the index position in the image where the first minimum was
+found. Its type is{\em Index< ImageDimension >}.
+  \item {\em Maximum} is the maximum value in the feature image for the object. Its type is
+the feature image pixel type.
+  \item {\em MaximumIndex} is the index position in the image where the first maximum was
+found. Its type is{\em Index< ImageDimension >}.
+  \item {\em Mean} is the mean of the pixel values in the object. Its type is {\em double}.
+  \item {\em Sum} is the sum of all the pixel values in the objects. Its type is {\em double}.
+  \item {\em Sigma} is the standard deviation of the pixels values in the objects. Its type
+is {\em double}.
+  \item {\em Variance} is the variance of the pixels values in the objects. Its type is
+{\em double}.
+  \item {\em Median} is the median of the pixels values in the obejct. Its type is
+{\em double}
+  \item {\em CenterOfGravity} is the center of gravity of the object. It type is
+{\em Point< double >}.
+%   \item {\em CentralMoments}
+%   \item {\em PrincipalMoments}
+%   \item {\em PrincipalAxes}
+  \item {\em Kurtosis} is the kurtosis of the pixel values in the objects. Its type is
+{\em double}.
+  \item {\em Skewness} is the skewness of the pixel values in the objects. Its type is
+{\em double}.
 \end{itemize}
@@
 thus the attributes must be valuated. Some filters are provided for the most
-common used one: {\em itk::ShapeLabelCollectionImageFilter} to fill the
+common used ones: {\em itk::ShapeLabelCollectionImageFilter} to fill the
 attributes of the {\em itk::ShapeLabelObject}s, and {\em
@@
 
+Finally, it has been chosen to develop a specific filter for the morphological
+reconstruction. It would have been possible to implement the reconstruction
+with the most common case (build the object collection, valuate the attributes
+filter the object, and rebuild the image), but for more efficiency, the reconstruction
+filter filters the collection directly, without giving them an attribute.
+
 \subsection{Generating an itk::Image from the itk::LabelCollectionImage}
@@
 
-\section{Available attributes}
-
-\subsection{Shape}
-
-\begin{itemize}
-  \item {\em Size}
-  \item {\em PhysicalSize}
-  \item {\em Centroid}
-  \item {\em Region}
-  \item {\em RegionElongation}
-  \item {\em SizeRegionRatio}
-  \item {\em SizeOnBorder}
-  \item {\em FeretDiameter}
-%   \item {\em Perimeter}
-\end{itemize}
-
-\subsection{Statistics}
-
-\begin{itemize}
-  \item {\em Minimum}
-  \item {\em Maximum}
-  \item {\em Mean}
-  \item {\em Sum}
-  \item {\em Sigma}
-  \item {\em Variance}
-  \item {\em Median}
-  \item {\em MaximumIndex}
-  \item {\em MinimumIndex}
-  \item {\em CenterOfGravity}
-%   \item {\em CentralMoments}
-%   \item {\em PrincipalMoments}
-%   \item {\em PrincipalAxes}
-  \item {\em Kurtosis}
-  \item {\em Skewness}
-\end{itemize}
-
 \section{Prebuilt mini-pipeline filters}
@@
 itk::Image},
+  \item valuation of the attribute(s) of the objects,
   \item filtering of the {\em itk::LabelCollectionImage},
@@
 
-Those filters have been made for binary, and labeled images.
+Because the objects are often get from a labeled image oor from a binary image,
+those filters have been made for binary, and labeled images.
 
@@
 
+To fit the ITK style, some iterators should be implemented to be able to iterate
+over all the 
+\begin{itemize}
+  \item objects,
+  \item lines,
+  \item or pixels
+\end{itemize}
+
+of an image, starting from 
+\begin{itemize}
+  \item an image,
+  \item an object,
+  \item or a line.
+\end{itemize}
+
+Doing that require a good knownledge of the iterator design. Any help on that point is
+welcome.
+
+Also, more attributes will be implemented, like the perimeter estimation, the usual moments, etc.
+
 \section{Conclusion}

### 2007-05-14 article/Article.tex
small corrections in the article
darcs-hash:20070514073934-2fc9d-7961b628a5dad2c74ec8ac204e47530437e4a9be.gz

@@
 in the foreground.
-  \item All the pixels greater than the mean of the maximum value in the image
-and the minimum value in the image are in the foreground. The other are in the
-background.
+  \item All the pixels greater than a value (zero by default, or the mean of the maximum value in the image
+and the minimum value in the image) are in the foreground. The other are in the
+background. This definition is often used in the levelset framework, where a border
+can be defined at a subpixel resolution.
 \end{itemize}
@@
 The labeled images are often used the represent the connected components of an
-image. As connected component, they can be efficiently store in memory as a set
+image. As connected component, they can be efficiently stored in memory as a set
 of lines, using the run-length encoding: a starting point for each line, and the
@@
 to the {\em Size} multiplicated by the physical pixel size. Its type is {\em double}.
-  \item {\em Centroid} is the position of the center of the shape. It is not
-constrained to be in the object, and thus can be outside if the object is convex.
+  \item {\em Centroid} is the position of the center of the shape in physical coordinates. It is not
+constrained to be in the object, and thus can be outside if the object is not convex.
 Its type is {\em Point< double, ImageDimension >}. 
@@
 
+Finally, all the binary and label filters should be implemented as a subclass of {\em InPlaceImageFilter}.
+
 \section{Conclusion}

### 2007-05-15 itkLabelShapeKeepNObjectsImageFilter.h
ShapeLabelCollectionImageFilter is now fully multithreaded and can take an optional image to decrease its computation time and memory usage. The Label filters are using a label for the LabelObject of the same type than the pixel type of the input image
darcs-hash:20070515093552-2fc9d-2665ec609a99f74e9eddba0d30025af995cfadc2.gz

@@ -72,7 +72,7 @@ public:
   itkStaticConstMacro(ImageDimension, unsigned int,
                       TInputImage::ImageDimension);
 
-  typedef ShapeLabelObject<unsigned long, ImageDimension> LabelObjectType;
+  typedef ShapeLabelObject<InputImagePixelType, ImageDimension> LabelObjectType;
   typedef typename itk::LabelCollectionImage< LabelObjectType > LabelCollectionImageType;
   typedef typename itk::LabelImageToLabelCollectionImageFilter< InputImageType, LabelCollectionImageType > LabelizerType;
   typedef typename itk::ShapeLabelCollectionImageFilter< LabelCollectionImageType > LabelObjectValuatorType;

### 2007-05-15 itkLabelStatisticsOpeningImageFilter.h

@@ -77,7 +77,7 @@ public:
   itkStaticConstMacro(ImageDimension, unsigned int,
                       TInputImage::ImageDimension);
 
-  typedef StatisticsLabelObject<unsigned long, ImageDimension> LabelObjectType;
+  typedef StatisticsLabelObject<InputImagePixelType, ImageDimension> LabelObjectType;
   typedef typename itk::LabelCollectionImage< LabelObjectType > LabelCollectionImageType;
   typedef typename itk::LabelImageToLabelCollectionImageFilter< InputImageType, LabelCollectionImageType > LabelizerType;
   typedef typename itk::StatisticsLabelCollectionImageFilter< LabelCollectionImageType, TFeatureImage > LabelObjectValuatorType;

### 2007-05-15 itkShapeLabelCollectionImageFilter.h

@@ -26,11 +26,19 @@ namespace itk {
  * ShapeLabelCollectionImageFilter can be used to set the attributes values
  * of the ShapeLabelObject in a LabelCollectionImage.
  *
+ * ShapeLabelCollectionImageFilter take an optional parameter, used only to optimize
+ * the computation time and the memory usage when the perimeter or the feret diameter
+ * are used: the exact copy of the input LabelCollectionImage but stored in an Image.
+ * It can be set with SetLabelImage(). It is cleared at the end of the computation, and
+ * so must be reset before running Update() again. It is not part of the pipeline management
+ * design, to let the subclasses of ShapeLabelCollectionImageFilter use the
+ * pipeline desing to specify a really required input.
+ *
  * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
  *
  * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
  */
-template<class TImage>
+template<class TImage, class TLabelImage=Image< typename TImage::PixelType, TImage::ImageDimension > >
 class ITK_EXPORT ShapeLabelCollectionImageFilter : 
     public InPlaceLabelCollectionImageFilter<TImage>
 {
@@ -50,6 +58,11 @@ public:
   typedef typename ImageType::IndexType       IndexType;
   typedef typename ImageType::SizeType        SizeType;
   typedef typename ImageType::LabelObjectType LabelObjectType;
+  
+  typedef TLabelImage LabelImageType;
+  typedef typename LabelImageType::Pointer         LabelImagePointer;
+  typedef typename LabelImageType::ConstPointer    LabelImageConstPointer;
+  typedef typename LabelImageType::PixelType       LabelPixelType;
   
   /** ImageDimension constants */
   itkStaticConstMacro(ImageDimension, unsigned int,
@@ -92,13 +105,21 @@ public:
   itkBooleanMacro(ComputePerimeter);
 
 
+   /** Set the label image */
+  void SetLabelImage( const TLabelImage *input )
+     {
+     m_LabelImage = input;
+     }
+
 protected:
   ShapeLabelCollectionImageFilter();
   ~ShapeLabelCollectionImageFilter() {};
 
   virtual void ThreadedGenerateData( LabelObjectType * labelObject );
   
-  void GenerateExtendedData();
+  virtual void BeforeThreadedGenerateData();
+
[…]

### 2007-05-15 itkShapeRelabelImageFilter.h

@@ -71,7 +71,7 @@ public:
   itkStaticConstMacro(ImageDimension, unsigned int,
                       TInputImage::ImageDimension);
 
-  typedef ShapeLabelObject<unsigned long, ImageDimension> LabelObjectType;
+  typedef ShapeLabelObject<InputImagePixelType, ImageDimension> LabelObjectType;
   typedef typename itk::LabelCollectionImage< LabelObjectType > LabelCollectionImageType;
   typedef typename itk::LabelImageToLabelCollectionImageFilter< InputImageType, LabelCollectionImageType > LabelizerType;
   typedef typename itk::ShapeLabelCollectionImageFilter< LabelCollectionImageType > LabelObjectValuatorType;

### 2007-05-15 itkStatisticsRelabelImageFilter.h

@@ -76,7 +76,7 @@ public:
   itkStaticConstMacro(ImageDimension, unsigned int,
                       TInputImage::ImageDimension);
 
-  typedef StatisticsLabelObject<unsigned long, ImageDimension> LabelObjectType;
+  typedef StatisticsLabelObject<InputImagePixelType, ImageDimension> LabelObjectType;
   typedef typename itk::LabelCollectionImage< LabelObjectType > LabelCollectionImageType;
   typedef typename itk::LabelImageToLabelCollectionImageFilter< InputImageType, LabelCollectionImageType > LabelizerType;
   typedef typename itk::StatisticsLabelCollectionImageFilter< LabelCollectionImageType, TFeatureImage > LabelObjectValuatorType;

### 2007-05-15 article/Article.tex
StatisticsLabelCollectionImageFilter is now multithreaded
darcs-hash:20070515095232-2fc9d-13fc7dfe7cd72dd8ca62f4badc3d82348c7c31b8.gz

@@
 \end{itemize}
+
+The classes {\em itk::ShapeLabelObject} and {\em itk::StatisticsLabelObject} have been
+created to reduce the number of filters made to manipulate the attributes, and to make
+the computation of all the set of attributes much efficient. In the early stage of
+development, all the attributes were managed as in {\em AttributeLabelObject}, and
+a set of 8 classes made to manipulate a single were provided, leading to a huge
+number of classes.
 
@@
 Also, more attributes will be implemented, like the perimeter estimation, the usual moments, etc.
+It may be useful to implement the most commonly used opening, keep N objects and relabel transforms in a more efficient way, by using an {\em AttributeLabelObject} instead of a {\em ShapeLabelObject} or a {\em StatisticsLabelObject}.
+
+All the {\em Shape} filters are currently able to use the Feret diameter only in 2D images.
+For the other dimensions, the feret diameter is not computed, and so always get a value of $0$.
+The computation of the Feret diameter should be forced if the user want to use it.
 

### 2007-05-15 itkStatisticsLabelCollectionImageFilter.h

@@ -44,13 +44,14 @@ public:
 
   /** Some convenient typedefs. */
   typedef TImage ImageType;
-  typedef typename ImageType::Pointer         ImagePointer;
-  typedef typename ImageType::ConstPointer    ImageConstPointer;
-  typedef typename ImageType::PixelType       PixelType;
-  typedef typename ImageType::IndexType       IndexType;
-  typedef typename ImageType::PointType       PointType;
-  typedef typename ImageType::LabelObjectType::MatrixType       MatrixType;
-  typedef typename ImageType::LabelObjectType::VectorType       VectorType;
+  typedef typename ImageType::Pointer          ImagePointer;
+  typedef typename ImageType::ConstPointer     ImageConstPointer;
+  typedef typename ImageType::PixelType        PixelType;
+  typedef typename ImageType::IndexType        IndexType;
+  typedef typename ImageType::PointType        PointType;
+  typedef typename ImageType::LabelObjectType  LabelObjectType;
+  typedef typename LabelObjectType::MatrixType MatrixType;
+  typedef typename LabelObjectType::VectorType VectorType;
   
   typedef TFeatureImage FeatureImageType;
   typedef typename FeatureImageType::Pointer         FeatureImagePointer;
@@ -108,13 +109,16 @@ protected:
   StatisticsLabelCollectionImageFilter();
   ~StatisticsLabelCollectionImageFilter() {};
 
-  /** Single-threaded version of GenerateData.  This filter delegates
-   * to GrayscaleGeodesicErodeImageFilter. */
-  void GenerateData();
+  virtual void ThreadedGenerateData( LabelObjectType * labelObject );
+  
+  virtual void BeforeThreadedGenerateData();
   
 private:
   StatisticsLabelCollectionImageFilter(const Self&); //purposely not implemented
   void operator=(const Self&); //purposely not implemented
+
+  FeatureImagePixelType m_Minimum;
+  FeatureImagePixelType m_Maximum;
 
 } ; // end of class
 

### 2007-06-11 article/Article.tex
add a word about the threading support and the inplace filtering
darcs-hash:20070611093626-2fc9d-6e718455db9ff810aa8e2be28d4f551b65d2e9c1.gz

@@
 No attribute are stored in this class, which can thus be see as the base class
-for the abjects with some attributes, or which can be used when no attributes
+for the objects with some attributes, or which can be used when no attributes
 are required.
@@
 with the most common case (build the object collection, valuate the attributes
-filter the object, and rebuild the image), but for more efficiency, the reconstruction
-filter filters the collection directly, without giving them an attribute.
+filter the object, and rebuild the image), but in order to make it compatible
+with the {\em ShapeLabelObject} and {\em StatisticsLabelObject}, the reconstruction
+filter filters the collection directly, without setting an attribute in the objects.
 
@@
 
+\section{Threading support}
+
+When possible, the filters provided with that contribution have been multithreaded.
+Some of them however, are not (easily) threadable (the {\em KeepNObjects} and {\em Relabel}
+filters), are shouldn't get any performance improvement in a threaded version
+(the {\em Opening} filters).
+
+The {\em BinaryImageToLabelCollectionImageFilter} class is a slight modification of the
+Richard Beare's {\em ConnectedComponentImageFilter}, and thus, has not been threaded.
+It should however be possible to increase its performance that way.
+
+The classical thread architecture is used when the input image is an {\em Image}: the image
+is splitted in several regions (one per thread), and each thread work on its own region.
+
+Because the {\em LabelCollectionImage} image is not an array of pixels, it can't be splitted
+that way. Instead, several threads are created, and try to take an object in the collection.
+If they get one, they process that object individually, and try to get another one when the
+object is processed. If no object can be get, the thread ends. A {\em FastMutexLock} is used
+to ensure that only one thread take an object at a time.
+
+For the developer, the usage of the threading support is made very simple, by subclassing
+{\em LabelCollectionImageFilter}, or {\em InPlaceLabelCollectionImageFilter}, and implementing
+the method {\em virtual void ThreadedGenerateData( LabelObjectType * labelObject )} in the
+new class. This method only has to process the labelObject passed in parameter. All the
+threading code and mutex lock management is already implemented. The mutex lock remain
+accessible if the subclass need to use it, as the {\em m\_LabelObjectContainerLock} ivar.
+
+\section{In place filtering}
+
+All the filters which are taking a {\em LabelCollectionImage} as input, and are producing a {\em LabelCollectionImage} as output, are implemented as a subclass of {\em InPlaceLabelCollectionImageFilter} and
+thus are running in place by default.
+
+The use can modify this behavior with the {\em SetInPlace( bool )}, {\em InPlaceOn()}, and {\em InPlaceOff()} methods, as with the usual {\em InPlaceImageFilter}.
+
+To use that feature, a developer only have to subclass {\em InPlaceLabelCollectionImageFilter} and
+implement the {\em virtual void ThreadedGenerateData( LabelObjectType * labelObject )}, to get easy thread
+support (see the previous section), or the {\em virtual void GenerateData()} if the filter is not threadable. In that last case,
+the only image to manipulate is the one get with the {\em GetOutput()} method, which is the input image if the filter runs in place, or a copy of the input image if the filter is not running in place.
+
 \section{Wrappers support}
@@
 
-\section{Future work}
+\section{Performance}
+
+TODO
+
+\section{Known bugs and future work}
 
@@
 
+The computation of the moments is partially implemented.
+The help of someone with a good knownledge of that subject would be very helpful to complete that work.
+The moments for the binary shape shoudl also be implemented.
+
 All the {\em Shape} filters are currently able to use the Feret diameter only in 2D images.
@@
 The computation of the Feret diameter should be forced if the user want to use it.
+
+The {\em BinaryImageToLabelCollectionImageFilter} class should be threaded to get the best of that filter on multiprocessors systems.
 
@@
 
-% \url{http://www.itk.org}
-% \code{Insight/Documentation/Style.pdf}
-% \section{Principles of Solar Spot Detection}
-% \cite{ITKSoftwareGuide}.
-% \doxygen{ImageToImageFilter}
-
-% \small \begin{verbatim}
-% \end{verbatim} \normalsize
-
-% The {itemize} environment uses a bullet for each \item.  If you want the 
-% \item's numbered, use the {enumerate} environment instead.
-% \begin{itemize}
-%   \item  Insight Toolkit 2.4.
-%   \item  CMake 2.2
-% \end{itemize}
-
-% \ref{cthead1}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{cthead1}
-\caption{The input image.\label{cthead1}}
-\end{figure}
+ITK is currntly lacking a good way to manipulate the binary objects. That contribution I hope to have mostly
+filled that lack.
 

### 2007-06-11 article/Article.tex
add some examples
darcs-hash:20070611115803-2fc9d-e1d5cb21f09637743eaa659fffafcc630462b877.gz

@@
 with the {\em ShapeLabelObject} and {\em StatisticsLabelObject}, the reconstruction
-filter filters the collection directly, without setting an attribute in the objects.
+filter filters the collection directly, without setting an attribute in the objects
+\footnote{I'm not really pleased with that design though, and I'thinking about
+reimplementing it using the generic attributes. It would have no impact on the
+binary filters API.}.
 
@@
 
-\subsection{...}
+\subsection{Prebuilt pipelines}
+
+\subsubsection{Binary shape opening}
+
+The source code is available in the file {\em binary\_shape\_opening.cxx}.
+
+\small \begin{verbatim}
+#include "itkImageFileReader.h"
+#include "itkImageFileWriter.h"
+#include "itkSimpleFilterWatcher.h"
+
+#include "itkBinaryShapeOpeningImageFilter.h"
+
+int main(int argc, char * argv[])
+{
+
+  if( argc != 9 )
+    {
+    std::cerr << "usage: " << argv[0] << " input output foreground background lambda reverseOrdering connectivity attribute" << std::endl;
+    // std::cerr << "  : " << std::endl;
+    exit(1);
+    }
+
+  const int dim = 3;
+
+  typedef itk::Image< unsigned char, dim > IType;
+
+  typedef itk::ImageFileReader< IType > ReaderType;
+  ReaderType::Pointer reader = ReaderType::New();
+  reader->SetFileName( argv[1] );
+
+  typedef itk::BinaryShapeOpeningImageFilter< IType > BinaryOpeningType;
+  BinaryOpeningType::Pointer opening = BinaryOpeningType::New();
+  opening->SetInput( reader->GetOutput() );
+  opening->SetForegroundValue( atoi(argv[3]) );
+  opening->SetBackgroundValue( atoi(argv[4]) );
+  opening->SetLambda( atof(argv[5]) );
+  opening->SetReverseOrdering( atoi(argv[6]) );
+  opening->SetFullyConnected( atoi(argv[7]) );
+  opening->SetAttribute( argv[8] );
+  itk::SimpleFilterWatcher watcher(opening, "filter");
+
+  typedef itk::ImageFileWriter< IType > WriterType;
+  WriterType::Pointer writer = WriterType::New();
+  writer->SetInput( opening->GetOutput() );
+  writer->SetFileName( argv[2] );
+  writer->Update();
+  return 0;
+}
+
+\end{verbatim} \normalsize
+
+\subsubsection{Statistics relabel}
+
+The source code is available in the file {\em statistics\_relabel.cxx}.
+
+\small \begin{verbatim}
+#include "itkImageFileReader.h"
+#include "itkImageFileWriter.h"
+#include "itkSimpleFilterWatcher.h"
+
+#include "itkStatisticsRelabelImageFilter.h"
+
+int main(int argc, char * argv[])
+{
+
+  if( argc != 8 )
+    {
+    std::cerr << "usage: " << argv[0] << " input input output background useBg reverseOrdering attribute" << std::endl;
+    // std::cerr << "  : " << std::endl;
+    exit(1);
+    }
+
+  const int dim = 3;
+
+  typedef itk::Image< unsigned char, dim > IType;
+
+  typedef itk::ImageFileReader< IType > ReaderType;
+  ReaderType::Pointer reader = ReaderType::New();
+  reader->SetFileName( argv[1] );
+
+  ReaderType::Pointer reader2 = ReaderType::New();
+  reader2->SetFileName( argv[2] );
+
+  typedef itk::StatisticsRelabelImageFilter< IType, IType > RelabelType;
+  RelabelType::Pointer relabel = RelabelType::New();
+  relabel->SetInput( reader->GetOutput() );
+  relabel->SetFeatureImage( reader2->GetOutput() );
+  relabel->SetBackgroundValue( atoi(argv[4]) );
+  relabel->SetUseBackground( atoi(argv[5]) );
+  relabel->SetReverseOrdering( atoi(argv[6]) );
+  relabel->SetAttribute( argv[7] );
+  itk::SimpleFilterWatcher watcher(relabel, "filter");
+
+  typedef itk::ImageFileWriter< IType > WriterType;
+  WriterType::Pointer writer = WriterType::New();
+  writer->SetInput( relabel->GetOutput() );
+  writer->SetFileName( argv[3] );
+  writer->Update();
+  return 0;
+}
+\end{verbatim} \normalsize
+
+\subsubsection{Label shape keep N obejcts}
+
+The source code is available in the file {\em label\_shape\_keep\_n\_objects.cxx}.
+
+\small \begin{verbatim}
+#include "itkImageFileReader.h"
+#include "itkImageFileWriter.h"
+#include "itkSimpleFilterWatcher.h"
+
+#include "itkLabelShapeKeepNObjectsImageFilter.h"
+
+int main(int argc, char * argv[])
+{
+
+  if( argc != 7 )
+    {
+    std::cerr << "usage: " << argv[0] << " input output background nb reverseOrdering attribute" << std::endl;
+    // std::cerr << "  : " << std::endl;
+    exit(1);
+    }
+
+  const int dim = 3;
+
+  typedef itk::Image< unsigned char, dim > IType;
+
+  typedef itk::ImageFileReader< IType > ReaderType;
+  ReaderType::Pointer reader = ReaderType::New();
+  reader->SetFileName( argv[1] );
+
+  typedef itk::LabelShapeKeepNObjectsImageFilter< IType > LabelOpeningType;
+  LabelOpeningType::Pointer opening = LabelOpeningType::New();
+  opening->SetInput( reader->GetOutput() );
+  opening->SetBackgroundValue( atoi(argv[3]) );
+  opening->SetNumberOfObjects( atoi(argv[4]) );
+  opening->SetReverseOrdering( atoi(argv[5]) );
+  opening->SetAttribute( argv[6] );
+  itk::SimpleFilterWatcher watcher(opening, "filter");
+
+  typedef itk::ImageFileWriter< IType > WriterType;
+  WriterType::Pointer writer = WriterType::New();
+  writer->SetInput( opening->GetOutput() );
+  writer->SetFileName( argv[2] );
+  writer->Update();
+  return 0;
+}
+\end{verbatim} \normalsize
+
+\subsubsection{Binary fill holes}
+
+The source code is available in the file {\em binary\_fillhole.cxx}.
+
+\small \begin{verbatim}
+#include "itkImageFileReader.h"
+#include "itkImageFileWriter.h"
+#include "itkCommand.h"
+#include "itkSimpleFilterWatcher.h"
+
+#include "itkLabelObject.h"
+#include "itkLabelCollectionImage.h"
+#include "itkBinaryFillholeImageFilter.h"
+
+int main(int argc, char * argv[])
+{
+
+  if( argc != 5 )
+    {
+    std::cerr << "usage: " << argv[0] << " input output conn fg" << std::endl;
+    // std::cerr << "  : " << std::endl;
+    exit(1);
+    }
+
+  const int dim = 2;
+
+  typedef itk::Image< unsigned char, dim > IType;
+
+  typedef itk::ImageFileReader< IType > ReaderType;
+  ReaderType::Pointer reader = ReaderType::New();
+  reader->SetFileName( argv[1] );
+  reader->Update();
+
+ typedef itk::BinaryFillholeImageFilter< IType > I2LType;
+  I2LType::Pointer reconstruction = I2LType::New();
+  reconstruction->SetInput( reader->GetOutput() );
+  reconstruction->SetFullyConnected( atoi(argv[3]) );
+  reconstruction->SetForegroundValue( atoi(argv[4]) );
+//   reconstruction->SetBackgroundValue( atoi(argv[5]) );
+  itk::SimpleFilterWatcher watcher(reconstruction, "filter");
+
+  typedef itk::ImageFileWriter< IType > WriterType;
+  WriterType::Pointer writer = WriterType::New();
+  writer->SetInput( reconstruction->GetOutput() );
+  writer->SetFileName( argv[2] );
+  writer->Update();
+  return 0;
+}
+\end{verbatim} \normalsize
+
+\subsection{LabelObject and LabelCollectionImage manipulation}
+
+\subsubsection{LabelObject}
+
+\subsubsection{ShapeLabelObject}
+
+\subsubsection{StatisticsLabelObject}
+
+\subsubsection{AttributeLabelObject}
+
+The {\em AttributeLabelObject} let the user specify the type of the attribute
+he wants to use, and thus is the good choice to implement a new attribute.
+
+The source code is available in the file {\em generic\_attribute.cxx}.
+
+First we include the headers of the class we will use, and parse the command line.
+
+\small \begin{verbatim}
+#include "itkImageFileReader.h"
+#include "itkImageFileWriter.h"
+
+#include "itkAttributeLabelObject.h"
+#include "itkLabelCollectionImage.h"
+
+#include "itkLabelImageToLabelCollectionImageFilter.h"
+
+#include "itkAttributeKeepNObjectsLabelCollectionImageFilter.h"
+#include "itkAttributeOpeningLabelCollectionImageFilter.h"
+#include "itkAttributeRelabelLabelCollectionImageFilter.h"
+
+#include "itkLabelCollectionImageToAttributeImageFilter.h"
+#include "itkLabelCollectionImageToLabelImageFilter.h"
+
+int main(int argc, char * argv[])
+{
+
+  if( argc != 10 )
+    {
+    std::cerr << "usage: " << argv[0] << " label input attr keep open relabel bg lambda nb" << std::endl;
+    // std::cerr << "  : " << std::endl;
+    exit(1);
+    }
+\end{verbatim} \normalsize
+Declare the dimension used, and the type of the image for input and output.
+\small \begin{verbatim}
+  const int dim = 2;
+  typedef unsigned char PType;
+  typedef itk::Image< PType, dim > IType;
+\end{verbatim} \normalsize
+The AttributeLabelObject class take 3 template parameters: the 2 ones
+from the LabelObject class, and the type of the attribute associated
+with each node. Here we have chosen a double. We then declares the
+type of the LabelCollectionImage with the type of the label object.
+\small \begin{verbatim}
+  typedef itk::AttributeLabelObject< unsigned long, dim, double > LOType;
+  typedef itk::LabelCollectionImage< LOType > LCIType;
+\end{verbatim} \normalsize
+We read the input images.
+\small \begin{verbatim}
+  typedef itk::ImageFileReader< IType > ReaderType;
+  ReaderType::Pointer reader = ReaderType::New();
+  reader->SetFileName( argv[1] );
+
+  ReaderType::Pointer reader2 = ReaderType::New();
+  reader2->SetFileName( argv[2] );
+\end{verbatim} \normalsize
+And convert the label image to a LabelCollectionImage.
+\small \begin{verbatim}
+  typedef itk::LabelImageToLabelCollectionImageFilter< IType, LCIType > I2LType;
+  I2LType::Pointer i2l = I2LType::New();
+  i2l->SetInput( reader->GetOutput() );
+  i2l->SetBackgroundValue( atoi(argv[7]) );
+\end{verbatim} \normalsize
+The next step is made outside the pipeline model, so we call Update() now.
+\small \begin{verbatim}
+  i2l->Update();
+  reader2->Update();
+\end{verbatim} \normalsize
+Now we will valuate the attribute. The attribute will be the mean of the pixels
+values in the 2nd image. Note that the StatisticsLabelObject can give us that value, without
+having to code that by hand - that's an example.
+
+Lets begin by declaring the iterator for the objects in the image, and get the object container, to reuse it later.
+\small \begin{verbatim}
+  LCIType::LabelObjectContainerType::const_iterator it;
+  LCIType::Pointer labelCollection = i2l->GetOutput();
+  const LCIType::LabelObjectContainerType & labelObjectContainer = labelCollection->GetLabelObjectContainer();
+\end{verbatim} \normalsize
+Now iterate over all the objects in the image.
+\small \begin{verbatim}
+  for( it = labelObjectContainer.begin(); it != labelObjectContainer.end(); it++ )
+    {
+\end{verbatim} \normalsize
+The label is there if we need it, but it can also be found at labelObject->GetLabel().
+\small \begin{verbatim}
+    const PType & label = it->first;
+    LOType * labelObject = it->second;
+\end{verbatim} \normalsize
+Init the variables used for the computation.
+\small \begin{verbatim}
+    double mean = 0;
+    unsigned long size = 0;
+\end{verbatim} \normalsize
+Create the iterator for the lines, and iterate over them
+\small \begin{verbatim}
+    LOType::LineContainerType::const_iterator lit;
+    LOType::LineContainerType lineContainer = labelObject->GetLineContainer();
+
+    for( lit = lineContainer.begin(); lit != lineContainer.end(); lit++ )
+      {
+      const LCIType::IndexType & firstIdx = lit->GetIndex();
+      const unsigned long & length = lit->GetLength();
+
+      size += length;
+\end{verbatim} \normalsize
+Then iterate over all the pixels in the line, and get the pixel values in the feature image to compute their mean.
+\small \begin{verbatim}
+      long endIdx0 = firstIdx[0] + length;
+      for( LCIType::IndexType idx = firstIdx; idx[0]<endIdx0; idx[0]++)
+        {
+        mean += reader2->GetOutput()->GetPixel( idx );
+        }
+      }
+\end{verbatim} \normalsize
+Complete the compuation of the mean, and set it as attibute value for the current object.
+\small \begin{verbatim}
+    mean /= size;
+    labelObject->SetAttribute( mean );
+\end{verbatim} \normalsize
+The LabelObject class provides a Print() method to display its ivars.
+\small \begin{verbatim}
+    labelObject->Print( std::cout );
+
+    }
+\end{verbatim} \normalsize
+Now that the objects have their attribute, we are free to manipulate them with
+the common filters, or by hand. The default accessor (AttributeLabelObject)
+is the wright one when using AttributeLabelObject so we don't have to specify it.
+A different one can be used if needed though.
+\small \begin{verbatim}
+  typedef itk::AttributeKeepNObjectsLabelCollectionImageFilter< LCIType > KeepType;
+  KeepType::Pointer keep = KeepType::New();
+  keep->SetInput( labelCollection );
+  keep->SetReverseOrdering( true );
+  keep->SetNumberOfObjects( atoi(argv[9]) );
+\end{verbatim} \normalsize
+Prevent the filter to run in place, so the input image is not modified.
+\small \begin{verbatim}
+  keep->SetInPlace( false );
+
+  typedef itk::AttributeOpeningLabelCollectionImageFilter< LCIType > OpeningType;
+  OpeningType::Pointer opening = OpeningType::New();
+  opening->SetInput( labelCollection );
+  opening->SetLambda( atof(argv[8]) );
+  keep->SetInPlace( false );
+
+  typedef itk::AttributeRelabelLabelCollectionImageFilter< LCIType > RelabelType;
+  RelabelType::Pointer relabel = RelabelType::New();
+  relabel->SetInput( labelCollection );
+  keep->SetInPlace( false );
+\end{verbatim} \normalsize
+The attribute values can be put directly in a classic image.
+\small \begin{verbatim}
+  typedef itk::LabelCollectionImageToAttributeImageFilter< LCIType, IType > A2IType;
+  A2IType::Pointer a2i = A2IType::New();
+  a2i->SetInput( labelCollection );
+\end{verbatim} \normalsize
+Or the label collection can be converted back to an label image, or to a binary image
+(not shown here)
+\small \begin{verbatim}
+  typedef itk::LabelCollectionImageToLabelImageFilter< LCIType, IType > L2IType;
+  L2IType::Pointer l2i = L2IType::New();
+\end{verbatim} \normalsize
+Finally, write the results
+\small \begin{verbatim}
+  typedef itk::ImageFileWriter< IType > WriterType;
+  WriterType::Pointer writer = WriterType::New();
+
+  writer->SetInput( a2i->GetOutput() );
+  writer->SetFileName( argv[3] );
+  writer->Update();
+
+  writer->SetInput( l2i->GetOutput() );
+
+  l2i->SetInput( keep->GetOutput() );
+  writer->SetFileName( argv[4] );
+  writer->Update();
+
+  l2i->SetInput( opening->GetOutput() );
+  writer->SetFileName( argv[5] );
+  writer->Update();
+
+  l2i->SetInput( relabel->GetOutput() );
+  writer->SetFileName( argv[6] );
+  writer->Update();
+
+  return 0;
+}
+\end{verbatim} \normalsize
 

### 2007-06-12 article/Article.tex
more of the article
darcs-hash:20070612082030-2fc9d-96f7cbe63e59ef1fa99184f9679c338d39d72a85.gz

@@
 
-Because the objects are often get from a labeled image oor from a binary image,
+Because the objects are often get from a labeled image or from a binary image,
 those filters have been made for binary, and labeled images.
@@
 
-\subsubsection{LabelObject}
-
-\subsubsection{ShapeLabelObject}
-
-\subsubsection{StatisticsLabelObject}
-
+% \subsubsection{LabelObject}
+% 
+% TODO
+% 
+% \subsubsection{ShapeLabelObject}
+% 
+% TODO
+% 
+% \subsubsection{StatisticsLabelObject}
+% 
+% TODO
+% 
 \subsubsection{AttributeLabelObject}
@@
 implement the {\em virtual void ThreadedGenerateData( LabelObjectType * labelObject )}, to get easy thread
-support (see the previous section), or the {\em virtual void GenerateData()} if the filter is not threadable. In that last case,
+support \footnote{see the previous section}, or the {\em virtual void GenerateData()} if the filter is not threadable. In that last case,
 the only image to manipulate is the one get with the {\em GetOutput()} method, which is the input image if the filter runs in place, or a copy of the input image if the filter is not running in place.
@@
 
-ITK is currntly lacking a good way to manipulate the binary objects. That contribution I hope to have mostly
+ITK is currently lacking a good way to manipulate the binary objects. That contribution I hope to have mostly
 filled that lack.

### 2007-08-10 article/Article.tex
more of the article
darcs-hash:20070810084508-2fc9d-05f2c848b6f60e9e7a3c1103260ad4c6c77faf57.gz

@@
 
-ITK is currently lacking a good way to manipulate the binary objects. That contribution I hope to have mostly
+ITK is currently lacking a good way to manipulate the binary objects. With that contribution I hope to have mostly
 filled that lack.
+
+\section{Acknowledgments}
+I thank Richard Beare for his suggestion to use the run length encoding to represent the binary objects, and Julien Jomier for his help for the choice to {\em not} use the {\em SpatialObject} class as base class of the {\em LabelObejct} class.
+
+I thank Dr Pierre Adenot and MIMA2 confocal facilities
+(\url{http://mima2.jouy.inra.fr}) for providing the 3D test image.
+I am grateful to the INRA MIGALE bioinformatics platform
+(\url{http://migale.jouy.inra.fr}) for providing the computational resources
+used for the timing tests.
 

### 2007-08-16 itkInPlaceLabelCollectionImageFilter.h
enhance threading test
darcs-hash:20070816100815-2fc9d-8ea7f1f3e35276592005a30fb7b3837ab7bcc80a.gz

@@ -87,6 +87,7 @@ public:
   typedef typename InputImageType::ConstPointer   InputImageConstPointer;
   typedef typename InputImageType::RegionType     InputImageRegionType; 
   typedef typename InputImageType::PixelType      InputImagePixelType;
+  typedef typename InputImageType::LabelObjectType LabelObjectType;
 
   typedef typename InputImageType::PixelType       PixelType;
   typedef typename InputImageType::IndexType       IndexType;

### 2007-08-16 article/Article.tex
enhance the article
darcs-hash:20070816100853-2fc9d-c41f329c9d27656df2cbe7d345bccb2bcdd0b46c.gz

@@
 The labeled images are often used the represent the connected components of an
-image. As connected component, they can be efficiently stored in memory as a set
+image. In this contribution, another representation has been chosen.
+
+The objects contained in the image, as connected component, can be efficiently stored in memory as a set
 of lines, using the run-length encoding: a starting point for each line, and the
-length of the line on a given dimension (by convention, the dimension 0). The
-image the can be seen as a collection of objects.
+length of the line on a given dimension (by convention, the dimension 0).
+
+The image is a collection of those objects, which also store some values of the image, like its size, its spacing, etc.
 
@@
 like
-the spacing, the physical position, etc.
+the spacing, the physical position - all the metadata found in {\em itk::Image}.
 
 The {\em itk::LabelCollectionImage} provide a part of the API of the {\em
-itk::Image} class,
-and so can be manipulated as an image\footnote{It doesn't support the itk::Image
-iterators though}
-in may cases. The performance can be very different however.
+itk::Image} class, and so can be manipulated as an image\footnote{It doesn't
+support the itk::Image iterators though} in many cases. The performance can be
+very different however, because of the very different data structure used.
+
+The {\em itk::LabelCollectionImage} is a templated class, which take a single
+parameter: the type of {\em labeled object} stored by that class. The dimension
+of the image is took from the {\em labeled object} class, and thus don't need to
+be defined as template parameter of that class. The pixel type of the image
+also comes from the {\em labeled object} class.
 
@@
 
-No attribute are stored in this class, which can thus be see as the base class
-for the objects with some attributes, or which can be used when no attributes
+No attribute are stored in this class, which can thus be seen as the base class
+for the objects with attributes, or which can be used when no attributes
 are required.
 
-Several subclasses are provided with that article:
+The {\em itk::LabelObject} class is templated and takes to required template parameters:
+\begin{itemize}
+  \item the type of the label,
+  \item the dimension of the image.
+\end{itemize}
+
+Several subclasses are provided with that contribution, to cover the most common
+usages of the labeled objects manipulation:
 \begin{itemize}
@@
 grey values of a feature image in the same place than the labeled object.
-Computing the values of those attributes does require a feature image.
+Computing the values of those attributes {\em does} require a feature image.
 \end{itemize}
@@
 development, all the attributes were managed as in {\em AttributeLabelObject}, and
-a set of 8 classes made to manipulate a single were provided, leading to a huge
+a set of 8 classes made to manipulate a single attribute were provided, leading to a huge
 number of classes.
@@
 in order to be able to give some parameter independant of the image spacing.
+
+Both {\em itk::ShapeLabelObject} and {\em itk::StatisticsLabelObject} are templated classes.
+They take the same template parameters than the {\em itk::LabelObject} class.
+The 2 first template parameters of the {\em itk::AttributeLabelObject} class or the same
+than the {\em itk::LabelObject} class. The third one is the attribute type.
 
@@
 The {\em itk::LabelCollectionImage} class provide some methods to fill the
-image. However, the most efficient way is to convert a labeled image or a binary
+image "by hand", like the usual {\em SetPixel()} method. However, the most efficient way is to convert a labeled image or a binary
 image stored in an {\em itk::Image} to a {\em itk::LabelCollectionImage}, by
@@
 The label objects produced by those filters have no attribute value set, and
-thus the attributes must be valuated. Some filters are provided for the most
-common used ones: {\em itk::ShapeLabelCollectionImageFilter} to fill the
-attributes of the {\em itk::ShapeLabelObject}s, and {\em
-itk::ShapeLabelCollectionImageFilter} to fill the attributes of the {\em
-itk::StatisticsLabelObject}s. For the {\em itk::AttributeLabelObject} class or
+thus, the attributes must be valuated. Some filters are provided for the most
+common used ones:
+
+\begin{itemize}
+  \item {\em itk::ShapeLabelCollectionImageFilter} to fill the
+attributes of the {\em itk::ShapeLabelObject}s, 
+  \item and {\em itk::ShapeLabelCollectionImageFilter} to fill the attributes of the {\em
+itk::StatisticsLabelObject}s.
+\end{itemize}
+
+For the {\em itk::AttributeLabelObject} class or
 other classes, the user must set the value by himself, for example by
@@
 
-Once created and, optionally, valued, several filters are provided to manipulate
+Once created and, optionally, valuated, several filters are provided to manipulate
 the {\em itk::LabelCollectionImage}:
@@
 OpeningLabelCollectionImageFilter} classes. Those classes will remove all the
-objects with an attribute value lower or greater than a given value. It's a very
-convenient way to enhance a segmentation for example, because we often can use
-that way some criteria  which have not been used during the segmentation
-procedure, like the size of the object, the mean value of its pixels, etc.
+objects with an attribute value lower or greater than a given value.
+Because we often can use some criteria  which have not been used during the segmentation
+procedure, like the size of the object, the mean value of its pixels, etc., the attribute
+opening is often a very efficient way to enhance a segmentation. For example, after
+a thresholding of a grayscale image, the objects too small or too beg to be of interest
+can be removed that way.
+
   \item A fixed number of objects can be kept, with the {\em
@@
 highest, or with the lowest attribute values.
+
   \item The objects can be relabel, with the {\em
@@
 
+\subsection{Reading attribute values}
+
+In that example, we will read a binary image, and get some of attributes
+about the obejcts contained in that image.
+The source code is available in the file {\em attribute\_values.cxx}.
+
+First include the classes we'll use
+\small \begin{verbatim}
+#include "itkImageFileReader.h"
+#include "itkShapeLabelObject.h"
+#include "itkLabelCollectionImage.h"
+#include "itkBinaryImageToLabelCollectionImageFilter.h"
+#include "itkShapeLabelCollectionImageFilter.h"
+
+int main(int, char * argv[])
+{
+  const int dim = 2;
+\end{verbatim} \normalsize
+then declare the type of the input image
+\small \begin{verbatim}
+  typedef unsigned char PixelType;
+  typedef itk::Image< PixelType, dim >    ImageType;
+
+\end{verbatim} \normalsize
+read the input image
+\small \begin{verbatim}
+  typedef itk::ImageFileReader< ImageType > ReaderType;
+  ReaderType::Pointer reader = ReaderType::New();
+  reader->SetFileName( argv[1] );
+
+\end{verbatim} \normalsize
+define the object type. Here the ShapeLabelObject type
+is chosen in order to read some attribute related to the shape
+of the objects (by opposition to the content of the object, with
+the StatisticsLabelObejct).
+\small \begin{verbatim}
+  typedef unsigned long LabelType;
+  typedef itk::ShapeLabelObject< LabelType, dim > LabelObjectType;
+  typedef itk::LabelCollectionImage< LabelObjectType > LabelCollectionType;
+
+\end{verbatim} \normalsize
+convert the image in a collection of objects
+\small \begin{verbatim}
+  typedef itk::BinaryImageToLabelCollectionImageFilter< ImageType, LabelCollectionType > ConverterType;
+  ConverterType::Pointer converter = ConverterType::New();
+  converter->SetInput( reader->GetOutput() );
+  converter->SetForegroundValue( 200 );
+
+\end{verbatim} \normalsize
+and valuate the attributes with the dedicated filter: ShapeLabelCollectionImageFilter
+\small \begin{verbatim}
+  typedef itk::ShapeLabelCollectionImageFilter< LabelCollectionType > ShapeFilterType;
+  ShapeFilterType::Pointer shape = ShapeFilterType::New();
+  shape->SetInput( converter->GetOutput() );
+
+\end{verbatim} \normalsize
+update the shape filter, so its output will be up to date
+\small \begin{verbatim}
+  shape->Update();
+
+\end{verbatim} \normalsize
+then we can read the attribute values we're interested in. {\em BinaryImageToLabelCollectionImageFilter}
+produces consecutives labels, so a simple {for} loop will do the job.
+\small \begin{verbatim}
+  LabelCollectionType::Pointer collection = shape->GetOutput();
+  for( int label=1; label<collection->GetNumberOfObjects(); label++ )
+    {
+    LabelObjectType::Pointer labelObject = collection->GetLabelObject( label );
+    std::cout << label << "\t" << labelObject->GetPhysicalSize() << "\t" << labelObject->GetCentroid() << std::endl;
+    }
+
+  return 0;
+}
+\end{verbatim} \normalsize
+
 \section{Threading support}
@@
 
-\section{Performance}
-
-TODO
+% \section{Performance}
+% 
+% TODO
 
@@
 
-Also, more attributes will be implemented, like the perimeter estimation, the usual moments, etc.
+Also, more attributes will be implemented, like the perimeter estimation, the usual image moments, etc.
 It may be useful to implement the most commonly used opening, keep N objects and relabel transforms in a more efficient way, by using an {\em AttributeLabelObject} instead of a {\em ShapeLabelObject} or a {\em StatisticsLabelObject}.
@@
 The help of someone with a good knownledge of that subject would be very helpful to complete that work.
-The moments for the binary shape shoudl also be implemented.
+The moments for the binary shape should also be implemented.
 

### 2007-08-16 article/Article.tex
minor corrections
darcs-hash:20070816123635-2fc9d-3e4c7401a9abb4ac53181fad56e61bc0c99bf75e.gz

@@
 manipulation based on object attributes, as well as the binary specialization of
-some mathematical morphology filter already include in ITK, and not related to
+some mathematical morphology filter already included in ITK, and not related to
 the attribute of the objects. With those last filters, this contribution comes
@@
 
-All the source codes are provided, as well as a full set of test and several
+All the source codes are provided, as well as a full set of tests and several
 usage examples of the new classes.

### 2007-08-27 article/Article.tex
update doc
darcs-hash:20070827094330-2fc9d-c87da7963a9323a4f21a12b188cfbdb8a1d3fb90.gz

@@
   \item {\em FeretDiameter} is the diameter in physical units of the sphere which include
-all the object. The feret diameter is computed by default only if the dimension of the image
-is $2$, because of its high computation cost for higher dimensions. Its type is {\em double}.
+all the object. The feret diameter is not computed by default, because of its high computation.
+Its type is {\em double}.
+  \item {\em BinaryPrincipalMoments} contains the principal moments. Its type is
+{\em itk::Vector< double, ImageDimension >}.
+  \item {\em BinaryPrincipalAxes} contains the principal axes of the object. Its type is
+{\em itk::Matrix< double, ImageDimension, ImageDimension >}.
+  \item {\em BinaryElongation} is the elongation of the shape, computed as the ratio
+of the largest principal moment by the smallest principal moment. Its value is greater
+or equal to $1$· Its type si {\em double}.
 %   \item {\em Perimeter}
@@
 {\em double}.
+  \item {\em PrincipalMoments} contains the principal moments. Its type is
+{\em itk::Vector< double, ImageDimension >}.
+  \item {\em PrincipalAxes} contains the principal axes of the object. Its type is
+{\em itk::Matrix< double, ImageDimension, ImageDimension >}.
+  \item {\em Elongation} is the elongation of the shape, computed as the ratio
+of the largest principal moment by the smallest principal moment. Its value is greater
+or equal to $1$· Its type si {\em double}.
 \end{itemize}
@@
 
-Also, more attributes will be implemented, like the perimeter estimation, the usual image moments, etc.
+Also, more attributes will be implemented, like the perimeter estimation.
 It may be useful to implement the most commonly used opening, keep N objects and relabel transforms in a more efficient way, by using an {\em AttributeLabelObject} instead of a {\em ShapeLabelObject} or a {\em StatisticsLabelObject}.
 
-The computation of the moments is partially implemented.
-The help of someone with a good knownledge of that subject would be very helpful to complete that work.
-The moments for the binary shape should also be implemented.
-
-All the {\em Shape} filters are currently able to use the Feret diameter only in 2D images.
-For the other dimensions, the feret diameter is not computed, and so always get a value of $0$.
+All the {\em Shape} filters are currently unable to use the Feret diameter.
+The feret diameter is not computed by default, and so always get a value of $0$.
 The computation of the Feret diameter should be forced if the user want to use it.

### 2007-08-27 article/Article.tex
minor fixes in the article
darcs-hash:20070827133851-2fc9d-6e9eb8802bf984a62f3d06d159980098ea89a635.gz

@@
 % snail-mail address if you like.
-\author{Ga\"etan Lehmann{$^2$}}
+\author{Ga\"etan Lehmann{$^1$}}
 \authoraddress{{$^1$}INRA, UMR 1198; ENVA; CNRS, FRE 2857, Biologie du
@@
 \section{Acknowledgments}
-I thank Richard Beare for his suggestion to use the run length encoding to represent the binary objects, and Julien Jomier for his help for the choice to {\em not} use the {\em SpatialObject} class as base class of the {\em LabelObejct} class.
+I thank Richard Beare for his suggestion to use the run length encoding to represent the binary objects, and Julien Jomier for his help for the choice to {\em not} use the {\em itk::SpatialObject} class as base class of the {\em itk::LabelObejct} class.
 

### 2007-08-29 article/Article.tex
some info about how is computed the roundness
darcs-hash:20070829134929-2fc9d-d02c527bfa0fcd0318a3b02a95b32c5006a7f7fa.gz

@@
 
+\section{Computation details}
+
+\subsection{Binary image moments}
+
+\subsection{Roundness}
+
+The computation works with any image dimension, and so use the definition
+of volume and area of an hypersphere in any dimension.
+
+\begin{eqnarray}
+V_n(r) & = {\pi^\frac{n}{2}r^n\over\Gamma(\frac{n}{2} + 1)}
+\end{eqnarray}
+where $V_n$ is the volume of the hypersphere $n$ is the image dimension,
+and $r$ is the radius of the hypersphere.
+
+\begin{eqnarray}
+\Gamma\left(\frac{n}{2}+1\right) = \begin{cases}
+  \left(\frac{n}{2}\right)!               & \text{if $n$ is even}, \\
+  \sqrt{\pi}\frac{n!!}{2^{(n+1)/2}} & \text{if $n$ is odd}.
+                                   \end{cases}
+\end{eqnarray}
+
+$n!!$ is the double factorial, defined as
+
+\begin{eqnarray}
+n!! = \begin{cases}
+  1          & \text{if $n < 2$}, \\
+  n (n-2)!!  & \text{if $n \geq 2$}.
+      \end{cases}
+\end{eqnarray}
+
+\begin{eqnarray}
+A_n(r) & = {\frac{n V_n}{r}}
+\end{eqnarray}
+
+Where $A_n$ is the area of the hypersphere.
+
+\begin{eqnarray}
+R & = {\frac{a}{A_n(r)}}
+\end{eqnarray}
+
+where $R$ is the roundness, $a$ is the measured area of the object, and the $r$ is the radius of an hypersphere with the same volume than the object.
+
 \section{Usage examples}

### 2007-08-29 article/Article.tex
add details about binary moment computation
darcs-hash:20070829162327-2fc9d-59d8891b28b49862e09a0a6e46dbfc21d5471c93.gz

@@
 
+Central image moments for grayscale images are usually computed as
+
+\begin{eqnarray}
+Cm_{i,j} = \sum_{p \in D} I(p).p_i.p_j
+\end{eqnarray}
+
+where $Cm_{i,j}$ is the central moment, $D$ is the domain of definition of the
+image $I$, $I(p)$ is the pixel value of the image at the position $p$,
+$0 \leq i < n$, $0 \leq i < n$, $n$ is the image dimension, and $p_i$ is the
+physical position on the axis $i$. With binary images, $I(p)$ is either $0$ 
+if $p$ is outside the object, or $1$ if $p$ is inside.
+
+The complexity is $O(N_{P_I})$, where $N_{P_I}$ is the number of pixels in the image.
+
+With the run-length encoding of the binary objects, the complexity can be decreased
+to $O(N_{L_O})$, where $N_{L_O}$ is the number of lines in the object.
+
+\begin{eqnarray}
+Cm_{i,j} & = & \sum_{p \in D} I(p).p_i.p_j \\ \nonumber
+         & = & \sum_{p \in O} p_i.p_j \\ \nonumber
+         & = & \sum_{l \in O}  \sum_{p \in L} p_i.p_j
+\end{eqnarray}
+
+In a line, $p_i$ is a constant if $i > 0$, so
+
+\begin{eqnarray}
+Cm_{i,j} = \begin{cases}
+  \underset{L \in O}\sum l_L.p_i.p_j                & \text{if $i > 0$ and $j > 0$}, \\
+  \underset{L \in O}\sum l_L.p_i.\underset{p \in L}\sum p_0  & \text{if $i > 0$ and $j = 0$}, \\
+  \underset{L \in O}\sum l_L.p_j.\underset{p \in L}\sum p_0  & \text{if $i = 0$ and $j > 0$}, \\
+  \underset{L \in O}\sum \underset{p \in L}\sum p_0^2            & \text{if $i = j = 0$}.
+           \end{cases}
+\end{eqnarray}
+
+It is known that
+\begin{eqnarray}
+\sum_{x=1}^n x   & = & \frac{n(n+1)}{2} \\
+\sum_{x=1}^n x^2 & = & \frac{n(n+1)(2n+1)}{6}
+\end{eqnarray}
+
+In order to use those formulae, the physical position has to be expanded in
+\begin{eqnarray}
+p_j = o_j + s_j i_j
+\end{eqnarray}
+where $o_j$ is the origin of the line on the axis $j$, $s_j$ is the spacing on the axis $j$, and
+$i_j$ is the index on the axis $j$.
+
+With equations TODO and TODO, its easy to compute the sum of physical positions of the axis $0$:
+
+\begin{eqnarray}
+\sum_{p \in L} p_0  & = & \sum_{i_0=0}^{l_L-1} (o_0 + s_0 i_0) \\ \nonumber
+                    & = & l_L.o_0 + s_0\sum_{i_0=0}^{l_L-1} i_0 \\ \nonumber
+                    & = & l_L.o_0 + s_0\left( \frac{(l_L-1)l}{2} \right)
+\end{eqnarray}
+
+where $l_L$ is the length of the line (in pixels), and the the sum of the square of the physical positions of the axis $0$:
+
+\begin{eqnarray}
+\sum_{p \in L} p_0^2  & = & \sum_{i_0=0}^{l_L-1} ( o_0 + s_0 i_0 )^2 \\ \nonumber
+                      & = & \sum_{i_0=0}^{l_L-1} ( o_0^2 + s_0^2 i_0^2 + 2 o_0 i_0) \\ \nonumber
+                      & = & l_L.o_0^2 + s_0^2\sum_{i_0=0}^{l_L-1} i_0^2 + 2 o_0 \sum_{i_0=0}^{l_L-1} i_0 \\ \nonumber
+                      & = & l_L.o_0^2 + s_0^2 \left( \frac{(l_L-1)l_L(2l_L-1)}{6} \right) + 2 o_0 \left( \frac{(l_L-1)l_L}{2} \right)
+\end{eqnarray}
+
+Finally, central moments are:
+\begin{eqnarray}
+Cm_{i,j} = \begin{cases}
+  \underset{L \in O}\sum l_L.p_i.p_j                & \text{if $i > 0$ and $j > 0$}, \\
+  \underset{L \in O}\sum l_L.p_i \left( l_L.o_0 + s_0\left( \frac{(l_L-1)l_L}{2}  \right) \right) & \text{if $i > 0$ and $j = 0$}, \\
+  \underset{L \in O}\sum l_L.p_j \left( l_L.o_0 + s_0\left( \frac{(l_L-1)l_L}{2}  \right) \right) & \text{if $i = 0$ and $j > 0$}, \\
+  \underset{L \in O}\sum \left( l_L.o_0^2 + s_0^2 \left( \frac{(l_L-1)l_L(2l_L-1)}{6} \right) + 2 o_0 \left( \frac{(l_L-1)l_L}{2} \right) \right)            & \text{if $i = j = 0$}.
+           \end{cases}
+\end{eqnarray}
+
 \subsection{Roundness}

### 2007-08-30 article/Article.tex
some corrections on the computation details
darcs-hash:20070830135535-2fc9d-98127f46b4d9fb87085437cec0d521419f0906a1.gz

--- 2007-08-29 article/Article.tex
@@
 
+Central image moments for grayscale images are usually computed as
+
+\begin{eqnarray}
+Cm_{i,j} & = & \frac{S_{i,j}}{M} - Cg_i.Cg_j \\
+S_{i,j}  & = & \sum_{p \in D} \left( I(p).p_i.p_j \right)
+\end{eqnarray}
+
+where $S_{i,j}$ is the central moment, $D$ is the domain of definition of the
+image $I$, $I(p)$ is the pixel value of the image at the position $p$,
+$0 \leq i < n$, $0 \leq i < n$, $n$ is the image dimension, $p_i$ is the
+physical position on the axis $i$, $M$ is the total mass, $Cg$ is the center of
+gravity. With binary images, $I(p)$ is either $0$ 
+if $p$ is outside the object, or $1$ if $p$ is inside.
+
+The complexity is $O(N_{P_I})$, where $N_{P_I}$ is the number of pixels in the image.
+
+With the run-length encoding of the binary objects, the complexity can be decreased
+to $O(N_{L_O})$, where $N_{L_O}$ is the number of lines in the object.
+
+\begin{eqnarray}
+S_{i,j} & = & \sum_{p \in D} \left( I(p).p_i.p_j \right) \\ \nonumber
+         & = & \sum_{p \in O} \left( p_i.p_j \right) \\ \nonumber
+         & = & \sum_{L \in O}  \sum_{p \in L} \left( p_i.p_j \right)
+\end{eqnarray}
+
+Where $O$ is a binary object in the image, and $L$ is a line of the object $O$, encoded
+with the run-length encoding. In a line, $p_i$ is a constant if $i > 0$, so, $S_{i,j}$
+can be written:
+
+\begin{eqnarray}
+S_{i,j} = \begin{cases}
+  \underset{L \in O}\sum \left( l_L.p_i.p_j \right)                & \text{if $i > 0$ and $j > 0$}, \\
+  \underset{L \in O}\sum \left( l_L.p_i.\underset{p \in L}\sum p_0 \right)  & \text{if $i > 0$ and $j = 0$}, \\
+  \underset{L \in O}\sum \left( l_L.p_j.\underset{p \in L}\sum p_0 \right)  & \text{if $i = 0$ and $j > 0$}, \\
+  \underset{L \in O}\sum \underset{p \in L}\sum p_0^2            & \text{if $i = j = 0$}.
+           \end{cases}
+\end{eqnarray}
+
+It is known that
+\begin{eqnarray}
+\label{equ:sumx}
+\sum_{x=0}^n x   & = & \frac{n(n+1)}{2} \\
+\label{equ:sumx2}
+\sum_{x=0}^n x^2 & = & \frac{n(n+1)(2n+1)}{6}
+\end{eqnarray}
+
+In order to use those formulae in the computation of $S_{i,j}$, the physical position has to be expanded in:
+\begin{eqnarray}
+\label{equ:expandedPosition}
+p_j = o_j + s_j i_j
+\end{eqnarray}
+where $o_j$ is the origin of the line on the axis $j$, $s_j$ is the spacing on the axis $j$, and
+$i_j$ is the index on the axis $j$.
+
+With equations \ref{equ:expandedPosition}, \ref{equ:sumx} and \ref{equ:sumx2}, it is easy to remove the loop in the computation of the sum of physical positions of the axis $0$:
+
+\begin{eqnarray}
+\sum_{p \in L} p_0  & = & \sum_{i_0=0}^{l_L-1} (o_0 + s_0 i_0) \\ \nonumber
+                    & = & l_L.o_0 + s_0\sum_{i_0=0}^{l_L-1} i_0 \\ \nonumber
+                    & = & l_L.o_0 + s_0\left( \frac{(l_L-1)l_L}{2} \right) \\ \nonumber
+                    & = & l_L \left( o_0 + \frac{s_0(l_L-1)}{2} \right)
+\end{eqnarray}
+
+where $l_L$ is the length of the line (in pixels), and in the sum of the square of the physical positions of the axis $0$:
+
+\begin{eqnarray}
+\sum_{p \in L} p_0^2  & = & \sum_{i_0=0}^{l_L-1} ( o_0 + s_0 i_0 )^2 \\ \nonumber
+                      & = & \sum_{i_0=0}^{l_L-1} ( o_0^2 + s_0^2 i_0^2 + 2 o_0 i_0) \\ \nonumber
+                      & = & l_L.o_0^2 + s_0^2\sum_{i_0=0}^{l_L-1} i_0^2 + 2 o_0 \sum_{i_0=0}^{l_L-1} i_0 \\ \nonumber
+                      & = & l_L.o_0^2 + s_0^2 \left( \frac{(l_L-1)l_L(2l_L-1)}{6} \right) + 2 o_0 \left( \frac{(l_L-1)l_L}{2} \right) \\ \nonumber
+                      & = & l_L\left( o_0^2 + (l_L-1)\left(\frac{s_0^2(2l_L-1)}{6}  + o_0 \right) \right)
+\end{eqnarray}
+
+Finally, $S_{i,j}$, used in the computation of the central moments, is computed as:
+\begin{eqnarray}
+S_{i,j} = \begin{cases}
+  \underset{L \in O}\sum \left( l_L.p_i.p_j \right)                & \text{if $i > 0$ and $j > 0$}, \\
+  \underset{L \in O}\sum \left( p_i.l_L^2 \left( o_0 + \frac{s_0(l_L-1)}{2} \right) \right) & \text{if $i > 0$ and $j = 0$}, \\
+  \underset{L \in O}\sum \left( p_j.l_L^2 \left( o_0 + \frac{s_0(l_L-1)}{2} \right) \right) & \text{if $i = 0$ and $j > 0$}, \\
+  \underset{L \in O}\sum \left( l_L\left( o_0^2 + (l_L-1)\left(\frac{s_0^2(2l_L-1)}{6}  + o_0 \right) \right) \right)            & \text{if $i = j = 0$}.
+           \end{cases}
+\end{eqnarray}
+
 \subsection{Roundness}
@@
 \begin{eqnarray}
-V_n(r) & = {\pi^\frac{n}{2}r^n\over\Gamma(\frac{n}{2} + 1)}
+\label{equ:hypersphereVolume}
+V_n(r) = \frac{\pi^\frac{n}{2}r^n}{\Gamma(\frac{n}{2} + 1)}
 \end{eqnarray}
@@
 
-$n!!$ is the double factorial, defined as
+$n!!$ is the {\em double factorial}, defined as:
 
@@
 \begin{eqnarray}
-A_n(r) & = {\frac{n V_n}{r}}
-\end{eqnarray}
-
-Where $A_n$ is the area of the hypersphere.
-
-\begin{eqnarray}
-R & = {\frac{a}{A_n(r)}}
-\end{eqnarray}
-
-where $R$ is the roundness, $a$ is the measured area of the object, and the $r$ is the radius of an hypersphere with the same volume than the object.
+A_n(r) = {\frac{n V_n}{r}}
+\end{eqnarray}
+
+where $A_n$ is the area of the hypersphere.
+
+\begin{eqnarray}
+R = {\frac{a}{A_n(r)}}
+\end{eqnarray}
+
+where $R$ is the roundness, $a$ is the measured area of the 
+object\footnote{More details about perimeter estimation will be published 
+in another article.}, and the $r$ is the radius of an hypersphere with the
+same volume than the object, computed using equation
+\ref{equ:hypersphereVolume}.
 

### 2007-08-30 itkShapeLabelCollectionImageFilter.h
perimeter and roundness attributes
darcs-hash:20070830153052-2fc9d-c530751e06bee8f0d8482e861c050092a03fc7ce.gz

@@ -16,8 +16,11 @@
 =========================================================================*/
 #ifndef __itkShapeLabelCollectionImageFilter_h
 #define __itkShapeLabelCollectionImageFilter_h
+#include "itkLabelPerimeterEstimationCalculator.h"
 
 #include "itkInPlaceLabelCollectionImageFilter.h"
+
+#define PI 3.14159265358979323846
 
 namespace itk {
 /** \class ShapeLabelCollectionImageFilter
@@ -70,6 +73,8 @@ public:
   itkStaticConstMacro(ImageDimension, unsigned int,
                       TImage::ImageDimension);
 
+  typedef LabelPerimeterEstimationCalculator< LabelImageType > PerimeterCalculatorType;
+
   /** Standard New method. */
   itkNewMacro(Self);  
 
@@ -107,11 +112,30 @@ public:
   itkBooleanMacro(ComputePerimeter);
 
 
-   /** Set the label image */
+  /** Set the label image */
   void SetLabelImage( const TLabelImage *input )
      {
      m_LabelImage = input;
      }
+
+  /** */
+  static long factorial( long n );
+
+  /** */
+  static long doubleFactorial( long n );
+
+  /** */
+  static double gammaN2p1( long n );
+
+  /** */
+  static double hyperSphereVolume( double radius );
+
+  /** */
+  static double hyperSphereArea( double radius );
+
+  /** */
+  static double hyperSphereRadiusFromVolume( double radius );
+
 
 protected:
   ShapeLabelCollectionImageFilter();
@@ -134,6 +158,8 @@ private:
   bool m_ComputePerimeter;
 
   LabelImageConstPointer m_LabelImage;
+
+  typename PerimeterCalculatorType::Pointer m_PerimeterCalculator;
 
 } ; // end of class
 

### 2007-08-30 itkShapeLabelObject.h

@@ -155,6 +155,32 @@ public:
     }
 };
 
+template< class TLabelObject >
+class ITK_EXPORT PerimeterLabelObjectAccessor
+{
+public:
+  typedef TLabelObject LabelObjectType;
+  typedef double AttributeValueType;
+
+  inline const AttributeValueType operator()( const LabelObjectType * labelObject )
+    {
+    return labelObject->GetPerimeter();
+    }
+};
+
+template< class TLabelObject >
+class ITK_EXPORT RoundnessLabelObjectAccessor
+{
+public:
+  typedef TLabelObject LabelObjectType;
+  typedef double AttributeValueType;
+
+  inline const AttributeValueType operator()( const LabelObjectType * labelObject )
+    {
+    return labelObject->GetRoundness();
+    }
+};
+
 }
 
 
@@ -210,6 +236,8 @@ public:
   static const AttributeType BINARY_PRINCIPAL_MOMENTS=8;
   static const AttributeType BINARY_PRINCIPAL_AXES=9;
   static const AttributeType BINARY_ELONGATION=10;
+  static const AttributeType PERIMETER=11;
+  static const AttributeType ROUNDNESS=12;
 
   static AttributeType GetAttributeFromName( const std::string & s )
     {
@@ -257,6 +285,14 @@ public:
       {
       return BINARY_ELONGATION;
       }
+    else if( s == "Perimeter" )
+      {
+      return PERIMETER;
+      }
+    else if( s == "Roundness" )
+      {
+      return ROUNDNESS;
+      }
     // can't recognize the namespace
     throw std::runtime_error("Unknown attribute.");
     }
@@ -296,6 +332,12 @@ public:
         break;
       case BINARY_ELONGATION:
         return "BinaryElongation";
+        break;
+      case PERIMETER:
+        return "Perimeter";
+        break;
+      case ROUNDNESS:
+        return "Roundness";
         break;
       }
       // can't recognize the namespace
@@ -442,6 +484,30 @@ public:
     m_BinaryElongation = v;
     }
 
+//   itkGetConstMacro( Perimeter, double );
+//   itkSetMacro( Perimeter, double );
+  const double & GetPerimeter() const
+    {
+    return m_Perimeter;
+    }
+
+  void SetPerimeter( const double & v )
+    {
+    m_Perimeter = v;
+    }
+
[…]

### 2007-08-31 article/Article.tex
perimeter and roundness attributes
darcs-hash:20070830153052-2fc9d-c530751e06bee8f0d8482e861c050092a03fc7ce.gz
add some doc
darcs-hash:20070831102836-2fc9d-c94e480bc3fbc4c3f4a327d7342b0d0c6f65c38f.gz

@@
   \item The {\em itk::LabelCollectionImageToMaskImageFilter} class can be used
-to mask an image with the objects of the {\em itk::LabelCollectionImage}.
+to mask an image with the objects of the {\em itk::LabelCollectionImage}. With
+that filter, the image can be cropped to contain only the masked zone, or the
+masked zone padded by a user defined number of pixels.
   \item Finally, {\em itk::LabelCollectionImageToAttributeImageFilter} produce
@@
 \begin{eqnarray}
-R = {\frac{a}{A_n(r)}}
+R = {\frac{A_n(r)}{a}}
 \end{eqnarray}
@@
 \ref{equ:hypersphereVolume}.
+
+\subsection{Pixel's neighborhood}
+
+The run-length encoding does not allow an easy access to the neighbors of a
+given pixel. If the neighborhood of all the pixels must be accessed, it is
+much easier to convert the {itk::LabelCollectionImage} to a {\em itk::Image}
+with the {\em itk::LabelCollectionImageToLabelImageFilter}, and use that
+image to access the neighbors. That's what is done in {\em itk::ShapeLabelCollectionImageFilter}
+to compute the maximum Feret diameter, and the perimeter estimation.
 
@@
 
+\subsection{The mask features}
+
+The {\em itk::LabelCollectionImageToMaskImageFilter} class let the user mask
+a part of an {\em itk::Image} with the objects of a {\em itk::LabelCollectionImage}.
+It can also crop the image to contain only the masked region.
+
+The source code is available in the file {\em mask.cxx}.
+
+First we include the headers of the class we will use, and parse the command line.
+
+\small \begin{verbatim}
+#include "itkImageFileReader.h"
+#include "itkImageFileWriter.h"
+#include "itkSimpleFilterWatcher.h"
+
+#include "itkLabelObject.h"
+#include "itkLabelCollectionImage.h"
+#include "itkLabelImageToLabelCollectionImageFilter.h"
+#include "itkLabelCollectionImageToMaskImageFilter.h"
+
+int main(int argc, char * argv[])
+{
+
+  if( argc != 9 )
+    {
+    std::cerr << "usage: " << argv[0] << " labelImage input output label bg neg crop cropBorder" << std::endl;
+    // std::cerr << "  : " << std::endl;
+    exit(1);
+    }
+\end{verbatim} \normalsize
+the filters are able to work in any dimension. Lets choose 3, so the program can be tested on
+2D and 2D image.
+\small \begin{verbatim}
+  const int dim = 3;
+\end{verbatim} \normalsize
+declare the input image type
+\small \begin{verbatim}
+  typedef itk::Image< unsigned char, dim > ImageType;
+\end{verbatim} \normalsize
+and the label object type to use. The input image is a label image, so the 
+type of the label can be the same type than the pixel type. itk::LabelObject is
+chosen, because only the mask feature is tested here, so we don't need any
+attribute.
+\small \begin{verbatim}
+  typedef itk::LabelObject< unsigned char, dim > LabelObjectType;
+  typedef itk::LabelCollectionImage< LabelObjectType > LabelCollectionImageType;
+\end{verbatim} \normalsize
+read the label image and the input image to be masked.
+\small \begin{verbatim}
+  typedef itk::ImageFileReader< ImageType > ReaderType;
+  ReaderType::Pointer reader = ReaderType::New();
+  reader->SetFileName( argv[1] );
+
+  ReaderType::Pointer reader2 = ReaderType::New();
+  reader2->SetFileName( argv[2] );
+\end{verbatim} \normalsize
+convert the label image to a label collection image.
+\small \begin{verbatim}
+  typedef itk::LabelImageToLabelCollectionImageFilter< ImageType, LabelCollectionImageType> I2LType;
+  I2LType::Pointer i2l = I2LType::New();
+  i2l->SetInput( reader->GetOutput() );
+  i2l->SetUseBackground( true );
+\end{verbatim} \normalsize
+then mask the image. Two inputs are required (the label collection image, and
+the image to be masked). The label used to mask the image is passed with the 
+{\em SetLabel()} method. The background in the output image, where the image is masked,
+is passed with {\em SetBackground()}. The user can choose to mask the image outside the
+label object (that's the default behavior), or inside the label object with the
+chosen label, by calling {\em SetNegated()}. Finally, the image can be cropped to the
+masked region, by calling {\em SetCrop(true)}, or to a region padded by a border, by
+calling both {\em SetCrop()} and {\em SetCropBorder()}. The crop border defaults to $0$, and the
+image is not cropped by default.
+\small \begin{verbatim}
+  typedef itk::LabelCollectionImageToMaskImageFilter< LabelCollectionImageType, ImageType > MaskType;
+  MaskType::Pointer mask = MaskType::New();
+  mask->SetInput( i2l->GetOutput() );
+  mask->SetFeatureImage( reader2->GetOutput() );
+  mask->SetLabel( atoi(argv[4]) );
+  mask->SetBackgroundValue( atoi(argv[5]) );
+  mask->SetNegated( atoi(argv[6]) );
+  mask->SetCrop( atoi(argv[7]) );
+  MaskType::SizeType border;
+  border.Fill( atoi(argv[8]) );
+  mask->SetCropBorder( border );
+  itk::SimpleFilterWatcher watcher6(mask, "filter");
+\end{verbatim} \normalsize
+Finally, save the output image.
+\small \begin{verbatim}
+  typedef itk::ImageFileWriter< ImageType > WriterType;
+  WriterType::Pointer writer = WriterType::New();
+  writer->SetInput( mask->GetOutput() );
+  writer->SetFileName( argv[3] );
+  writer->Update();
+
+  return 0;
+}
+\end{verbatim} \normalsize
+
 \section{Threading support}

### 2007-08-31 article/Article.tex
minor additions and fixes in the article
darcs-hash:20070831141458-2fc9d-d1b4a187f5f1cefe3af69e8f2d658c7c8a9ce48d.gz

@@
 to mask an image with the objects of the {\em itk::LabelCollectionImage}. With
-that filter, the image can be cropped to contain only the masked zone, or the
-masked zone padded by a user defined number of pixels.
+that filter, the image can be cropped to contain only the non-masked zone\footnote{
+The code used to produce the output region based on the content of the image
+is partially copied from a contribution of Peter Cech \url{http://www.vision.ee.ethz.ch/~pcech/itkAutoCropImageFilter/}.}
+, or the non-masked zone padded by a user defined number of pixels.
   \item Finally, {\em itk::LabelCollectionImageToAttributeImageFilter} produce
@@
 
-Doing that require a good knownledge of the iterator design. Any help on that point is
+Doing that require a good knowledge of the iterator design. Any help on that point is
 welcome.
 
-Also, more attributes will be implemented, like the perimeter estimation.
 It may be useful to implement the most commonly used opening, keep N objects and relabel transforms in a more efficient way, by using an {\em AttributeLabelObject} instead of a {\em ShapeLabelObject} or a {\em StatisticsLabelObject}.
 
-All the {\em Shape} filters are currently unable to use the Feret diameter.
-The feret diameter is not computed by default, and so always get a value of $0$.
-The computation of the Feret diameter should be forced if the user want to use it.
-
 The {\em BinaryImageToLabelCollectionImageFilter} class should be threaded to get the best of that filter on multiprocessors systems.
+
+The converters from/to image are provided, but it may be useful to  have the converters from/to other objects representations:
+\begin{itemize}
+  \item spatial objects,
+  \item meshs,
+  \item structuring elements.
+\end{itemize}
 

### 2007-09-11 article/Article.tex
add a python example
darcs-hash:20070911102055-2fc9d-09a2cd7b446050ae72f80c17d1394ae798113326.gz

@@
 
+\subsection{A full python example}
+
+In that example, we want to:
+\begin{itemize}
+\item find the nuclei in the first image
+\item find the spots insice the nucleus in the second image
+\item get the mean value in the nucleus, in the zone of each spot.
+\end{itemize}
+
+\begin{figure}[htbp]
+\begin{center}
+\subfigure[Nucleus]{\includegraphics[scale=0.45]{noyaux}}
+\subfigure[Spots]{\includegraphics[scale=0.45]{spots}}
+\caption{The input images.}
+\end{center}
+\end{figure}
+
+The source code is available in example.py.
+
+Lets begin with the usual {\em imports}.
+\small \begin{verbatim}
+import itk, sys
+itk.auto_progress()
+\end{verbatim} \normalsize
+Then declare the type we will use, as is {\em c++}.
+\small \begin{verbatim}
+Dimension = 2
+PixelType = itk.UC
+ImageType = itk.Image[ PixelType, Dimension ]
+
+DistancePixelType = itk.F
+DistanceImageType = itk.Image[ DistancePixelType, Dimension ]
+
+RGBPixelType = itk.RGBPixel[PixelType]
+RGBImageType = itk.Image[ RGBPixelType, Dimension ]
+
+LabelObjectType = itk.StatisticsLabelObject[itk.UL, Dimension]
+LabelCollectionImageType = itk.LabelCollectionImage[LabelObjectType]
+\end{verbatim} \normalsize
+read the image of the nucleus
+\small \begin{verbatim}
+nuclei = itk.ImageFileReader[ImageType].New(FileName="images/noyaux.png")
+\end{verbatim} \normalsize
+perform a simple binarization. Note that the Otsu filter does not use the same convention as usual: the white part is outside.
+\small \begin{verbatim}
+otsu = itk.OtsuThresholdImageFilter[ImageType, ImageType].New(nuclei,
+    OutsideValue=255, InsideValue=0)
+\end{verbatim} \normalsize
+The nuclei are not separated. We split them with a watershed.
+\small \begin{verbatim}
+maurer = itk.SignedMaurerDistanceMapImageFilter[ImageType, DistanceImageType].New(otsu)
+watershed = itk.MorphologicalWatershedImageFilter[DistanceImageType, ImageType].New(maurer,
+    Level=60, MarkWatershedLine=False)
+mask = itk.MaskImageFilter[ImageType, ImageType, ImageType].New(watershed, otsu)
+\end{verbatim} \normalsize
+And now switch to the label collection representation
+\small \begin{verbatim}
+label = itk.LabelImageToLabelCollectionImageFilter[ImageType, LabelCollectionImageType]
+    .New(mask)
+\end{verbatim} \normalsize
+compute the attribute values
+\small \begin{verbatim}
+stats = itk.StatisticsLabelCollectionImageFilter[LabelCollectionImageType, ImageType]
+    .New(label, nuclei)
+\end{verbatim} \normalsize
+drop the objects too small to be a nucleus, and the ones on the border
+\small \begin{verbatim}
+size = itk.ShapeOpeningLabelCollectionImageFilter[LabelCollectionImageType].New(stats,
+    Attribute='Size', Lambda=100)
+border = itk.ShapeOpeningLabelCollectionImageFilter[LabelCollectionImageType].New(size,
+    Attribute='SizeOnBorder', Lambda=10, ReverseOrdering=True)
+\end{verbatim} \normalsize
+Reoder the labels. The objects with the highest mean are the first ones.
+\small \begin{verbatim}
+relabel = itk.StatisticsRelabelLabelCollectionImageFilter[LabelCollectionImageType]
+    .New(border, Attribute='Mean')
+\end{verbatim} \normalsize
+for visual validation:
+\small \begin{verbatim}
+labelNuclei = itk.LabelCollectionImageToLabelImageFilter[LabelCollectionImageType,
+    ImageType].New(relabel)
+overlay = itk.LabelOverlayImageFilter[ImageType, ImageType, RGBImageType].New(nuclei,
+    labelNuclei, UseBackground=True)
+itk.write(overlay, "nuclei-overlay.png")
+\end{verbatim} \normalsize
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.45]{nuclei-overlay}
+\caption{The segmented nuclei. The too small objects and the ones on the border have been excluded.}
+\label{fig:overseg}
+\end{center}
+\end{figure}
+
+Now, the spots:
+\small \begin{verbatim}
+spots = itk.ImageFileReader[ImageType].New(FileName="images/spots.png")
+\end{verbatim} \normalsize
+Mask the spot image to keep only the nucleus zone. The rest of the image is cropped, excepted a border of 2 pixels
+\small \begin{verbatim}
+maskSpots = itk.LabelCollectionImageToMaskImageFilter.LI2IUC2.New(relabel, spots, Label=1,
+    Crop=True, CropBorder=2)
+\end{verbatim} \normalsize
+A simple thresholding:
+\small \begin{verbatim}
+th = itk.BinaryThresholdImageFilter[ImageType, ImageType].New(maskSpots, LowerThreshold=110)
+\end{verbatim} \normalsize
+Now swith to the label collection representation, and compute the attribute values. This time, the input image is not a label image, but a binary one.
+\small \begin{verbatim}
+slabel = itk.BinaryImageToLabelCollectionImageFilter[ImageType, LabelCollectionImageType]
+    .New(th)
+sstats = itk.StatisticsLabelCollectionImageFilter[LabelCollectionImageType, ImageType]
+    .New(slabel, nuclei)
+\end{verbatim} \normalsize
+we know there are for spots in the nubleus, so keep the 4 biggest spots. The other attribute are also usable - we may have chosen to keep the 4 brightest spots for example.
+\small \begin{verbatim}
+skeep = itk.ShapeKeepNObjectsLabelCollectionImageFilter[LabelCollectionImageType].New(
+    sstats, Attribute='Size', NumberOfObjects=4)
+\end{verbatim} \normalsize
+Reoder the labels. The bigger objects first.
+\small \begin{verbatim}
+srelabel = itk.StatisticsRelabelLabelCollectionImageFilter[LabelCollectionImageType].New(
+    skeep, Attribute='Size')
+\end{verbatim} \normalsize
+Finally, display the values we are interested in:
+\begin{itemize}
+  \item the nucleus number,
+  \item the spot position,
+  \item the mean value in the nucleus in the spot zone.
+\end{itemize}
+
+\small \begin{verbatim}
+print "nuclei", "x", "y", "mean"
+
+for nl in range(1, relabel.GetOutput().GetNumberOfObjects()+1):
+  maskSpots.SetLabel(nl)
+  srelabel.UpdateLargestPossibleRegion()
+  labeCollection = srelabel.GetOutput()
+
+  for l in range(1, labeCollection.GetNumberOfObjects()+1):
+    lo = labeCollection.GetLabelObject(l)
+    print nl, lo.GetCentroid()[0], lo.GetCentroid()[1], lo.GetMean()
+\end{verbatim} \normalsize
+
 \section{Threading support}

### 2007-09-11 example.py

@@ -1,0 +1,67 @@
+
+import itk, sys
+itk.auto_progress()
+
+Dimension = 2
+PixelType = itk.UC
+ImageType = itk.Image[ PixelType, Dimension ]
+
+DistancePixelType = itk.F
+DistanceImageType = itk.Image[ DistancePixelType, Dimension ]
+
+RGBPixelType = itk.RGBPixel[PixelType]
+RGBImageType = itk.Image[ RGBPixelType, Dimension ]
+
+LabelObjectType = itk.StatisticsLabelObject[itk.UL, Dimension]
+LabelCollectionImageType = itk.LabelCollectionImage[LabelObjectType]
+
+# read the image of the nucleus
+nuclei = itk.ImageFileReader[ImageType].New(FileName="images/noyaux.png")
+# perform a simple binarization. Note that the Otsu filter does not use the same convention as usual : the white part is outside.
+otsu = itk.OtsuThresholdImageFilter[ImageType, ImageType].New(nuclei, OutsideValue=255, InsideValue=0)
+# split the nuclei
+maurer = itk.SignedMaurerDistanceMapImageFilter[ImageType, DistanceImageType].New(otsu)
+watershed = itk.MorphologicalWatershedImageFilter[DistanceImageType, ImageType].New(maurer, Level=60, MarkWatershedLine=False)
+mask = itk.MaskImageFilter[ImageType, ImageType, ImageType].New(watershed, otsu)
+# now switch to the label collection representation
+label = itk.LabelImageToLabelCollectionImageFilter[ImageType, LabelCollectionImageType].New(mask)
+# compute the attribute values, including the perimeter and the Feret diameter
+stats = itk.StatisticsLabelCollectionImageFilter[LabelCollectionImageType, ImageType].New(label, nuclei, ComputePerimeter=True, ComputeFeretDiameter=True)
+# drop the objects too small to be a nucleus, and the ones on the border
+size = itk.ShapeOpeningLabelCollectionImageFilter[LabelCollectionImageType].New(stats, Attribute='Size', Lambda=100)
+border = itk.ShapeOpeningLabelCollectionImageFilter[LabelCollectionImageType].New(size, Attribute='SizeOnBorder', Lambda=10, ReverseOrdering=True)
+# reoder the labels. The objects with the highest mean are the first ones.
[…]

### 2007-09-11 article/Article.tex
hum, record the table
darcs-hash:20070911120623-2fc9d-8efb3bdb81b319778c05546ac19c987b3fca824f.gz
add some examples
darcs-hash:20070911160033-2fc9d-d51d9ffc4f04b087135ddeda32880cc6650524e8.gz

@@
 
+\begin{figure}[htbp]
+\begin{center}
+\subfigure[A label Image.]{\includegraphics[scale=0.7]{cthead1-label2}}
+\subfigure[The same image with colored labels]{\includegraphics[scale=.7]{cthead1-label2-rgb}}
+\caption{(a) the label image of connected components in Figure~\ref{fig:binaryImage}. (b) is the same image with labels colored with {\em itk::LabelToRGBImageFilter}.\label{fig:labelImage}}
+\end{center}
+\end{figure}
+
 \subsection{Binary image}
@@
 let us manipulate a single object in a labeled image.
+
+\begin{figure}[htbp]
+\begin{center}
+\subfigure[A simple binary image.]{\includegraphics[scale=0.7]{cthead1-bin}}
+\subfigure[A binary image, or a label image?]{\includegraphics[scale=.7]{2th_cthead1}}
+\caption{(a) is a simple binary image.
+Usually, the white pixel have the value 255, and the background the value 0.
+(b) contains 3 values (0, 100 and 200).
+The foreground value must be defined by the user, either 0, 100 or 200, and the values which are not the foreground are in the background.\label{fig:binaryImage}}
+\end{center}
+\end{figure}
 
@@
 
+\begin{figure}[htbp]
+\begin{center}
+\subfigure[A label image]{\includegraphics[scale=.7]{cthead1-label2-rgb}}
+\subfigure[All the objects smaller than 1000 pixels removed]{\includegraphics[scale=.7]{cthead1-label2-size-bigger-than-1000}}
+\subfigure[All the objects greater than 1000 pixels removed]{\includegraphics[scale=.7]{cthead1-label2-size-smaller-than-1000}}
+\subfigure[All the objects with roundness smaller than 0.8 removed]{\includegraphics[scale=.7]{cthead1-label2-roundness-greater-than-0_8}}
+\subfigure[All the objects with elongation smaller than 10 removed]{\includegraphics[scale=.7]{cthead1-label2-binaryElongation-greater-than-10}}
+\subfigure[All the objects with perimeter smaller than 100 removed]{\includegraphics[scale=.7]{cthead1-label2-perimeter-greater-than-100}}
+\caption{Some example of opening with different attribute and parameters.}
+\end{center}
+\end{figure}
+
 It can also be useful to simply get the attribute values associated with the
@@
 
+\begin{table}[phtb]
+\centering
+\small
+\begin{tabular}{cccc}
+\hline
+nucleus	& x	& y	& mean	\\
+\hline
+1	& 117.925925926	& 146.111111111	& 188.185185185	\\
+1	& 154.25	& 87.4166666667	& 126.416666667	\\
+1	& 107.666666667	& 155.125	& 122.0	\\
+1	& 95.2380952381	& 78.2857142857	& 121.0	\\
+2	& 417.631578947	& 158.736842105	& 132.894736842	\\
+2	& 431.277777778	& 177.388888889	& 131.222222222	\\
+2	& 390.117647059	& 207.588235294	& 96.8235294118	\\
+2	& 396.8		& 113.666666667	& 113.2	\\
+3	& 251.148148148	& 358.814814815	& 105.037037037	\\
+3	& 189.333333333	& 407.888888889	& 111.074074074	\\
+3	& 293.72	& 454.8		& 95.48	\\
+3	& 239.888888889	& 411.111111111	& 135.222222222	\\
+\hline
+\hline
+\end{tabular}
+\caption{Output of the python example.}
+\end{table}
+
 \section{Threading support}

### 2007-09-11 itkLabelPerimeterEstimationCalculator.h
fix bug when no perimter is computed for an object
darcs-hash:20070911160201-2fc9d-3296ca49f5549690ae11c71763f18a4391df4254.gz

@@ -80,7 +80,16 @@ public:
       {
       return m_Perimeters.find( label )->second;
       }
-    itkExceptionMacro( << "Unknown label" );
+    itkExceptionMacro( << "Unknown label: " << static_cast<typename NumericTraits<InputImagePixelType>::PrintType>(label) );
+    }
+
+  bool HasLabel( const InputImagePixelType & label ) const
+    {
+    if( m_Perimeters.find( label ) != m_Perimeters.end() )
+      {
+      return true;
+      }
+    return false;
     }
 
 protected:

### 2007-09-12 itkShapeLabelObject.h
implement affine transform creation from the principal axes
darcs-hash:20070912202205-2fc9d-ca6b60a19e65bd8aa099609e56f5f682d96e0f56.gz

@@ -18,6 +18,7 @@
 #define __itkShapeLabelObject_h
 
 #include "itkLabelObject.h"
+#include "itkAffineTransform.h"
 
 namespace itk
 {
@@ -507,6 +508,65 @@ public:
     {
     m_Roundness = v;
     }
+
+
+// some helper methods - not really required, but really useful!
+
+  /** Affine transform for mapping to and from principal axis */
+  typedef AffineTransform<double,itkGetStaticConstMacro(ImageDimension)> AffineTransformType;
+  typedef typename AffineTransformType::Pointer      AffineTransformPointer;
+
+  /** Get the affine transform from principal axes to physical axes
+   * This method returns an affine transform which transforms from
+   * the principal axes coordinate system to physical coordinates. */
+  AffineTransformPointer GetBinaryPrincipalAxesToPhysicalAxesTransform() const
+    {
+    typename AffineTransformType::MatrixType matrix;
+    typename AffineTransformType::OffsetType offset;
+    for (unsigned int i = 0; i < ImageDimension; i++) 
+      {
+      offset[i]  = m_Centroid[i];
+      for (unsigned int j = 0; j < ImageDimension; j++)
+        {
+        matrix[j][i] = m_BinaryPrincipalAxes[i][j];    // Note the transposition
+        }
+      }
+  
+    AffineTransformPointer result = AffineTransformType::New();
+      
+    result->SetMatrix(matrix);
+    result->SetOffset(offset);
+  
+    return result;
+    }
+
+  /** Get the affine transform from physical axes to principal axes
+   * This method returns an affine transform which transforms from
+   * the physical coordinate system to the principal axes coordinate
+   * system. */
+  AffineTransformPointer GetPhysicalAxesToBinaryPrincipalAxesTransform(void) const
+    {
+    typename AffineTransformType::MatrixType matrix;
+    typename AffineTransformType::OffsetType offset;
+    for (unsigned int i = 0; i < ImageDimension; i++) 
+      {
+      offset[i]    = m_Centroid[i];
+      for (unsigned int j = 0; j < ImageDimension; j++)
+        {
+        matrix[j][i] = m_BinaryPrincipalAxes[i][j];    // Note the transposition
+        }
+      }
+  
+    AffineTransformPointer result = AffineTransformType::New();
+    result->SetMatrix(matrix);
+    result->SetOffset(offset);
+  
+    AffineTransformPointer inverse = AffineTransformType::New();
[…]

### 2007-09-12 itkStatisticsLabelObject.h

@@ -648,6 +648,65 @@ public:
     }
 
 
+// some helper methods - not really required, but really useful!
+
+  /** Affine transform for mapping to and from principal axis */
+  typedef AffineTransform<double,itkGetStaticConstMacro(ImageDimension)> AffineTransformType;
+  typedef typename AffineTransformType::Pointer      AffineTransformPointer;
+
+  /** Get the affine transform from principal axes to physical axes
+   * This method returns an affine transform which transforms from
+   * the principal axes coordinate system to physical coordinates. */
+  AffineTransformPointer GetPrincipalAxesToPhysicalAxesTransform() const
+    {
+    typename AffineTransformType::MatrixType matrix;
+    typename AffineTransformType::OffsetType offset;
+    for (unsigned int i = 0; i < ImageDimension; i++) 
+      {
+      offset[i]  = m_CenterOfGravity[i];
+      for (unsigned int j = 0; j < ImageDimension; j++)
+        {
+        matrix[j][i] = m_PrincipalAxes[i][j];    // Note the transposition
+        }
+      }
+  
+    AffineTransformPointer result = AffineTransformType::New();
+      
+    result->SetMatrix(matrix);
+    result->SetOffset(offset);
+  
+    return result;
+    }
+
+  /** Get the affine transform from physical axes to principal axes
+   * This method returns an affine transform which transforms from
+   * the physical coordinate system to the principal axes coordinate
+   * system. */
+  AffineTransformPointer GetPhysicalAxesToPrincipalAxesTransform(void) const
+    {
+    typename AffineTransformType::MatrixType matrix;
+    typename AffineTransformType::OffsetType offset;
+    for (unsigned int i = 0; i < ImageDimension; i++) 
+      {
+      offset[i]    = m_CenterOfGravity[i];
+      for (unsigned int j = 0; j < ImageDimension; j++)
+        {
+        matrix[j][i] = m_PrincipalAxes[i][j];    // Note the transposition
+        }
+      }
+  
+    AffineTransformPointer result = AffineTransformType::New();
+    result->SetMatrix(matrix);
+    result->SetOffset(offset);
+  
+    AffineTransformPointer inverse = AffineTransformType::New();
+    result->GetInverse(inverse);
+  
+    return inverse;
+    }
+
+
+
 protected:
   StatisticsLabelObject()
     {

### 2007-09-18 article/Article.tex
add Maria in the acknowledgments, and remove migale for now
darcs-hash:20070912203235-2fc9d-8c8a8d48765fdee03155a8898fb8ed30625ffc60.gz
rename LabelCollectionImage in LabelMap, which is way shorter
darcs-hash:20070918081250-2fc9d-4181f5ccd4d87f2e902459e66c2764ca30b691e2.gz

@@
 
-\subsection{itk::LabelCollectionImage}
-
-The {\em itk::LabelCollectionImage} class is in charge of managing the
+\subsection{itk::LabelMap}
+
+The {\em itk::LabelMap} class is in charge of managing the
 collection of labeled
@@
 
-The {\em itk::LabelCollectionImage} provide a part of the API of the {\em
+The {\em itk::LabelMap} provide a part of the API of the {\em
 itk::Image} class, and so can be manipulated as an image\footnote{It doesn't
@@
 
-The {\em itk::LabelCollectionImage} is a templated class, which take a single
+The {\em itk::LabelMap} is a templated class, which take a single
 parameter: the type of {\em labeled object} stored by that class. The dimension
@@
 
-\subsection{Generating the itk::LabelCollectionImage}
-
-The {\em itk::LabelCollectionImage} class provide some methods to fill the
+\subsection{Generating the itk::LabelMap}
+
+The {\em itk::LabelMap} class provide some methods to fill the
 image "by hand", like the usual {\em SetPixel()} method. However, the most efficient way is to convert a labeled image or a binary
-image stored in an {\em itk::Image} to a {\em itk::LabelCollectionImage}, by
-using {\em itk::BinaryImageToLabelCollectionImageFilter} or {\em
-itk::LabelImageToLabelCollectionImageFilter}.
+image stored in an {\em itk::Image} to a {\em itk::LabelMap}, by
+using {\em itk::BinaryImageToLabelMapFilter} or {\em
+itk::LabelImageToLabelMapFilter}.
 
@@
 \begin{itemize}
-  \item {\em itk::ShapeLabelCollectionImageFilter} to fill the
+  \item {\em itk::ShapeLabelMapFilter} to fill the
 attributes of the {\em itk::ShapeLabelObject}s, 
-  \item and {\em itk::ShapeLabelCollectionImageFilter} to fill the attributes of the {\em
+  \item and {\em itk::ShapeLabelMapFilter} to fill the attributes of the {\em
 itk::StatisticsLabelObject}s.
@@
 other classes, the user must set the value by himself, for example by
-implementing a subclass of {\em itk::InPlaceLabelCollectionImageFilter}.
-
-\subsection{Manipulating the itk::LabelCollectionImage}
+implementing a subclass of {\em itk::InPlaceLabelMapFilter}.
+
+\subsection{Manipulating the itk::LabelMap}
 
 Once created and, optionally, valuated, several filters are provided to manipulate
-the {\em itk::LabelCollectionImage}:
+the {\em itk::LabelMap}:
 
@@
   \item An opening can be performed with the {\em
-OpeningLabelCollectionImageFilter} classes. Those classes will remove all the
+OpeningLabelMapFilter} classes. Those classes will remove all the
 objects with an attribute value lower or greater than a given value.
@@
   \item A fixed number of objects can be kept, with the {\em
-KeepNObjectsLabelCollectionImageFilter} classes. They are chosen according to
+KeepNObjectsLabelMapFilter} classes. They are chosen according to
 the value of their attribute. The user can choose to keep the ones with the
@@
   \item The objects can be relabel, with the {\em
-RelabelLabelCollectionImageFilter} classes. The order of the label is dependant
+RelabelLabelMapFilter} classes. The order of the label is dependant
 of the value of the attribute. Again, the user can choose to have the objects
@@
 
-\subsection{Generating an itk::Image from the itk::LabelCollectionImage}
+\subsection{Generating an itk::Image from the itk::LabelMap}
 
@@
 \begin{itemize}
-  \item The {\em itk::LabelCollectionImageToLabelImageFilter} class simply
-convert a {\em itk::LabelCollectionImage} to a labeled image stored in a {\em
+  \item The {\em itk::LabelMapToLabelImageFilter} class simply
+convert a {\em itk::LabelMap} to a labeled image stored in a {\em
 itk::Image}.
-  \item The {\em itk::LabelCollectionImageToBinaryImageFilter} put all the
+  \item The {\em itk::LabelMapToBinaryImageFilter} put all the
 objects in the foreground of a binary image stored in a {itk::Image}. It is
 intended to be used with an image produced by the {\em
-itk::BinaryImageToLabelCollectionImageFilter}. The background values of the
+itk::BinaryImageToLabelMapFilter}. The background values of the
 original image can also be restored by this filter.
-  \item The {\em itk::LabelCollectionImageToMaskImageFilter} class can be used
-to mask an image with the objects of the {\em itk::LabelCollectionImage}. With
+  \item The {\em itk::LabelMapToMaskImageFilter} class can be used
+to mask an image with the objects of the {\em itk::LabelMap}. With
 that filter, the image can be cropped to contain only the non-masked zone\footnote{
@@
 , or the non-masked zone padded by a user defined number of pixels.
-  \item Finally, {\em itk::LabelCollectionImageToAttributeImageFilter} produce
+  \item Finally, {\em itk::LabelMapToAttributeImageFilter} produce
 an {\em itk::Image} with the value of the attribute of the objects of the {\em
-itk::LabelCollectionImage}. This filter is mostly useful to have a global view
+itk::LabelMap}. This filter is mostly useful to have a global view
 of the attribute values in the image.
@@
 \begin{itemize}
-  \item creation of the {\em itk::LabelCollectionImage} from an {\em
+  \item creation of the {\em itk::LabelMap} from an {\em
 itk::Image},
   \item valuation of the attribute(s) of the objects,
-  \item filtering of the {\em itk::LabelCollectionImage},
+  \item filtering of the {\em itk::LabelMap},
   \item creation of an {\em itk::Image} from the filtered {\em
-itk::LabelCollectionImage},
+itk::LabelMap},
 \end{itemize}
@@
 given pixel. If the neighborhood of all the pixels must be accessed, it is
-much easier to convert the {itk::LabelCollectionImage} to a {\em itk::Image}
-with the {\em itk::LabelCollectionImageToLabelImageFilter}, and use that
-image to access the neighbors. That's what is done in {\em itk::ShapeLabelCollectionImageFilter}
+much easier to convert the {itk::LabelMap} to a {\em itk::Image}
+with the {\em itk::LabelMapToLabelImageFilter}, and use that
+image to access the neighbors. That's what is done in {\em itk::ShapeLabelMapFilter}
 to compute the maximum Feret diameter, and the perimeter estimation.
@@
 #include "itkLabelObject.h"
-#include "itkLabelCollectionImage.h"
+#include "itkLabelMap.h"
 #include "itkBinaryFillholeImageFilter.h"
@@
 
-\subsection{LabelObject and LabelCollectionImage manipulation}
+\subsection{LabelObject and LabelMap manipulation}
 
@@
 #include "itkAttributeLabelObject.h"
-#include "itkLabelCollectionImage.h"
-
-#include "itkLabelImageToLabelCollectionImageFilter.h"
-
-#include "itkAttributeKeepNObjectsLabelCollectionImageFilter.h"
-#include "itkAttributeOpeningLabelCollectionImageFilter.h"
-#include "itkAttributeRelabelLabelCollectionImageFilter.h"
-
-#include "itkLabelCollectionImageToAttributeImageFilter.h"
-#include "itkLabelCollectionImageToLabelImageFilter.h"
+#include "itkLabelMap.h"
+
+#include "itkLabelImageToLabelMapFilter.h"
+
+#include "itkAttributeKeepNObjectsLabelMapFilter.h"
+#include "itkAttributeOpeningLabelMapFilter.h"
+#include "itkAttributeRelabelLabelMapFilter.h"
+
+#include "itkLabelMapToAttributeImageFilter.h"
+#include "itkLabelMapToLabelImageFilter.h"
 
@@
 with each node. Here we have chosen a double. We then declares the
-type of the LabelCollectionImage with the type of the label object.
+type of the LabelMap with the type of the label object.
 \small \begin{verbatim}
   typedef itk::AttributeLabelObject< unsigned long, dim, double > LOType;
-  typedef itk::LabelCollectionImage< LOType > LCIType;
+  typedef itk::LabelMap< LOType > LCIType;
 \end{verbatim} \normalsize
@@
 \end{verbatim} \normalsize
-And convert the label image to a LabelCollectionImage.
-\small \begin{verbatim}
-  typedef itk::LabelImageToLabelCollectionImageFilter< IType, LCIType > I2LType;
+And convert the label image to a LabelMap.
+\small \begin{verbatim}
+  typedef itk::LabelImageToLabelMapFilter< IType, LCIType > I2LType;
   I2LType::Pointer i2l = I2LType::New();
@@
 \small \begin{verbatim}
-  typedef itk::AttributeKeepNObjectsLabelCollectionImageFilter< LCIType > KeepType;
+  typedef itk::AttributeKeepNObjectsLabelMapFilter< LCIType > KeepType;
   KeepType::Pointer keep = KeepType::New();
@@
 
-  typedef itk::AttributeOpeningLabelCollectionImageFilter< LCIType > OpeningType;
+  typedef itk::AttributeOpeningLabelMapFilter< LCIType > OpeningType;
   OpeningType::Pointer opening = OpeningType::New();
@@
 
-  typedef itk::AttributeRelabelLabelCollectionImageFilter< LCIType > RelabelType;
+  typedef itk::AttributeRelabelLabelMapFilter< LCIType > RelabelType;
   RelabelType::Pointer relabel = RelabelType::New();
@@
 \small \begin{verbatim}
-  typedef itk::LabelCollectionImageToAttributeImageFilter< LCIType, IType > A2IType;
+  typedef itk::LabelMapToAttributeImageFilter< LCIType, IType > A2IType;
   A2IType::Pointer a2i = A2IType::New();
@@
 \small \begin{verbatim}
-  typedef itk::LabelCollectionImageToLabelImageFilter< LCIType, IType > L2IType;
+  typedef itk::LabelMapToLabelImageFilter< LCIType, IType > L2IType;
   L2IType::Pointer l2i = L2IType::New();
@@
 #include "itkShapeLabelObject.h"
-#include "itkLabelCollectionImage.h"
-#include "itkBinaryImageToLabelCollectionImageFilter.h"
-#include "itkShapeLabelCollectionImageFilter.h"
+#include "itkLabelMap.h"
+#include "itkBinaryImageToLabelMapFilter.h"
+#include "itkShapeLabelMapFilter.h"
 
@@
   typedef itk::ShapeLabelObject< LabelType, dim > LabelObjectType;
-  typedef itk::LabelCollectionImage< LabelObjectType > LabelCollectionType;
+  typedef itk::LabelMap< LabelObjectType > LabelCollectionType;
 
@@
 \small \begin{verbatim}
-  typedef itk::BinaryImageToLabelCollectionImageFilter< ImageType, LabelCollectionType > ConverterType;
+  typedef itk::BinaryImageToLabelMapFilter< ImageType, LabelCollectionType > ConverterType;
   ConverterType::Pointer converter = ConverterType::New();
@@
 \end{verbatim} \normalsize
-and valuate the attributes with the dedicated filter: ShapeLabelCollectionImageFilter
-\small \begin{verbatim}
-  typedef itk::ShapeLabelCollectionImageFilter< LabelCollectionType > ShapeFilterType;
+and valuate the attributes with the dedicated filter: ShapeLabelMapFilter
+\small \begin{verbatim}
+  typedef itk::ShapeLabelMapFilter< LabelCollectionType > ShapeFilterType;
   ShapeFilterType::Pointer shape = ShapeFilterType::New();
@@
 \end{verbatim} \normalsize
-then we can read the attribute values we're interested in. {\em BinaryImageToLabelCollectionImageFilter}
+then we can read the attribute values we're interested in. {\em BinaryImageToLabelMapFilter}
 produces consecutives labels, so a simple {for} loop will do the job.
@@
 
-The {\em itk::LabelCollectionImageToMaskImageFilter} class let the user mask
-a part of an {\em itk::Image} with the objects of a {\em itk::LabelCollectionImage}.
+The {\em itk::LabelMapToMaskImageFilter} class let the user mask
+a part of an {\em itk::Image} with the objects of a {\em itk::LabelMap}.
 It can also crop the image to contain only the masked region.
@@
 #include "itkLabelObject.h"
-#include "itkLabelCollectionImage.h"
-#include "itkLabelImageToLabelCollectionImageFilter.h"
-#include "itkLabelCollectionImageToMaskImageFilter.h"
+#include "itkLabelMap.h"
+#include "itkLabelImageToLabelMapFilter.h"
+#include "itkLabelMapToMaskImageFilter.h"
 
@@
   typedef itk::LabelObject< unsigned char, dim > LabelObjectType;
-  typedef itk::LabelCollectionImage< LabelObjectType > LabelCollectionImageType;
+  typedef itk::LabelMap< LabelObjectType > LabelMapType;
 \end{verbatim} \normalsize
@@
 \small \begin{verbatim}
-  typedef itk::LabelImageToLabelCollectionImageFilter< ImageType, LabelCollectionImageType> I2LType;
+  typedef itk::LabelImageToLabelMapFilter< ImageType, LabelMapType> I2LType;
   I2LType::Pointer i2l = I2LType::New();
@@
 \small \begin{verbatim}
-  typedef itk::LabelCollectionImageToMaskImageFilter< LabelCollectionImageType, ImageType > MaskType;
+  typedef itk::LabelMapToMaskImageFilter< LabelMapType, ImageType > MaskType;
   MaskType::Pointer mask = MaskType::New();
@@
 LabelObjectType = itk.StatisticsLabelObject[itk.UL, Dimension]
-LabelCollectionImageType = itk.LabelCollectionImage[LabelObjectType]
+LabelMapType = itk.LabelMap[LabelObjectType]
 \end{verbatim} \normalsize
@@
 \small \begin{verbatim}
-label = itk.LabelImageToLabelCollectionImageFilter[ImageType, LabelCollectionImageType]
+label = itk.LabelImageToLabelMapFilter[ImageType, LabelMapType]
     .New(mask)
@@
 \small \begin{verbatim}
-stats = itk.StatisticsLabelCollectionImageFilter[LabelCollectionImageType, ImageType]
+stats = itk.StatisticsLabelMapFilter[LabelMapType, ImageType]
     .New(label, nuclei)
@@
 \small \begin{verbatim}
-size = itk.ShapeOpeningLabelCollectionImageFilter[LabelCollectionImageType].New(stats,
+size = itk.ShapeOpeningLabelMapFilter[LabelMapType].New(stats,
     Attribute='Size', Lambda=100)
-border = itk.ShapeOpeningLabelCollectionImageFilter[LabelCollectionImageType].New(size,
+border = itk.ShapeOpeningLabelMapFilter[LabelMapType].New(size,
     Attribute='SizeOnBorder', Lambda=10, ReverseOrdering=True)
@@
 \small \begin{verbatim}
-relabel = itk.StatisticsRelabelLabelCollectionImageFilter[LabelCollectionImageType]
+relabel = itk.StatisticsRelabelLabelMapFilter[LabelMapType]
     .New(border, Attribute='Mean')
@@
 \small \begin{verbatim}
-labelNuclei = itk.LabelCollectionImageToLabelImageFilter[LabelCollectionImageType,
+labelNuclei = itk.LabelMapToLabelImageFilter[LabelMapType,
     ImageType].New(relabel)
@@
 \small \begin{verbatim}
-maskSpots = itk.LabelCollectionImageToMaskImageFilter.LI2IUC2.New(relabel, spots, Label=1,
+maskSpots = itk.LabelMapToMaskImageFilter.LI2IUC2.New(relabel, spots, Label=1,
     Crop=True, CropBorder=2)
@@
 \small \begin{verbatim}
-slabel = itk.BinaryImageToLabelCollectionImageFilter[ImageType, LabelCollectionImageType]
+slabel = itk.BinaryImageToLabelMapFilter[ImageType, LabelMapType]
     .New(th)
-sstats = itk.StatisticsLabelCollectionImageFilter[LabelCollectionImageType, ImageType]
+sstats = itk.StatisticsLabelMapFilter[LabelMapType, ImageType]
     .New(slabel, nuclei)
@@
 \small \begin{verbatim}
-skeep = itk.ShapeKeepNObjectsLabelCollectionImageFilter[LabelCollectionImageType].New(
+skeep = itk.ShapeKeepNObjectsLabelMapFilter[LabelMapType].New(
     sstats, Attribute='Size', NumberOfObjects=4)
@@
 \small \begin{verbatim}
-srelabel = itk.StatisticsRelabelLabelCollectionImageFilter[LabelCollectionImageType].New(
+srelabel = itk.StatisticsRelabelLabelMapFilter[LabelMapType].New(
     skeep, Attribute='Size')
@@
 
-The {\em BinaryImageToLabelCollectionImageFilter} class is a slight modification of the
+The {\em BinaryImageToLabelMapFilter} class is a slight modification of the
 Richard Beare's {\em ConnectedComponentImageFilter}, and thus, has not been threaded.
@@
 
-Because the {\em LabelCollectionImage} image is not an array of pixels, it can't be splitted
+Because the {\em LabelMap} image is not an array of pixels, it can't be splitted
 that way. Instead, several threads are created, and try to take an object in the collection.
@@
 For the developer, the usage of the threading support is made very simple, by subclassing
-{\em LabelCollectionImageFilter}, or {\em InPlaceLabelCollectionImageFilter}, and implementing
+{\em LabelMapFilter}, or {\em InPlaceLabelMapFilter}, and implementing
 the method {\em virtual void ThreadedGenerateData( LabelObjectType * labelObject )} in the
@@
 
-All the filters which are taking a {\em LabelCollectionImage} as input, and are producing a {\em LabelCollectionImage} as output, are implemented as a subclass of {\em InPlaceLabelCollectionImageFilter} and
+All the filters which are taking a {\em LabelMap} as input, and are producing a {\em LabelMap} as output, are implemented as a subclass of {\em InPlaceLabelMapFilter} and
 thus are running in place by default.
@@
 
-To use that feature, a developer only have to subclass {\em InPlaceLabelCollectionImageFilter} and
+To use that feature, a developer only have to subclass {\em InPlaceLabelMapFilter} and
 implement the {\em virtual void ThreadedGenerateData( LabelObjectType * labelObject )}, to get easy thread
@@
 
-The {\em BinaryImageToLabelCollectionImageFilter} class should be threaded to get the best of that filter on multiprocessors systems.
+The {\em BinaryImageToLabelMapFilter} class should be threaded to get the best of that filter on multiprocessors systems.
 
@@
 (\url{http://mima2.jouy.inra.fr}) for providing the 3D test image.
-I am grateful to the INRA MIGALE bioinformatics platform
-(\url{http://migale.jouy.inra.fr}) for providing the computational resources
-used for the timing tests.
+% I am grateful to the INRA MIGALE bioinformatics platform
+% (\url{http://migale.jouy.inra.fr}) for providing the computational resources
+% used for the timing tests.
+I thank Dr Maria Ballester for providing the image used in the python example.
 

### 2007-09-18 example.py

@@ -13,7 +13,7 @@ RGBPixelType = itk.RGBPixel[PixelType]
 RGBImageType = itk.Image[ RGBPixelType, Dimension ]
 
 LabelObjectType = itk.StatisticsLabelObject[itk.UL, Dimension]
-LabelCollectionImageType = itk.LabelCollectionImage[LabelObjectType]
+LabelMapType = itk.LabelMap[LabelObjectType]
 
 # read the image of the nucleus
 nuclei = itk.ImageFileReader[ImageType].New(FileName="images/noyaux.png")
@@ -24,30 +24,30 @@ maurer = itk.SignedMaurerDistanceMapImageFilter[ImageType, DistanceImageType].Ne
 watershed = itk.MorphologicalWatershedImageFilter[DistanceImageType, ImageType].New(maurer, Level=60, MarkWatershedLine=False)
 mask = itk.MaskImageFilter[ImageType, ImageType, ImageType].New(watershed, otsu)
 # now switch to the label collection representation
-label = itk.LabelImageToLabelCollectionImageFilter[ImageType, LabelCollectionImageType].New(mask)
+label = itk.LabelImageToLabelMapFilter[ImageType, LabelMapType].New(mask)
 # compute the attribute values, including the perimeter and the Feret diameter
-stats = itk.StatisticsLabelCollectionImageFilter[LabelCollectionImageType, ImageType].New(label, nuclei, ComputePerimeter=True, ComputeFeretDiameter=True)
+stats = itk.StatisticsLabelMapFilter[LabelMapType, ImageType].New(label, nuclei, ComputePerimeter=True, ComputeFeretDiameter=True)
 # drop the objects too small to be a nucleus, and the ones on the border
-size = itk.ShapeOpeningLabelCollectionImageFilter[LabelCollectionImageType].New(stats, Attribute='Size', Lambda=100)
-border = itk.ShapeOpeningLabelCollectionImageFilter[LabelCollectionImageType].New(size, Attribute='SizeOnBorder', Lambda=10, ReverseOrdering=True)
+size = itk.ShapeOpeningLabelMapFilter[LabelMapType].New(stats, Attribute='Size', Lambda=100)
+border = itk.ShapeOpeningLabelMapFilter[LabelMapType].New(size, Attribute='SizeOnBorder', Lambda=10, ReverseOrdering=True)
 # reoder the labels. The objects with the highest mean are the first ones.
[…]

### 2007-09-18 itkAttributeKeepNObjectsLabelCollectionImageFilter.h

@@ -1,141 +1,0 @@
-/*=========================================================================
-
-  Program:   Insight Segmentation & Registration Toolkit
-  Module:    $RCSfile: itkAttributeKeepNObjectsLabelCollectionImageFilter.h,v $
-  Language:  C++
-  Date:      $Date: 2006/03/28 19:59:05 $
-  Version:   $Revision: 1.6 $
-
-  Copyright (c) Insight Software Consortium. All rights reserved.
-  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
-
-     This software is distributed WITHOUT ANY WARRANTY; without even 
-     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
-     PURPOSE.  See the above copyright notices for more information.
-
-=========================================================================*/
-#ifndef __itkAttributeKeepNObjectsLabelCollectionImageFilter_h
-#define __itkAttributeKeepNObjectsLabelCollectionImageFilter_h
-
-#include "itkInPlaceLabelCollectionImageFilter.h"
-#include "itkAttributeLabelObject.h"
-
-namespace itk {
-/** \class AttributeKeepNObjectsLabelCollectionImageFilter
- * \brief keep N objects according to their attribute
- *
- * AttributeKeepNObjectsLabelCollectionImageFilter keep the N objects in a label collection image
- * with the highest (or lowest) attribute value. The attribute is provide by an
- * attribute accessor given in template parameter.
- *
- * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
- *
- * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
- */
-template<class TImage, class TAttributeAccessor=
-    typename Functor::AttributeLabelObjectAccessor< typename TImage::LabelObjectType > >
-class ITK_EXPORT AttributeKeepNObjectsLabelCollectionImageFilter : 
-    public InPlaceLabelCollectionImageFilter<TImage>
-{
-public:
-  /** Standard class typedefs. */
-  typedef AttributeKeepNObjectsLabelCollectionImageFilter Self;
-  typedef InPlaceLabelCollectionImageFilter<TImage>
-  Superclass;
-  typedef SmartPointer<Self>        Pointer;
-  typedef SmartPointer<const Self>  ConstPointer;
-
-  /** Some convenient typedefs. */
[…]

### 2007-09-18 itkAttributeLabelObject.h

@@ -67,7 +67,7 @@ public:
   /** Run-time type information (and related methods). */
   itkTypeMacro(AttributeLabelObject, LabelObject);
 
-  typedef LabelCollectionImage< Self > LabelCollectionImageType;
+  typedef LabelMap< Self > LabelMapType;
 
   itkStaticConstMacro(ImageDimension, unsigned int, VImageDimension);
 

### 2007-09-18 itkAttributeOpeningLabelCollectionImageFilter.h

@@ -1,122 +1,0 @@
-/*=========================================================================
-
-  Program:   Insight Segmentation & Registration Toolkit
-  Module:    $RCSfile: itkAttributeOpeningLabelCollectionImageFilter.h,v $
-  Language:  C++
-  Date:      $Date: 2006/03/28 19:59:05 $
-  Version:   $Revision: 1.6 $
-
-  Copyright (c) Insight Software Consortium. All rights reserved.
-  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
-
-     This software is distributed WITHOUT ANY WARRANTY; without even 
-     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
-     PURPOSE.  See the above copyright notices for more information.
-
-=========================================================================*/
-#ifndef __itkAttributeOpeningLabelCollectionImageFilter_h
-#define __itkAttributeOpeningLabelCollectionImageFilter_h
-
-#include "itkInPlaceLabelCollectionImageFilter.h"
-#include "itkAttributeLabelObject.h"
-
-namespace itk {
-/** \class AttributeOpeningLabelCollectionImageFilter
- * \brief remove the objects according to the value of their attribute
- *
- * AttributeOpeningLabelCollectionImageFilter removes the objects in a label collection image
- * with an attribute value smaller or greater than a threshold called Lambda.
- * The attribute is provide by an attribute accessor given in template parameter.
- *
- * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
- *
- * \sa AttributeLabelObject
- * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
- */
-template<class TImage, class TAttributeAccessor=
-    typename Functor::AttributeLabelObjectAccessor< typename TImage::LabelObjectType > >
-class ITK_EXPORT AttributeOpeningLabelCollectionImageFilter : 
-    public InPlaceLabelCollectionImageFilter<TImage>
-{
-public:
-  /** Standard class typedefs. */
-  typedef AttributeOpeningLabelCollectionImageFilter Self;
-  typedef InPlaceLabelCollectionImageFilter<TImage>
-  Superclass;
-  typedef SmartPointer<Self>        Pointer;
-  typedef SmartPointer<const Self>  ConstPointer;
-
[…]

### 2007-09-18 itkAttributeRelabelImageFilter.h

@@ -18,10 +18,10 @@
 #define __itkAttributeRelabelImageFilter_h
 
 #include "itkImageToImageFilter.h"
-#include "itkLabelCollectionImage.h"
-#include "itkLabelImageToLabelCollectionImageFilter.h"
-#include "itkAttributeRelabelLabelCollectionImageFilter.h"
-#include "itkLabelCollectionImageToLabelImageFilter.h"
+#include "itkLabelMap.h"
+#include "itkLabelImageToLabelMapFilter.h"
+#include "itkAttributeRelabelLabelMapFilter.h"
+#include "itkLabelMapToLabelImageFilter.h"
 #include "itkAttributeLabelObject.h"
 
 
@@ -72,13 +72,13 @@ public:
                       TInputImage::ImageDimension);
 
   typedef TLabelObject LabelObjectType;
-  typedef typename itk::LabelCollectionImage< LabelObjectType > LabelCollectionImageType;
-  typedef typename itk::LabelImageToLabelCollectionImageFilter< InputImageType, LabelCollectionImageType > LabelizerType;
+  typedef typename itk::LabelMap< LabelObjectType > LabelMapType;
+  typedef typename itk::LabelImageToLabelMapFilter< InputImageType, LabelMapType > LabelizerType;
   typedef TLabelObjectValuator LabelObjectValuatorType;
   typedef TAttributeAccessor AttributeAccessorType;
   typedef typename AttributeAccessorType::AttributeValueType AttributeValueType;
-  typedef typename itk::AttributeRelabelLabelCollectionImageFilter< LabelCollectionImageType, AttributeAccessorType > RelabelType;
-  typedef typename itk::LabelCollectionImageToLabelImageFilter< LabelCollectionImageType, OutputImageType > BinarizerType;
+  typedef typename itk::AttributeRelabelLabelMapFilter< LabelMapType, AttributeAccessorType > RelabelType;
+  typedef typename itk::LabelMapToLabelImageFilter< LabelMapType, OutputImageType > BinarizerType;
 
   /** Standard New method. */
   itkNewMacro(Self);  

### 2007-09-18 itkAttributeRelabelLabelCollectionImageFilter.h

@@ -1,135 +1,0 @@
-/*=========================================================================
-
-  Program:   Insight Segmentation & Registration Toolkit
-  Module:    $RCSfile: itkAttributeRelabelLabelCollectionImageFilter.h,v $
-  Language:  C++
-  Date:      $Date: 2006/03/28 19:59:05 $
-  Version:   $Revision: 1.6 $
-
-  Copyright (c) Insight Software Consortium. All rights reserved.
-  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
-
-     This software is distributed WITHOUT ANY WARRANTY; without even 
-     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
-     PURPOSE.  See the above copyright notices for more information.
-
-=========================================================================*/
-#ifndef __itkAttributeRelabelLabelCollectionImageFilter_h
-#define __itkAttributeRelabelLabelCollectionImageFilter_h
-
-#include "itkInPlaceLabelCollectionImageFilter.h"
-#include "itkAttributeLabelObject.h"
-
-namespace itk {
-/** \class AttributeRelabelLabelCollectionImageFilter
- * \brief relabel objects according to their shape attributes
- *
- * AttributeRelabelLabelCollectionImageFilter relabel a label collection image according to the
- * attribute of the objects.
- * The attribute is provide by an attribute accessor given in template parameter.
- *
- * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
- *
- * \sa AttributeLabelObject, RelabelComponentImageFilter
- * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
- */
-template<class TImage, class TAttributeAccessor=
-    typename Functor::AttributeLabelObjectAccessor< typename TImage::LabelObjectType > >
-class ITK_EXPORT AttributeRelabelLabelCollectionImageFilter : 
-    public InPlaceLabelCollectionImageFilter<TImage>
-{
-public:
-  /** Standard class typedefs. */
-  typedef AttributeRelabelLabelCollectionImageFilter Self;
-  typedef InPlaceLabelCollectionImageFilter<TImage>
-  Superclass;
-  typedef SmartPointer<Self>        Pointer;
-  typedef SmartPointer<const Self>  ConstPointer;
-
-  /** Some convenient typedefs. */
[…]

### 2007-09-18 itkBinaryAttributeKeepNObjectsImageFilter.h

@@ -18,10 +18,10 @@
 #define __itkBinaryAttributeKeepNObjectsImageFilter_h
 
 #include "itkImageToImageFilter.h"
-#include "itkLabelCollectionImage.h"
-#include "itkBinaryImageToLabelCollectionImageFilter.h"
-#include "itkAttributeKeepNObjectsLabelCollectionImageFilter.h"
-#include "itkLabelCollectionImageToBinaryImageFilter.h"
+#include "itkLabelMap.h"
+#include "itkBinaryImageToLabelMapFilter.h"
+#include "itkAttributeKeepNObjectsLabelMapFilter.h"
+#include "itkLabelMapToBinaryImageFilter.h"
 #include "itkAttributeLabelObject.h"
 
 
@@ -40,7 +40,7 @@ namespace itk {
  *
  * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
  *
- * \sa AttributeLabelObject, InPlaceLabelCollectionImageFilter
+ * \sa AttributeLabelObject, InPlaceLabelMapFilter
  * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
  */
 template<class TInputImage, class TLabelObject, class TLabelObjectValuator, class TAttributeAccessor=
@@ -77,13 +77,13 @@ public:
                       TInputImage::ImageDimension);
 
   typedef TLabelObject LabelObjectType;
-  typedef typename itk::LabelCollectionImage< LabelObjectType > LabelCollectionImageType;
-  typedef typename itk::BinaryImageToLabelCollectionImageFilter< InputImageType, LabelCollectionImageType > LabelizerType;
+  typedef typename itk::LabelMap< LabelObjectType > LabelMapType;
+  typedef typename itk::BinaryImageToLabelMapFilter< InputImageType, LabelMapType > LabelizerType;
   typedef TLabelObjectValuator LabelObjectValuatorType;
   typedef TAttributeAccessor AttributeAccessorType;
   typedef typename AttributeAccessorType::AttributeValueType AttributeValueType;
-  typedef typename itk::AttributeKeepNObjectsLabelCollectionImageFilter< LabelCollectionImageType, AttributeAccessorType > KeepNObjectsType;
-  typedef typename itk::LabelCollectionImageToBinaryImageFilter< LabelCollectionImageType, OutputImageType > BinarizerType;
[…]

### 2007-09-18 itkBinaryAttributeOpeningImageFilter.h

@@ -18,10 +18,10 @@
 #define __itkBinaryAttributeOpeningImageFilter_h
 
 #include "itkImageToImageFilter.h"
-#include "itkLabelCollectionImage.h"
-#include "itkBinaryImageToLabelCollectionImageFilter.h"
-#include "itkAttributeOpeningLabelCollectionImageFilter.h"
-#include "itkLabelCollectionImageToBinaryImageFilter.h"
+#include "itkLabelMap.h"
+#include "itkBinaryImageToLabelMapFilter.h"
+#include "itkAttributeOpeningLabelMapFilter.h"
+#include "itkLabelMapToBinaryImageFilter.h"
 #include "itkAttributeLabelObject.h"
 
 
@@ -41,7 +41,7 @@ namespace itk {
  *
  * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
  *
- * \sa AttributeLabelObject, InPlaceLabelCollectionImageFilter
+ * \sa AttributeLabelObject, InPlaceLabelMapFilter
  * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
  */
 template<class TInputImage, class TLabelObject, class TLabelObjectValuator, class TAttributeAccessor=
@@ -78,13 +78,13 @@ public:
                       TInputImage::ImageDimension);
 
   typedef TLabelObject LabelObjectType;
-  typedef typename itk::LabelCollectionImage< LabelObjectType > LabelCollectionImageType;
-  typedef typename itk::BinaryImageToLabelCollectionImageFilter< InputImageType, LabelCollectionImageType > LabelizerType;
+  typedef typename itk::LabelMap< LabelObjectType > LabelMapType;
+  typedef typename itk::BinaryImageToLabelMapFilter< InputImageType, LabelMapType > LabelizerType;
   typedef TLabelObjectValuator LabelObjectValuatorType;
   typedef TAttributeAccessor AttributeAccessorType;
   typedef typename AttributeAccessorType::AttributeValueType AttributeValueType;
-  typedef typename itk::AttributeOpeningLabelCollectionImageFilter< LabelCollectionImageType, AttributeAccessorType > OpeningType;
-  typedef typename itk::LabelCollectionImageToBinaryImageFilter< LabelCollectionImageType, OutputImageType > BinarizerType;
[…]

### 2007-09-18 itkBinaryImageToLabelCollectionImageFilter.h

@@ -1,236 +1,0 @@
-/*=========================================================================
-
-  Program:   Insight Segmentation & Registration Toolkit
-  Module:    $RCSfile: itkBinaryImageToLabelCollectionImageFilter.h,v $
-  Language:  C++
-  Date:      $Date: 2007/02/18 20:03:03 $
-  Version:   $Revision: 1.16 $
-
-  Copyright (c) Insight Software Consortium. All rights reserved.
-  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
-
-     This software is distributed WITHOUT ANY WARRANTY; without even 
-     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
-     PURPOSE.  See the above copyright notices for more information.
-
-=========================================================================*/
-
-#ifndef __itkBinaryImageToLabelCollectionImageFilter_h
-#define __itkBinaryImageToLabelCollectionImageFilter_h
-
-#include "itkImageToImageFilter.h"
-#include "itkImage.h"
-#include "itkConceptChecking.h"
-#include <vector>
-#include <map>
-#include "itkProgressReporter.h"
-
-namespace itk
-{
-
-/**
- * \class BinaryImageToLabelCollectionImageFilter
- * \brief Label the connected components in a binary image and produce a collection of label objects
- *
- * BinaryImageToLabelCollectionImageFilter labels the objects in a binary image.
- * Each distinct object is assigned a unique label. 
- * The final object labels start with 1 and are consecutive. Objects
- * that are reached earlier by a raster order scan have a lower
- * label.
- *
- * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
- *
- * \sa ConnectedComponentImageFilter, LabelImageToLabelCollectionImageFilter, LabelCollectionImage
- */
-
-template <class TInputImage, class TOutputImage>
-class ITK_EXPORT BinaryImageToLabelCollectionImageFilter : 
-    public ImageToImageFilter< TInputImage, TOutputImage > 
-{
-public:
-  /**
-   * Standard "Self" & Superclass typedef.
-   */
-  typedef BinaryImageToLabelCollectionImageFilter                   Self;
-  typedef ImageToImageFilter< TInputImage, TOutputImage > Superclass;
-
-  /**
-   * Types from the Superclass
-   */
[…]

### 2007-09-18 itkBinaryImageToLabelMapFilter.h

@@ -1,0 +1,236 @@
+/*=========================================================================
+
+  Program:   Insight Segmentation & Registration Toolkit
+  Module:    $RCSfile: itkBinaryImageToLabelMapFilter.h,v $
+  Language:  C++
+  Date:      $Date: 2007/02/18 20:03:03 $
+  Version:   $Revision: 1.16 $
+
+  Copyright (c) Insight Software Consortium. All rights reserved.
+  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
+
+     This software is distributed WITHOUT ANY WARRANTY; without even 
+     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
+     PURPOSE.  See the above copyright notices for more information.
+
+=========================================================================*/
+
+#ifndef __itkBinaryImageToLabelMapFilter_h
+#define __itkBinaryImageToLabelMapFilter_h
+
+#include "itkImageToImageFilter.h"
+#include "itkImage.h"
+#include "itkConceptChecking.h"
+#include <vector>
+#include <map>
+#include "itkProgressReporter.h"
+
+namespace itk
+{
+
+/**
+ * \class BinaryImageToLabelMapFilter
+ * \brief Label the connected components in a binary image and produce a collection of label objects
+ *
+ * BinaryImageToLabelMapFilter labels the objects in a binary image.
+ * Each distinct object is assigned a unique label. 
+ * The final object labels start with 1 and are consecutive. Objects
+ * that are reached earlier by a raster order scan have a lower
+ * label.
+ *
+ * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
+ *
+ * \sa ConnectedComponentImageFilter, LabelImageToLabelMapFilter, LabelMap
+ */
+
+template <class TInputImage, class TOutputImage>
+class ITK_EXPORT BinaryImageToLabelMapFilter : 
+    public ImageToImageFilter< TInputImage, TOutputImage > 
+{
+public:
+  /**
+   * Standard "Self" & Superclass typedef.
+   */
+  typedef BinaryImageToLabelMapFilter                   Self;
+  typedef ImageToImageFilter< TInputImage, TOutputImage > Superclass;
+
+  /**
+   * Types from the Superclass
+   */
+  typedef typename Superclass::InputImagePointer InputImagePointer;
+
+  /**
[…]

### 2007-09-18 itkBinaryReconstructionByDilationImageFilter.h

@@ -19,10 +19,10 @@
 
 #include "itkImageToImageFilter.h"
 #include "itkLabelObject.h"
-#include "itkLabelCollectionImage.h"
-#include "itkBinaryImageToLabelCollectionImageFilter.h"
-#include "itkReconstructionLabelCollectionImageFilter.h"
-#include "itkLabelCollectionImageToBinaryImageFilter.h"
+#include "itkLabelMap.h"
+#include "itkBinaryImageToLabelMapFilter.h"
+#include "itkReconstructionLabelMapFilter.h"
+#include "itkLabelMapToBinaryImageFilter.h"
 
 
 namespace itk {
@@ -78,10 +78,10 @@ public:
                       TInputImage::ImageDimension);
 
   typedef LabelObject<unsigned long, ImageDimension> LabelObjectType;
-  typedef typename itk::LabelCollectionImage< LabelObjectType > LabelCollectionImageType;
-  typedef typename itk::BinaryImageToLabelCollectionImageFilter< InputImageType, LabelCollectionImageType > LabelizerType;
-  typedef typename itk::ReconstructionLabelCollectionImageFilter< LabelCollectionImageType, InputImageType > ReconstructionType;
-  typedef typename itk::LabelCollectionImageToBinaryImageFilter< LabelCollectionImageType, OutputImageType > BinarizerType;
+  typedef typename itk::LabelMap< LabelObjectType > LabelMapType;
+  typedef typename itk::BinaryImageToLabelMapFilter< InputImageType, LabelMapType > LabelizerType;
+  typedef typename itk::ReconstructionLabelMapFilter< LabelMapType, InputImageType > ReconstructionType;
+  typedef typename itk::LabelMapToBinaryImageFilter< LabelMapType, OutputImageType > BinarizerType;
 
   /** Standard New method. */
   itkNewMacro(Self);  

### 2007-09-18 itkBinaryReconstructionByErosionImageFilter.h

@@ -19,11 +19,11 @@
 
 #include "itkImageToImageFilter.h"
 #include "itkLabelObject.h"
-#include "itkLabelCollectionImage.h"
+#include "itkLabelMap.h"
 #include "itkBinaryNotImageFilter.h"
-#include "itkBinaryImageToLabelCollectionImageFilter.h"
-#include "itkReconstructionLabelCollectionImageFilter.h"
-#include "itkLabelCollectionImageToMaskImageFilter.h"
+#include "itkBinaryImageToLabelMapFilter.h"
+#include "itkReconstructionLabelMapFilter.h"
+#include "itkLabelMapToMaskImageFilter.h"
 
 
 namespace itk {
@@ -78,10 +78,10 @@ public:
 
   typedef BinaryNotImageFilter< InputImageType > NotType;
   typedef LabelObject<unsigned long, ImageDimension> LabelObjectType;
-  typedef typename itk::LabelCollectionImage< LabelObjectType > LabelCollectionImageType;
-  typedef typename itk::BinaryImageToLabelCollectionImageFilter< InputImageType, LabelCollectionImageType > LabelizerType;
-  typedef typename itk::ReconstructionLabelCollectionImageFilter< LabelCollectionImageType, InputImageType > ReconstructionType;
-  typedef typename itk::LabelCollectionImageToMaskImageFilter< LabelCollectionImageType, OutputImageType > BinarizerType;
+  typedef typename itk::LabelMap< LabelObjectType > LabelMapType;
+  typedef typename itk::BinaryImageToLabelMapFilter< InputImageType, LabelMapType > LabelizerType;
+  typedef typename itk::ReconstructionLabelMapFilter< LabelMapType, InputImageType > ReconstructionType;
+  typedef typename itk::LabelMapToMaskImageFilter< LabelMapType, OutputImageType > BinarizerType;
 
   /** Standard New method. */
   itkNewMacro(Self);  

### 2007-09-18 itkBinaryShapeKeepNObjectsImageFilter.h

@@ -19,11 +19,11 @@
 
 #include "itkImageToImageFilter.h"
 #include "itkShapeLabelObject.h"
-#include "itkLabelCollectionImage.h"
-#include "itkBinaryImageToLabelCollectionImageFilter.h"
-#include "itkShapeLabelCollectionImageFilter.h"
-#include "itkShapeKeepNObjectsLabelCollectionImageFilter.h"
-#include "itkLabelCollectionImageToBinaryImageFilter.h"
+#include "itkLabelMap.h"
+#include "itkBinaryImageToLabelMapFilter.h"
+#include "itkShapeLabelMapFilter.h"
+#include "itkShapeKeepNObjectsLabelMapFilter.h"
+#include "itkLabelMapToBinaryImageFilter.h"
 
 
 namespace itk {
@@ -73,12 +73,12 @@ public:
                       TInputImage::ImageDimension);
 
   typedef ShapeLabelObject<unsigned long, ImageDimension> LabelObjectType;
-  typedef typename itk::LabelCollectionImage< LabelObjectType > LabelCollectionImageType;
-  typedef typename itk::BinaryImageToLabelCollectionImageFilter< InputImageType, LabelCollectionImageType > LabelizerType;
-  typedef typename itk::ShapeLabelCollectionImageFilter< LabelCollectionImageType > LabelObjectValuatorType;
+  typedef typename itk::LabelMap< LabelObjectType > LabelMapType;
+  typedef typename itk::BinaryImageToLabelMapFilter< InputImageType, LabelMapType > LabelizerType;
+  typedef typename itk::ShapeLabelMapFilter< LabelMapType > LabelObjectValuatorType;
   typedef typename LabelObjectType::AttributeType AttributeType;
-  typedef typename itk::ShapeKeepNObjectsLabelCollectionImageFilter< LabelCollectionImageType > KeepNObjectsType;
-  typedef typename itk::LabelCollectionImageToBinaryImageFilter< LabelCollectionImageType, OutputImageType > BinarizerType;
+  typedef typename itk::ShapeKeepNObjectsLabelMapFilter< LabelMapType > KeepNObjectsType;
+  typedef typename itk::LabelMapToBinaryImageFilter< LabelMapType, OutputImageType > BinarizerType;
 
   /** Standard New method. */
   itkNewMacro(Self);  

### 2007-09-18 itkBinaryShapeOpeningImageFilter.h

@@ -19,11 +19,11 @@
 
 #include "itkImageToImageFilter.h"
 #include "itkShapeLabelObject.h"
-#include "itkLabelCollectionImage.h"
-#include "itkBinaryImageToLabelCollectionImageFilter.h"
-#include "itkShapeLabelCollectionImageFilter.h"
-#include "itkShapeOpeningLabelCollectionImageFilter.h"
-#include "itkLabelCollectionImageToBinaryImageFilter.h"
+#include "itkLabelMap.h"
+#include "itkBinaryImageToLabelMapFilter.h"
+#include "itkShapeLabelMapFilter.h"
+#include "itkShapeOpeningLabelMapFilter.h"
+#include "itkLabelMapToBinaryImageFilter.h"
 
 
 namespace itk {
@@ -73,12 +73,12 @@ public:
                       TInputImage::ImageDimension);
 
   typedef ShapeLabelObject<unsigned long, ImageDimension> LabelObjectType;
-  typedef typename itk::LabelCollectionImage< LabelObjectType > LabelCollectionImageType;
-  typedef typename itk::BinaryImageToLabelCollectionImageFilter< InputImageType, LabelCollectionImageType > LabelizerType;
-  typedef typename itk::ShapeLabelCollectionImageFilter< LabelCollectionImageType > LabelObjectValuatorType;
+  typedef typename itk::LabelMap< LabelObjectType > LabelMapType;
+  typedef typename itk::BinaryImageToLabelMapFilter< InputImageType, LabelMapType > LabelizerType;
+  typedef typename itk::ShapeLabelMapFilter< LabelMapType > LabelObjectValuatorType;
   typedef typename LabelObjectType::AttributeType AttributeType;
-  typedef typename itk::ShapeOpeningLabelCollectionImageFilter< LabelCollectionImageType > OpeningType;
-  typedef typename itk::LabelCollectionImageToBinaryImageFilter< LabelCollectionImageType, OutputImageType > BinarizerType;
+  typedef typename itk::ShapeOpeningLabelMapFilter< LabelMapType > OpeningType;
+  typedef typename itk::LabelMapToBinaryImageFilter< LabelMapType, OutputImageType > BinarizerType;
 
   /** Standard New method. */
   itkNewMacro(Self);  

### 2007-09-18 itkBinaryStatisticsKeepNObjectsImageFilter.h

@@ -19,11 +19,11 @@
 
 #include "itkImageToImageFilter.h"
 #include "itkStatisticsLabelObject.h"
-#include "itkLabelCollectionImage.h"
-#include "itkBinaryImageToLabelCollectionImageFilter.h"
-#include "itkStatisticsLabelCollectionImageFilter.h"
-#include "itkStatisticsKeepNObjectsLabelCollectionImageFilter.h"
-#include "itkLabelCollectionImageToBinaryImageFilter.h"
+#include "itkLabelMap.h"
+#include "itkBinaryImageToLabelMapFilter.h"
+#include "itkStatisticsLabelMapFilter.h"
+#include "itkStatisticsKeepNObjectsLabelMapFilter.h"
+#include "itkLabelMapToBinaryImageFilter.h"
 
 
 namespace itk {
@@ -78,12 +78,12 @@ public:
                       TInputImage::ImageDimension);
 
   typedef StatisticsLabelObject<unsigned long, ImageDimension> LabelObjectType;
-  typedef typename itk::LabelCollectionImage< LabelObjectType > LabelCollectionImageType;
-  typedef typename itk::BinaryImageToLabelCollectionImageFilter< InputImageType, LabelCollectionImageType > LabelizerType;
-  typedef typename itk::StatisticsLabelCollectionImageFilter< LabelCollectionImageType, TFeatureImage > LabelObjectValuatorType;
+  typedef typename itk::LabelMap< LabelObjectType > LabelMapType;
+  typedef typename itk::BinaryImageToLabelMapFilter< InputImageType, LabelMapType > LabelizerType;
+  typedef typename itk::StatisticsLabelMapFilter< LabelMapType, TFeatureImage > LabelObjectValuatorType;
   typedef typename LabelObjectType::AttributeType AttributeType;
-  typedef typename itk::StatisticsKeepNObjectsLabelCollectionImageFilter< LabelCollectionImageType > KeepNObjectsType;
-  typedef typename itk::LabelCollectionImageToBinaryImageFilter< LabelCollectionImageType, OutputImageType > BinarizerType;
+  typedef typename itk::StatisticsKeepNObjectsLabelMapFilter< LabelMapType > KeepNObjectsType;
+  typedef typename itk::LabelMapToBinaryImageFilter< LabelMapType, OutputImageType > BinarizerType;
 
   /** Standard New method. */
   itkNewMacro(Self);  

### 2007-09-18 itkBinaryStatisticsOpeningImageFilter.h

@@ -19,11 +19,11 @@
 
 #include "itkImageToImageFilter.h"
 #include "itkStatisticsLabelObject.h"
-#include "itkLabelCollectionImage.h"
-#include "itkBinaryImageToLabelCollectionImageFilter.h"
-#include "itkStatisticsLabelCollectionImageFilter.h"
-#include "itkStatisticsOpeningLabelCollectionImageFilter.h"
-#include "itkLabelCollectionImageToBinaryImageFilter.h"
+#include "itkLabelMap.h"
+#include "itkBinaryImageToLabelMapFilter.h"
+#include "itkStatisticsLabelMapFilter.h"
+#include "itkStatisticsOpeningLabelMapFilter.h"
+#include "itkLabelMapToBinaryImageFilter.h"
 
 
 namespace itk {
@@ -78,12 +78,12 @@ public:
                       TInputImage::ImageDimension);
 
   typedef StatisticsLabelObject<unsigned long, ImageDimension> LabelObjectType;
-  typedef typename itk::LabelCollectionImage< LabelObjectType > LabelCollectionImageType;
-  typedef typename itk::BinaryImageToLabelCollectionImageFilter< InputImageType, LabelCollectionImageType > LabelizerType;
-  typedef typename itk::StatisticsLabelCollectionImageFilter< LabelCollectionImageType, TFeatureImage > LabelObjectValuatorType;
+  typedef typename itk::LabelMap< LabelObjectType > LabelMapType;
+  typedef typename itk::BinaryImageToLabelMapFilter< InputImageType, LabelMapType > LabelizerType;
+  typedef typename itk::StatisticsLabelMapFilter< LabelMapType, TFeatureImage > LabelObjectValuatorType;
   typedef typename LabelObjectType::AttributeType AttributeType;
-  typedef typename itk::StatisticsOpeningLabelCollectionImageFilter< LabelCollectionImageType > OpeningType;
-  typedef typename itk::LabelCollectionImageToBinaryImageFilter< LabelCollectionImageType, OutputImageType > BinarizerType;
+  typedef typename itk::StatisticsOpeningLabelMapFilter< LabelMapType > OpeningType;
+  typedef typename itk::LabelMapToBinaryImageFilter< LabelMapType, OutputImageType > BinarizerType;
 
   /** Standard New method. */
   itkNewMacro(Self);  

### 2007-09-18 itkInPlaceLabelCollectionImageFilter.h

@@ -1,175 +1,0 @@
-/*=========================================================================
-
-  Program:   Insight Segmentation & Registration Toolkit
-  Module:    $RCSfile: itkInPlaceLabelCollectionImageFilter.h,v $
-  Language:  C++
-  Date:      $Date: 2004/07/11 14:56:38 $
-  Version:   $Revision: 1.4 $
-
-  Copyright (c) Insight Software Consortium. All rights reserved.
-  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
-
-  Portions of this code are covered under the VTK copyright.
-  See VTKCopyright.txt or http://www.kitware.com/VTKCopyright.htm for details.
-
-     This software is distributed WITHOUT ANY WARRANTY; without even 
-     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
-     PURPOSE.  See the above copyright notices for more information.
-
-=========================================================================*/
-#ifndef __itkInPlaceLabelCollectionImageFilter_h
-#define __itkInPlaceLabelCollectionImageFilter_h
-
-#include "itkLabelCollectionImageFilter.h"
-
-namespace itk
-{
-  
-/** \class InPlaceLabelCollectionImageFilter
- * \brief Base class for filters that take an image as input and overwrite that image as the output
- *
- * InPlaceLabelCollectionImageFilter is the base class for all process objects whose
- * output image data is constructed by overwriting the input image
- * data. In other words, the output bulk data is the same block of
- * memory as the input bulk data.  This filter provides the mechanisms
- * for in place image processing while maintaining general pipeline
- * mechanics. InPlaceLabelCollectionImageFilters use less memory than standard
- * ImageToImageFilters because the input buffer is reused as the
- * output buffer.  However, this benefit does not come without a cost.
- * Since the filter overwrites its input, the ownership of the bulk
- * data is transitioned from the input data object to the output data
- * object.  When a data object has multiple consumers with one
- * of the consumers being an in place filter, the in place filter
- * effectively destroys the bulk data for the data object. Upstream
- * filters will then have to re-execute to regenerate the data object's
- * bulk data for the remaining consumers.
- *
- * Since an InPlaceLabelCollectionImageFilter reuses the input bulk data memory for the
[…]

### 2007-09-18 itkInPlaceLabelMapFilter.h

@@ -1,0 +1,175 @@
+/*=========================================================================
+
+  Program:   Insight Segmentation & Registration Toolkit
+  Module:    $RCSfile: itkInPlaceLabelMapFilter.h,v $
+  Language:  C++
+  Date:      $Date: 2004/07/11 14:56:38 $
+  Version:   $Revision: 1.4 $
+
+  Copyright (c) Insight Software Consortium. All rights reserved.
+  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
+
+  Portions of this code are covered under the VTK copyright.
+  See VTKCopyright.txt or http://www.kitware.com/VTKCopyright.htm for details.
+
+     This software is distributed WITHOUT ANY WARRANTY; without even 
+     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
+     PURPOSE.  See the above copyright notices for more information.
+
+=========================================================================*/
+#ifndef __itkInPlaceLabelMapFilter_h
+#define __itkInPlaceLabelMapFilter_h
+
+#include "itkLabelMapFilter.h"
+
+namespace itk
+{
+  
+/** \class InPlaceLabelMapFilter
+ * \brief Base class for filters that take an image as input and overwrite that image as the output
+ *
+ * InPlaceLabelMapFilter is the base class for all process objects whose
+ * output image data is constructed by overwriting the input image
+ * data. In other words, the output bulk data is the same block of
+ * memory as the input bulk data.  This filter provides the mechanisms
+ * for in place image processing while maintaining general pipeline
+ * mechanics. InPlaceLabelMapFilters use less memory than standard
+ * ImageToImageFilters because the input buffer is reused as the
+ * output buffer.  However, this benefit does not come without a cost.
+ * Since the filter overwrites its input, the ownership of the bulk
+ * data is transitioned from the input data object to the output data
+ * object.  When a data object has multiple consumers with one
+ * of the consumers being an in place filter, the in place filter
+ * effectively destroys the bulk data for the data object. Upstream
+ * filters will then have to re-execute to regenerate the data object's
+ * bulk data for the remaining consumers.
+ *
+ * Since an InPlaceLabelMapFilter reuses the input bulk data memory for the
+ * output bulk data memory, the input image type must match the output
[…]

### 2007-09-18 itkLabelAttributeKeepNObjectsImageFilter.h

@@ -18,10 +18,10 @@
 #define __itkLabelAttributeKeepNObjectsImageFilter_h
 
 #include "itkImageToImageFilter.h"
-#include "itkLabelCollectionImage.h"
-#include "itkLabelImageToLabelCollectionImageFilter.h"
-#include "itkAttributeKeepNObjectsLabelCollectionImageFilter.h"
-#include "itkLabelCollectionImageToLabelImageFilter.h"
+#include "itkLabelMap.h"
+#include "itkLabelImageToLabelMapFilter.h"
+#include "itkAttributeKeepNObjectsLabelMapFilter.h"
+#include "itkLabelMapToLabelImageFilter.h"
 #include "itkAttributeLabelObject.h"
 
 
@@ -40,7 +40,7 @@ namespace itk {
  *
  * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
  *
- * \sa AttributeLabelObject, InPlaceLabelCollectionImageFilter
+ * \sa AttributeLabelObject, InPlaceLabelMapFilter
  * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
  */
 template<class TInputImage, class TLabelObject, class TLabelObjectValuator, class TAttributeAccessor=
@@ -77,13 +77,13 @@ public:
                       TInputImage::ImageDimension);
 
   typedef TLabelObject LabelObjectType;
-  typedef typename itk::LabelCollectionImage< LabelObjectType > LabelCollectionImageType;
-  typedef typename itk::LabelImageToLabelCollectionImageFilter< InputImageType, LabelCollectionImageType > LabelizerType;
+  typedef typename itk::LabelMap< LabelObjectType > LabelMapType;
+  typedef typename itk::LabelImageToLabelMapFilter< InputImageType, LabelMapType > LabelizerType;
   typedef TLabelObjectValuator LabelObjectValuatorType;
   typedef TAttributeAccessor AttributeAccessorType;
   typedef typename AttributeAccessorType::AttributeValueType AttributeValueType;
-  typedef typename itk::AttributeKeepNObjectsLabelCollectionImageFilter< LabelCollectionImageType, AttributeAccessorType > KeepNObjectsType;
-  typedef typename itk::LabelCollectionImageToLabelImageFilter< LabelCollectionImageType, OutputImageType > BinarizerType;
[…]

### 2007-09-18 itkLabelAttributeOpeningImageFilter.h

@@ -18,10 +18,10 @@
 #define __itkLabelAttributeOpeningImageFilter_h
 
 #include "itkImageToImageFilter.h"
-#include "itkLabelCollectionImage.h"
-#include "itkLabelImageToLabelCollectionImageFilter.h"
-#include "itkAttributeOpeningLabelCollectionImageFilter.h"
-#include "itkLabelCollectionImageToLabelImageFilter.h"
+#include "itkLabelMap.h"
+#include "itkLabelImageToLabelMapFilter.h"
+#include "itkAttributeOpeningLabelMapFilter.h"
+#include "itkLabelMapToLabelImageFilter.h"
 #include "itkAttributeLabelObject.h"
 
 
@@ -41,7 +41,7 @@ namespace itk {
  *
  * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
  *
- * \sa AttributeLabelObject, InPlaceLabelCollectionImageFilter
+ * \sa AttributeLabelObject, InPlaceLabelMapFilter
  * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
  */
 template<class TInputImage, class TLabelObject, class TLabelObjectValuator, class TAttributeAccessor=
@@ -78,13 +78,13 @@ public:
                       TInputImage::ImageDimension);
 
   typedef TLabelObject LabelObjectType;
-  typedef typename itk::LabelCollectionImage< LabelObjectType > LabelCollectionImageType;
-  typedef typename itk::LabelImageToLabelCollectionImageFilter< InputImageType, LabelCollectionImageType > LabelizerType;
+  typedef typename itk::LabelMap< LabelObjectType > LabelMapType;
+  typedef typename itk::LabelImageToLabelMapFilter< InputImageType, LabelMapType > LabelizerType;
   typedef TLabelObjectValuator LabelObjectValuatorType;
   typedef TAttributeAccessor AttributeAccessorType;
   typedef typename AttributeAccessorType::AttributeValueType AttributeValueType;
-  typedef typename itk::AttributeOpeningLabelCollectionImageFilter< LabelCollectionImageType, AttributeAccessorType > OpeningType;
-  typedef typename itk::LabelCollectionImageToLabelImageFilter< LabelCollectionImageType, OutputImageType > BinarizerType;
[…]

### 2007-09-18 itkLabelCollectionImage.h

@@ -1,338 +1,0 @@
-/*=========================================================================
-
-  Program:   Insight Segmentation & Registration Toolkit
-  Module:    $RCSfile: itkLabelCollectionImage.h,v $
-  Language:  C++
-  Date:      $Date: 2006/04/20 14:54:09 $
-  Version:   $Revision: 1.136 $
-
-  Copyright (c) Insight Software Consortium. All rights reserved.
-  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
-
-     This software is distributed WITHOUT ANY WARRANTY; without even
-     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR
-     PURPOSE.  See the above copyright notices for more information.
-
-=========================================================================*/
-#ifndef __itkLabelCollectionImage_h
-#define __itkLabelCollectionImage_h
-
-#include "itkImageBase.h"
-#include "itkImageRegion.h"
-#include "itkFixedArray.h"
-#include "itkWeakPointer.h"
-#include <map>
-
-namespace itk
-{
-/** \class LabelCollectionImage
- *  \brief Templated n-dimensional image to store labeled objects.
- *
- * LabelCollectionImage is an image class specialized in storing the labeled
- * images. It represent the image in a different way than itk::Image.
- * Instead of storing the content of the image in an array of pixels values,
- * it store the a collection of labeled objects, and optionally a background
- * value.
- * This way of storing the content of the image allow an easy and efficient
- * manipulation of the objects in the image.
- *
- * The LabelCollectionImage shares a lot of methods with the itk::Image class.
- * it make it usable as input or output of the itk::ImageToImageFilter for example.
- * However the methods don't have the same complexity in the 2 classes, because
- * of the different way to store the data. GetPixel() is run in constant time
- * for example in itk::Image, but have a worst case complexity of O(L), where
- * L is the number of lines in the image (imageSize[1] * imageSize[2] for a 3D
- * image).
- *
- * \ingroup ImageObjects */
-template <class TLabelObject >
-class ITK_EXPORT LabelCollectionImage : public ImageBase<TLabelObject::ImageDimension>
-{
-public:
-  /** Standard class typedefs */
-  typedef LabelCollectionImage               Self;
-  typedef ImageBase<TLabelObject::ImageDimension>  Superclass;
-  typedef SmartPointer<Self>  Pointer;
[…]

### 2007-09-18 itkLabelCollectionImageFilter.h

@@ -1,119 +1,0 @@
-/*=========================================================================
-
-  Program:   Insight Segmentation & Registration Toolkit
-  Module:    $RCSfile: itkLabelCollectionImageFilter.h,v $
-  Language:  C++
-  Date:      $Date: 2004/07/11 14:56:38 $
-  Version:   $Revision: 1.4 $
-
-  Copyright (c) Insight Software Consortium. All rights reserved.
-  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
-
-  Portions of this code are covered under the VTK copyright.
-  See VTKCopyright.txt or http://www.kitware.com/VTKCopyright.htm for details.
-
-     This software is distributed WITHOUT ANY WARRANTY; without even 
-     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
-     PURPOSE.  See the above copyright notices for more information.
-
-=========================================================================*/
-#ifndef __itkLabelCollectionImageFilter_h
-#define __itkLabelCollectionImageFilter_h
-
-#include "itkImageToImageFilter.h"
-
-namespace itk
-{
-  
-/** \class LabelCollectionImageFilter
- * \brief Base class for filters that take an image as input and overwrite that image as the output
- *
- * LabelCollectionImageFilter is the base class for all process objects whose
- * are using a LabelCollectionImageFilter as input. It manage several threads,
- * and run a method TreadedGenerateData() for each object in the LabelCollectionImageFilter.
- * With that class, the developer don't need to take care of iterating over all the objects in
- * the image, or to manage by hand the threads.
- * 
- * \ingroup ImageFilters
- */
-template <class TInputImage, class TOutputImage>
-class ITK_EXPORT LabelCollectionImageFilter : public ImageToImageFilter<TInputImage, TOutputImage>
-{
-public:
-  /** Standard class typedefs. */
-  typedef LabelCollectionImageFilter  Self;
-  typedef ImageToImageFilter<TInputImage, TOutputImage>  Superclass;
-  typedef SmartPointer<Self>  Pointer;
-  typedef SmartPointer<const Self>  ConstPointer;
-  
-  
-  /** Run-time type information (and related methods). */
-  itkTypeMacro(LabelCollectionImageFilter,ImageToImageFilter);
-
-  /** Standard New method. */
-  itkNewMacro(Self);  
-
-  /** Some convenient typedefs. */
[…]

### 2007-09-18 itkLabelCollectionImageToAttributeImageFilter.h

@@ -1,120 +1,0 @@
-/*=========================================================================
-
-  Program:   Insight Segmentation & Registration Toolkit
-  Module:    $RCSfile: itkLabelCollectionImageToAttributeImageFilter.h,v $
-  Language:  C++
-  Date:      $Date: 2005/08/23 15:09:03 $
-  Version:   $Revision: 1.4 $
-
-  Copyright (c) Insight Software Consortium. All rights reserved.
-  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
-
-     This software is distributed WITHOUT ANY WARRANTY; without even 
-     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
-     PURPOSE.  See the above copyright notices for more information.
-
-=========================================================================*/
-#ifndef __itkLabelCollectionImageToAttributeImageFilter_h
-#define __itkLabelCollectionImageToAttributeImageFilter_h
-
-#include "itkImageToImageFilter.h"
-#include "itkAttributeLabelObject.h"
-
-namespace itk {
-
-/** \class LabelCollectionImageToAttributeImageFilter
- * \brief Convert a LabelCollectionImage to a labeled image
- *
- * LabelCollectionImageToAttributeImageFilter converts a LabelCollectionImage to an
- * Image where all the pixels get the attribute value of the label object they belong.
- *
- * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
- *
- * \sa LabelCollectionImageToBinaryImageFilter, LabelCollectionImageToMaskImageFilter
- * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
- */
-template<class TInputImage, class TOutputImage, class TAttributeAccessor=
-    typename Functor::AttributeLabelObjectAccessor< typename TInputImage::LabelObjectType > >
-class ITK_EXPORT LabelCollectionImageToAttributeImageFilter : 
-    public ImageToImageFilter<TInputImage, TOutputImage>
-{
-public:
-  /** Standard class typedefs. */
-  typedef LabelCollectionImageToAttributeImageFilter Self;
-  typedef ImageToImageFilter<TInputImage, TOutputImage>
-  Superclass;
-  typedef SmartPointer<Self>        Pointer;
-  typedef SmartPointer<const Self>  ConstPointer;
-
-  /** Some convenient typedefs. */
-  typedef TInputImage InputImageType;
[…]

### 2007-09-18 itkLabelCollectionImageToBinaryImageFilter.h

@@ -1,154 +1,0 @@
-/*=========================================================================
-
-  Program:   Insight Segmentation & Registration Toolkit
-  Module:    $RCSfile: itkLabelCollectionImageToBinaryImageFilter.h,v $
-  Language:  C++
-  Date:      $Date: 2005/08/23 15:09:03 $
-  Version:   $Revision: 1.4 $
-
-  Copyright (c) Insight Software Consortium. All rights reserved.
-  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
-
-     This software is distributed WITHOUT ANY WARRANTY; without even 
-     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
-     PURPOSE.  See the above copyright notices for more information.
-
-=========================================================================*/
-#ifndef __itkLabelCollectionImageToBinaryImageFilter_h
-#define __itkLabelCollectionImageToBinaryImageFilter_h
-
-#include "itkLabelCollectionImageFilter.h"
-#include "itkBarrier.h"
-
-namespace itk {
-
-/** \class LabelCollectionImageToBinaryImageFilter
- * \brief Convert a LabelCollectionImage to a binary image
- *
- * LabelCollectionImageToBinaryImageFilter to a binary image. All the objects in the image
- * are used as foreground.
- * The background values of the original binary image can be restored by passing this image
- * to the filter with the SetBackgroundImage() method.
- *
- * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
- *
- * \sa LabelCollectionImageToLabelImageFilter, LabelCollectionImageToMaskImageFilter
- * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
- */
-template<class TInputImage, class TOutputImage>
-class ITK_EXPORT LabelCollectionImageToBinaryImageFilter : 
-    public LabelCollectionImageFilter<TInputImage, TOutputImage>
-{
-public:
-  /** Standard class typedefs. */
-  typedef LabelCollectionImageToBinaryImageFilter Self;
-  typedef LabelCollectionImageFilter<TInputImage, TOutputImage>
-  Superclass;
-  typedef SmartPointer<Self>        Pointer;
-  typedef SmartPointer<const Self>  ConstPointer;
-
-  /** Some convenient typedefs. */
-  typedef TInputImage InputImageType;
-  typedef TOutputImage OutputImageType;
[…]

### 2007-09-18 itkLabelCollectionImageToLabelImageFilter.h

@@ -1,96 +1,0 @@
-/*=========================================================================
-
-  Program:   Insight Segmentation & Registration Toolkit
-  Module:    $RCSfile: itkLabelCollectionImageToLabelImageFilter.h,v $
-  Language:  C++
-  Date:      $Date: 2005/08/23 15:09:03 $
-  Version:   $Revision: 1.4 $
-
-  Copyright (c) Insight Software Consortium. All rights reserved.
-  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
-
-     This software is distributed WITHOUT ANY WARRANTY; without even 
-     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
-     PURPOSE.  See the above copyright notices for more information.
-
-=========================================================================*/
-#ifndef __itkLabelCollectionImageToLabelImageFilter_h
-#define __itkLabelCollectionImageToLabelImageFilter_h
-
-#include "itkLabelCollectionImageFilter.h"
-
-namespace itk {
-
-/** \class LabelCollectionImageToLabelImageFilter
- * \brief Convert a LabelCollectionImage to a labeled image
- *
- * LabelCollectionImageToBinaryImageFilter to a label image.
- *
- * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
- *
- * \sa LabelCollectionImageToBinaryImageFilter, LabelCollectionImageToMaskImageFilter
- * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
- */
-template<class TInputImage, class TOutputImage>
-class ITK_EXPORT LabelCollectionImageToLabelImageFilter : 
-    public LabelCollectionImageFilter<TInputImage, TOutputImage>
-{
-public:
-  /** Standard class typedefs. */
-  typedef LabelCollectionImageToLabelImageFilter Self;
-  typedef LabelCollectionImageFilter<TInputImage, TOutputImage>
-  Superclass;
-  typedef SmartPointer<Self>        Pointer;
-  typedef SmartPointer<const Self>  ConstPointer;
-
-  /** Some convenient typedefs. */
-  typedef TInputImage InputImageType;
-  typedef TOutputImage OutputImageType;
-  typedef typename InputImageType::Pointer         InputImagePointer;
-  typedef typename InputImageType::ConstPointer    InputImageConstPointer;
[…]

### 2007-09-18 itkLabelCollectionImageToMaskImageFilter.h

@@ -1,190 +1,0 @@
-/*=========================================================================
-
-  Program:   Insight Segmentation & Registration Toolkit
-  Module:    $RCSfile: itkLabelCollectionImageToMaskImageFilter.h,v $
-  Language:  C++
-  Date:      $Date: 2005/08/23 15:09:03 $
-  Version:   $Revision: 1.4 $
-
-  Copyright (c) Insight Software Consortium. All rights reserved.
-  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
-
-     This software is distributed WITHOUT ANY WARRANTY; without even 
-     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
-     PURPOSE.  See the above copyright notices for more information.
-
-=========================================================================*/
-#ifndef __itkLabelCollectionImageToMaskImageFilter_h
-#define __itkLabelCollectionImageToMaskImageFilter_h
-
-#include "itkLabelCollectionImageFilter.h"
-#include "itkBarrier.h"
-
-namespace itk {
-
-/** \class LabelCollectionImageToMaskImageFilter
- * \brief Mask and image with a LabelCollectionImage
- *
- * LabelCollectionImageToMaskImageFilter mask the content of an input image according
- * to the content of the input LabelCollectionImage. The masked pixel of the input image
- * are set to the BackgroundValue.
- * LabelCollectionImageToMaskImageFilter can keep the input image for one label only, with
- * Negated = false (the default) or it can mask the input image for a single label, when
- * Negated equals true. In Both cases, the label is set with SetLabel(). 
- *
- * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
- *
- * \sa LabelCollectionImageToBinaryImageFilter, LabelCollectionImageToLabelImageFilter
- * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
- */
-template<class TInputImage, class TOutputImage>
-class ITK_EXPORT LabelCollectionImageToMaskImageFilter : 
-    public LabelCollectionImageFilter<TInputImage, TOutputImage>
-{
-public:
-  /** Standard class typedefs. */
-  typedef LabelCollectionImageToMaskImageFilter Self;
-  typedef LabelCollectionImageFilter<TInputImage, TOutputImage>
-  Superclass;
[…]

### 2007-09-18 itkLabelImageToLabelCollectionImageFilter.h

@@ -1,129 +1,0 @@
-/*=========================================================================
-
-  Program:   Insight Segmentation & Registration Toolkit
-  Module:    $RCSfile: itkLabelImageToLabelCollectionImageFilter.h,v $
-  Language:  C++
-  Date:      $Date: 2005/08/23 15:09:03 $
-  Version:   $Revision: 1.4 $
-
-  Copyright (c) Insight Software Consortium. All rights reserved.
-  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
-
-     This software is distributed WITHOUT ANY WARRANTY; without even 
-     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
-     PURPOSE.  See the above copyright notices for more information.
-
-=========================================================================*/
-#ifndef __itkLabelImageToLabelCollectionImageFilter_h
-#define __itkLabelImageToLabelCollectionImageFilter_h
-
-#include "itkImageToImageFilter.h"
-
-namespace itk {
-
-/** \class LabelImageToLabelCollectionImageFilter
- * \brief convert a labeled image to a label collection image
- *
- * LabelImageToLabelCollectionImageFilter converts a label image to a label collection image.
- * The labels are the same in the input and the output image.
- * 
- * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
- *
- * \sa BinaryImageToLabelCollectionImageFilter, LabelCollectionImageToLabelImageFilter
- * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
- */
-template<class TInputImage, class TOutputImage>
-class ITK_EXPORT LabelImageToLabelCollectionImageFilter : 
-    public ImageToImageFilter<TInputImage, TOutputImage>
-{
-public:
-  /** Standard class typedefs. */
-  typedef LabelImageToLabelCollectionImageFilter Self;
-  typedef ImageToImageFilter<TInputImage, TOutputImage>
-  Superclass;
-  typedef SmartPointer<Self>        Pointer;
-  typedef SmartPointer<const Self>  ConstPointer;
-
-  /** Some convenient typedefs. */
-  typedef TInputImage InputImageType;
-  typedef TOutputImage OutputImageType;
-  typedef typename InputImageType::Pointer         InputImagePointer;
-  typedef typename InputImageType::ConstPointer    InputImageConstPointer;
[…]

### 2007-09-18 itkLabelImageToLabelMapFilter.h

@@ -1,0 +1,129 @@
+/*=========================================================================
+
+  Program:   Insight Segmentation & Registration Toolkit
+  Module:    $RCSfile: itkLabelImageToLabelMapFilter.h,v $
+  Language:  C++
+  Date:      $Date: 2005/08/23 15:09:03 $
+  Version:   $Revision: 1.4 $
+
+  Copyright (c) Insight Software Consortium. All rights reserved.
+  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
+
+     This software is distributed WITHOUT ANY WARRANTY; without even 
+     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
+     PURPOSE.  See the above copyright notices for more information.
+
+=========================================================================*/
+#ifndef __itkLabelImageToLabelMapFilter_h
+#define __itkLabelImageToLabelMapFilter_h
+
+#include "itkImageToImageFilter.h"
+
+namespace itk {
+
+/** \class LabelImageToLabelMapFilter
+ * \brief convert a labeled image to a label collection image
+ *
+ * LabelImageToLabelMapFilter converts a label image to a label collection image.
+ * The labels are the same in the input and the output image.
+ * 
+ * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
+ *
+ * \sa BinaryImageToLabelMapFilter, LabelMapToLabelImageFilter
+ * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
+ */
+template<class TInputImage, class TOutputImage>
+class ITK_EXPORT LabelImageToLabelMapFilter : 
+    public ImageToImageFilter<TInputImage, TOutputImage>
+{
+public:
+  /** Standard class typedefs. */
+  typedef LabelImageToLabelMapFilter Self;
+  typedef ImageToImageFilter<TInputImage, TOutputImage>
+  Superclass;
+  typedef SmartPointer<Self>        Pointer;
+  typedef SmartPointer<const Self>  ConstPointer;
+
+  /** Some convenient typedefs. */
+  typedef TInputImage InputImageType;
+  typedef TOutputImage OutputImageType;
+  typedef typename InputImageType::Pointer         InputImagePointer;
+  typedef typename InputImageType::ConstPointer    InputImageConstPointer;
+  typedef typename InputImageType::RegionType      InputImageRegionType;
[…]

### 2007-09-18 itkLabelMap.h

@@ -1,0 +1,338 @@
+/*=========================================================================
+
+  Program:   Insight Segmentation & Registration Toolkit
+  Module:    $RCSfile: itkLabelMap.h,v $
+  Language:  C++
+  Date:      $Date: 2006/04/20 14:54:09 $
+  Version:   $Revision: 1.136 $
+
+  Copyright (c) Insight Software Consortium. All rights reserved.
+  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
+
+     This software is distributed WITHOUT ANY WARRANTY; without even
+     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR
+     PURPOSE.  See the above copyright notices for more information.
+
+=========================================================================*/
+#ifndef __itkLabelMap_h
+#define __itkLabelMap_h
+
+#include "itkImageBase.h"
+#include "itkImageRegion.h"
+#include "itkFixedArray.h"
+#include "itkWeakPointer.h"
+#include <map>
+
+namespace itk
+{
+/** \class LabelMap
+ *  \brief Templated n-dimensional image to store labeled objects.
+ *
+ * LabelMap is an image class specialized in storing the labeled
+ * images. It represent the image in a different way than itk::Image.
+ * Instead of storing the content of the image in an array of pixels values,
+ * it store the a collection of labeled objects, and optionally a background
+ * value.
+ * This way of storing the content of the image allow an easy and efficient
+ * manipulation of the objects in the image.
+ *
+ * The LabelMap shares a lot of methods with the itk::Image class.
+ * it make it usable as input or output of the itk::ImageToImageFilter for example.
+ * However the methods don't have the same complexity in the 2 classes, because
+ * of the different way to store the data. GetPixel() is run in constant time
+ * for example in itk::Image, but have a worst case complexity of O(L), where
+ * L is the number of lines in the image (imageSize[1] * imageSize[2] for a 3D
+ * image).
+ *
+ * \ingroup ImageObjects */
+template <class TLabelObject >
+class ITK_EXPORT LabelMap : public ImageBase<TLabelObject::ImageDimension>
+{
+public:
+  /** Standard class typedefs */
+  typedef LabelMap               Self;
+  typedef ImageBase<TLabelObject::ImageDimension>  Superclass;
+  typedef SmartPointer<Self>  Pointer;
+  typedef SmartPointer<const Self>  ConstPointer;
+  typedef WeakPointer<const Self>  ConstWeakPointer;
+
[…]

### 2007-09-18 itkLabelMapFilter.h

@@ -1,0 +1,119 @@
+/*=========================================================================
+
+  Program:   Insight Segmentation & Registration Toolkit
+  Module:    $RCSfile: itkLabelMapFilter.h,v $
+  Language:  C++
+  Date:      $Date: 2004/07/11 14:56:38 $
+  Version:   $Revision: 1.4 $
+
+  Copyright (c) Insight Software Consortium. All rights reserved.
+  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
+
+  Portions of this code are covered under the VTK copyright.
+  See VTKCopyright.txt or http://www.kitware.com/VTKCopyright.htm for details.
+
+     This software is distributed WITHOUT ANY WARRANTY; without even 
+     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
+     PURPOSE.  See the above copyright notices for more information.
+
+=========================================================================*/
+#ifndef __itkLabelMapFilter_h
+#define __itkLabelMapFilter_h
+
+#include "itkImageToImageFilter.h"
+
+namespace itk
+{
+  
+/** \class LabelMapFilter
+ * \brief Base class for filters that take an image as input and overwrite that image as the output
+ *
+ * LabelMapFilter is the base class for all process objects whose
+ * are using a LabelMapFilter as input. It manage several threads,
+ * and run a method TreadedGenerateData() for each object in the LabelMapFilter.
+ * With that class, the developer don't need to take care of iterating over all the objects in
+ * the image, or to manage by hand the threads.
+ * 
+ * \ingroup ImageFilters
+ */
+template <class TInputImage, class TOutputImage>
+class ITK_EXPORT LabelMapFilter : public ImageToImageFilter<TInputImage, TOutputImage>
+{
+public:
+  /** Standard class typedefs. */
+  typedef LabelMapFilter  Self;
+  typedef ImageToImageFilter<TInputImage, TOutputImage>  Superclass;
+  typedef SmartPointer<Self>  Pointer;
+  typedef SmartPointer<const Self>  ConstPointer;
+  
+  
+  /** Run-time type information (and related methods). */
+  itkTypeMacro(LabelMapFilter,ImageToImageFilter);
+
+  /** Standard New method. */
+  itkNewMacro(Self);  
+
+  /** Some convenient typedefs. */
+  typedef TInputImage InputImageType;
+  typedef typename InputImageType::Pointer         InputImagePointer;
[…]

### 2007-09-18 itkLabelMapToAttributeImageFilter.h

@@ -1,0 +1,120 @@
+/*=========================================================================
+
+  Program:   Insight Segmentation & Registration Toolkit
+  Module:    $RCSfile: itkLabelMapToAttributeImageFilter.h,v $
+  Language:  C++
+  Date:      $Date: 2005/08/23 15:09:03 $
+  Version:   $Revision: 1.4 $
+
+  Copyright (c) Insight Software Consortium. All rights reserved.
+  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
+
+     This software is distributed WITHOUT ANY WARRANTY; without even 
+     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
+     PURPOSE.  See the above copyright notices for more information.
+
+=========================================================================*/
+#ifndef __itkLabelMapToAttributeImageFilter_h
+#define __itkLabelMapToAttributeImageFilter_h
+
+#include "itkImageToImageFilter.h"
+#include "itkAttributeLabelObject.h"
+
+namespace itk {
+
+/** \class LabelMapToAttributeImageFilter
+ * \brief Convert a LabelMap to a labeled image
+ *
+ * LabelMapToAttributeImageFilter converts a LabelMap to an
+ * Image where all the pixels get the attribute value of the label object they belong.
+ *
+ * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
+ *
+ * \sa LabelMapToBinaryImageFilter, LabelMapToMaskImageFilter
+ * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
+ */
+template<class TInputImage, class TOutputImage, class TAttributeAccessor=
+    typename Functor::AttributeLabelObjectAccessor< typename TInputImage::LabelObjectType > >
+class ITK_EXPORT LabelMapToAttributeImageFilter : 
+    public ImageToImageFilter<TInputImage, TOutputImage>
+{
+public:
+  /** Standard class typedefs. */
+  typedef LabelMapToAttributeImageFilter Self;
+  typedef ImageToImageFilter<TInputImage, TOutputImage>
+  Superclass;
+  typedef SmartPointer<Self>        Pointer;
+  typedef SmartPointer<const Self>  ConstPointer;
+
+  /** Some convenient typedefs. */
+  typedef TInputImage InputImageType;
+  typedef TOutputImage OutputImageType;
[…]

### 2007-09-18 itkLabelMapToBinaryImageFilter.h

@@ -1,0 +1,154 @@
+/*=========================================================================
+
+  Program:   Insight Segmentation & Registration Toolkit
+  Module:    $RCSfile: itkLabelMapToBinaryImageFilter.h,v $
+  Language:  C++
+  Date:      $Date: 2005/08/23 15:09:03 $
+  Version:   $Revision: 1.4 $
+
+  Copyright (c) Insight Software Consortium. All rights reserved.
+  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
+
+     This software is distributed WITHOUT ANY WARRANTY; without even 
+     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
+     PURPOSE.  See the above copyright notices for more information.
+
+=========================================================================*/
+#ifndef __itkLabelMapToBinaryImageFilter_h
+#define __itkLabelMapToBinaryImageFilter_h
+
+#include "itkLabelMapFilter.h"
+#include "itkBarrier.h"
+
+namespace itk {
+
+/** \class LabelMapToBinaryImageFilter
+ * \brief Convert a LabelMap to a binary image
+ *
+ * LabelMapToBinaryImageFilter to a binary image. All the objects in the image
+ * are used as foreground.
+ * The background values of the original binary image can be restored by passing this image
+ * to the filter with the SetBackgroundImage() method.
+ *
+ * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
+ *
+ * \sa LabelMapToLabelImageFilter, LabelMapToMaskImageFilter
+ * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
+ */
+template<class TInputImage, class TOutputImage>
+class ITK_EXPORT LabelMapToBinaryImageFilter : 
+    public LabelMapFilter<TInputImage, TOutputImage>
+{
+public:
+  /** Standard class typedefs. */
+  typedef LabelMapToBinaryImageFilter Self;
+  typedef LabelMapFilter<TInputImage, TOutputImage>
+  Superclass;
+  typedef SmartPointer<Self>        Pointer;
+  typedef SmartPointer<const Self>  ConstPointer;
+
+  /** Some convenient typedefs. */
+  typedef TInputImage InputImageType;
+  typedef TOutputImage OutputImageType;
+  typedef typename InputImageType::Pointer         InputImagePointer;
[…]

### 2007-09-18 itkLabelMapToLabelImageFilter.h

@@ -1,0 +1,96 @@
+/*=========================================================================
+
+  Program:   Insight Segmentation & Registration Toolkit
+  Module:    $RCSfile: itkLabelMapToLabelImageFilter.h,v $
+  Language:  C++
+  Date:      $Date: 2005/08/23 15:09:03 $
+  Version:   $Revision: 1.4 $
+
+  Copyright (c) Insight Software Consortium. All rights reserved.
+  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
+
+     This software is distributed WITHOUT ANY WARRANTY; without even 
+     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
+     PURPOSE.  See the above copyright notices for more information.
+
+=========================================================================*/
+#ifndef __itkLabelMapToLabelImageFilter_h
+#define __itkLabelMapToLabelImageFilter_h
+
+#include "itkLabelMapFilter.h"
+
+namespace itk {
+
+/** \class LabelMapToLabelImageFilter
+ * \brief Convert a LabelMap to a labeled image
+ *
+ * LabelMapToBinaryImageFilter to a label image.
+ *
+ * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
+ *
+ * \sa LabelMapToBinaryImageFilter, LabelMapToMaskImageFilter
+ * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
+ */
+template<class TInputImage, class TOutputImage>
+class ITK_EXPORT LabelMapToLabelImageFilter : 
+    public LabelMapFilter<TInputImage, TOutputImage>
+{
+public:
+  /** Standard class typedefs. */
+  typedef LabelMapToLabelImageFilter Self;
+  typedef LabelMapFilter<TInputImage, TOutputImage>
+  Superclass;
+  typedef SmartPointer<Self>        Pointer;
+  typedef SmartPointer<const Self>  ConstPointer;
+
+  /** Some convenient typedefs. */
+  typedef TInputImage InputImageType;
+  typedef TOutputImage OutputImageType;
+  typedef typename InputImageType::Pointer         InputImagePointer;
+  typedef typename InputImageType::ConstPointer    InputImageConstPointer;
+  typedef typename InputImageType::RegionType      InputImageRegionType;
+  typedef typename InputImageType::PixelType       InputImagePixelType;
[…]

### 2007-09-18 itkLabelMapToMaskImageFilter.h

@@ -1,0 +1,190 @@
+/*=========================================================================
+
+  Program:   Insight Segmentation & Registration Toolkit
+  Module:    $RCSfile: itkLabelMapToMaskImageFilter.h,v $
+  Language:  C++
+  Date:      $Date: 2005/08/23 15:09:03 $
+  Version:   $Revision: 1.4 $
+
+  Copyright (c) Insight Software Consortium. All rights reserved.
+  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
+
+     This software is distributed WITHOUT ANY WARRANTY; without even 
+     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
+     PURPOSE.  See the above copyright notices for more information.
+
+=========================================================================*/
+#ifndef __itkLabelMapToMaskImageFilter_h
+#define __itkLabelMapToMaskImageFilter_h
+
+#include "itkLabelMapFilter.h"
+#include "itkBarrier.h"
+
+namespace itk {
+
+/** \class LabelMapToMaskImageFilter
+ * \brief Mask and image with a LabelMap
+ *
+ * LabelMapToMaskImageFilter mask the content of an input image according
+ * to the content of the input LabelMap. The masked pixel of the input image
+ * are set to the BackgroundValue.
+ * LabelMapToMaskImageFilter can keep the input image for one label only, with
+ * Negated = false (the default) or it can mask the input image for a single label, when
+ * Negated equals true. In Both cases, the label is set with SetLabel(). 
+ *
+ * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
+ *
+ * \sa LabelMapToBinaryImageFilter, LabelMapToLabelImageFilter
+ * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
+ */
+template<class TInputImage, class TOutputImage>
+class ITK_EXPORT LabelMapToMaskImageFilter : 
+    public LabelMapFilter<TInputImage, TOutputImage>
+{
+public:
+  /** Standard class typedefs. */
+  typedef LabelMapToMaskImageFilter Self;
+  typedef LabelMapFilter<TInputImage, TOutputImage>
+  Superclass;
+  typedef SmartPointer<Self>        Pointer;
+  typedef SmartPointer<const Self>  ConstPointer;
+
+  /** Some convenient typedefs. */
[…]

### 2007-09-18 itkLabelObject.h

@@ -19,7 +19,7 @@
 
 #include <deque>
 #include <itkLightObject.h>
-#include "itkLabelCollectionImage.h"
+#include "itkLabelMap.h"
 
 namespace itk
 {
@@ -148,7 +148,7 @@ private:
  *  \brief The base class for the representation of an labeled binary object in an image
  * 
  * LabelObject is the base class to represent a labeled object in an image.
- * It should be used associated with the LabelCollectionImage.
+ * It should be used associated with the LabelMap.
  *
  * LabelObject store mainly 2 things: the label of the object, and a set of lines
  * which are part of the object.
@@ -161,7 +161,7 @@ private:
  *
  * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
  *
- * \sa LabelCollectionImageFilter, AttributeLabelObject
+ * \sa LabelMapFilter, AttributeLabelObject
  * \ingroup DataRepresentation 
  */
 template < class TLabel, unsigned int VImageDimension >

### 2007-09-18 itkLabelShapeKeepNObjectsImageFilter.h

@@ -19,11 +19,11 @@
 
 #include "itkImageToImageFilter.h"
 #include "itkShapeLabelObject.h"
-#include "itkLabelCollectionImage.h"
-#include "itkLabelImageToLabelCollectionImageFilter.h"
-#include "itkShapeLabelCollectionImageFilter.h"
-#include "itkShapeKeepNObjectsLabelCollectionImageFilter.h"
-#include "itkLabelCollectionImageToLabelImageFilter.h"
+#include "itkLabelMap.h"
+#include "itkLabelImageToLabelMapFilter.h"
+#include "itkShapeLabelMapFilter.h"
+#include "itkShapeKeepNObjectsLabelMapFilter.h"
+#include "itkLabelMapToLabelImageFilter.h"
 
 
 namespace itk {
@@ -73,12 +73,12 @@ public:
                       TInputImage::ImageDimension);
 
   typedef ShapeLabelObject<InputImagePixelType, ImageDimension> LabelObjectType;
-  typedef typename itk::LabelCollectionImage< LabelObjectType > LabelCollectionImageType;
-  typedef typename itk::LabelImageToLabelCollectionImageFilter< InputImageType, LabelCollectionImageType > LabelizerType;
-  typedef typename itk::ShapeLabelCollectionImageFilter< LabelCollectionImageType > LabelObjectValuatorType;
+  typedef typename itk::LabelMap< LabelObjectType > LabelMapType;
+  typedef typename itk::LabelImageToLabelMapFilter< InputImageType, LabelMapType > LabelizerType;
+  typedef typename itk::ShapeLabelMapFilter< LabelMapType > LabelObjectValuatorType;
   typedef typename LabelObjectType::AttributeType AttributeType;
-  typedef typename itk::ShapeKeepNObjectsLabelCollectionImageFilter< LabelCollectionImageType > KeepNObjectsType;
-  typedef typename itk::LabelCollectionImageToLabelImageFilter< LabelCollectionImageType, OutputImageType > BinarizerType;
+  typedef typename itk::ShapeKeepNObjectsLabelMapFilter< LabelMapType > KeepNObjectsType;
+  typedef typename itk::LabelMapToLabelImageFilter< LabelMapType, OutputImageType > BinarizerType;
 
   /** Standard New method. */
   itkNewMacro(Self);  

### 2007-09-18 itkLabelShapeOpeningImageFilter.h

@@ -19,11 +19,11 @@
 
 #include "itkImageToImageFilter.h"
 #include "itkShapeLabelObject.h"
-#include "itkLabelCollectionImage.h"
-#include "itkLabelImageToLabelCollectionImageFilter.h"
-#include "itkShapeLabelCollectionImageFilter.h"
-#include "itkShapeOpeningLabelCollectionImageFilter.h"
-#include "itkLabelCollectionImageToLabelImageFilter.h"
+#include "itkLabelMap.h"
+#include "itkLabelImageToLabelMapFilter.h"
+#include "itkShapeLabelMapFilter.h"
+#include "itkShapeOpeningLabelMapFilter.h"
+#include "itkLabelMapToLabelImageFilter.h"
 
 
 namespace itk {
@@ -73,12 +73,12 @@ public:
                       TInputImage::ImageDimension);
 
   typedef ShapeLabelObject<InputImagePixelType, ImageDimension> LabelObjectType;
-  typedef typename itk::LabelCollectionImage< LabelObjectType > LabelCollectionImageType;
-  typedef typename itk::LabelImageToLabelCollectionImageFilter< InputImageType, LabelCollectionImageType > LabelizerType;
-  typedef typename itk::ShapeLabelCollectionImageFilter< LabelCollectionImageType > LabelObjectValuatorType;
+  typedef typename itk::LabelMap< LabelObjectType > LabelMapType;
+  typedef typename itk::LabelImageToLabelMapFilter< InputImageType, LabelMapType > LabelizerType;
+  typedef typename itk::ShapeLabelMapFilter< LabelMapType > LabelObjectValuatorType;
   typedef typename LabelObjectType::AttributeType AttributeType;
-  typedef typename itk::ShapeOpeningLabelCollectionImageFilter< LabelCollectionImageType > OpeningType;
-  typedef typename itk::LabelCollectionImageToLabelImageFilter< LabelCollectionImageType, OutputImageType > BinarizerType;
+  typedef typename itk::ShapeOpeningLabelMapFilter< LabelMapType > OpeningType;
+  typedef typename itk::LabelMapToLabelImageFilter< LabelMapType, OutputImageType > BinarizerType;
 
   /** Standard New method. */
   itkNewMacro(Self);  

### 2007-09-18 itkLabelStatisticsKeepNObjectsImageFilter.h

@@ -19,11 +19,11 @@
 
 #include "itkImageToImageFilter.h"
 #include "itkStatisticsLabelObject.h"
-#include "itkLabelCollectionImage.h"
-#include "itkLabelImageToLabelCollectionImageFilter.h"
-#include "itkStatisticsLabelCollectionImageFilter.h"
-#include "itkStatisticsKeepNObjectsLabelCollectionImageFilter.h"
-#include "itkLabelCollectionImageToLabelImageFilter.h"
+#include "itkLabelMap.h"
+#include "itkLabelImageToLabelMapFilter.h"
+#include "itkStatisticsLabelMapFilter.h"
+#include "itkStatisticsKeepNObjectsLabelMapFilter.h"
+#include "itkLabelMapToLabelImageFilter.h"
 
 
 namespace itk {
@@ -78,12 +78,12 @@ public:
                       TInputImage::ImageDimension);
 
   typedef StatisticsLabelObject<InputImagePixelType, ImageDimension> LabelObjectType;
-  typedef typename itk::LabelCollectionImage< LabelObjectType > LabelCollectionImageType;
-  typedef typename itk::LabelImageToLabelCollectionImageFilter< InputImageType, LabelCollectionImageType > LabelizerType;
-  typedef typename itk::StatisticsLabelCollectionImageFilter< LabelCollectionImageType, TFeatureImage > LabelObjectValuatorType;
+  typedef typename itk::LabelMap< LabelObjectType > LabelMapType;
+  typedef typename itk::LabelImageToLabelMapFilter< InputImageType, LabelMapType > LabelizerType;
+  typedef typename itk::StatisticsLabelMapFilter< LabelMapType, TFeatureImage > LabelObjectValuatorType;
   typedef typename LabelObjectType::AttributeType AttributeType;
-  typedef typename itk::StatisticsKeepNObjectsLabelCollectionImageFilter< LabelCollectionImageType > KeepNObjectsType;
-  typedef typename itk::LabelCollectionImageToLabelImageFilter< LabelCollectionImageType, OutputImageType > BinarizerType;
+  typedef typename itk::StatisticsKeepNObjectsLabelMapFilter< LabelMapType > KeepNObjectsType;
+  typedef typename itk::LabelMapToLabelImageFilter< LabelMapType, OutputImageType > BinarizerType;
 
   /** Standard New method. */
   itkNewMacro(Self);  

### 2007-09-18 itkLabelStatisticsOpeningImageFilter.h

@@ -19,11 +19,11 @@
 
 #include "itkImageToImageFilter.h"
 #include "itkStatisticsLabelObject.h"
-#include "itkLabelCollectionImage.h"
-#include "itkLabelImageToLabelCollectionImageFilter.h"
-#include "itkStatisticsLabelCollectionImageFilter.h"
-#include "itkStatisticsOpeningLabelCollectionImageFilter.h"
-#include "itkLabelCollectionImageToLabelImageFilter.h"
+#include "itkLabelMap.h"
+#include "itkLabelImageToLabelMapFilter.h"
+#include "itkStatisticsLabelMapFilter.h"
+#include "itkStatisticsOpeningLabelMapFilter.h"
+#include "itkLabelMapToLabelImageFilter.h"
 
 
 namespace itk {
@@ -78,12 +78,12 @@ public:
                       TInputImage::ImageDimension);
 
   typedef StatisticsLabelObject<InputImagePixelType, ImageDimension> LabelObjectType;
-  typedef typename itk::LabelCollectionImage< LabelObjectType > LabelCollectionImageType;
-  typedef typename itk::LabelImageToLabelCollectionImageFilter< InputImageType, LabelCollectionImageType > LabelizerType;
-  typedef typename itk::StatisticsLabelCollectionImageFilter< LabelCollectionImageType, TFeatureImage > LabelObjectValuatorType;
+  typedef typename itk::LabelMap< LabelObjectType > LabelMapType;
+  typedef typename itk::LabelImageToLabelMapFilter< InputImageType, LabelMapType > LabelizerType;
+  typedef typename itk::StatisticsLabelMapFilter< LabelMapType, TFeatureImage > LabelObjectValuatorType;
   typedef typename LabelObjectType::AttributeType AttributeType;
-  typedef typename itk::StatisticsOpeningLabelCollectionImageFilter< LabelCollectionImageType > OpeningType;
-  typedef typename itk::LabelCollectionImageToLabelImageFilter< LabelCollectionImageType, OutputImageType > BinarizerType;
+  typedef typename itk::StatisticsOpeningLabelMapFilter< LabelMapType > OpeningType;
+  typedef typename itk::LabelMapToLabelImageFilter< LabelMapType, OutputImageType > BinarizerType;
 
   /** Standard New method. */
   itkNewMacro(Self);  

### 2007-09-18 itkReconstructionLabelCollectionImageFilter.h

@@ -1,131 +1,0 @@
-/*=========================================================================
-
-  Program:   Insight Segmentation & Registration Toolkit
-  Module:    $RCSfile: itkReconstructionLabelCollectionImageFilter.h,v $
-  Language:  C++
-  Date:      $Date: 2006/03/28 19:59:05 $
-  Version:   $Revision: 1.6 $
-
-  Copyright (c) Insight Software Consortium. All rights reserved.
-  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
-
-     This software is distributed WITHOUT ANY WARRANTY; without even 
-     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
-     PURPOSE.  See the above copyright notices for more information.
-
-=========================================================================*/
-#ifndef __itkReconstructionLabelCollectionImageFilter_h
-#define __itkReconstructionLabelCollectionImageFilter_h
-
-#include "itkInPlaceLabelCollectionImageFilter.h"
-
-namespace itk {
-/** \class ReconstructionLabelCollectionImageFilter
- * \brief 
- *
- * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
- */
-template<class TImage, class TMarkerImage>
-class ITK_EXPORT ReconstructionLabelCollectionImageFilter : 
-    public InPlaceLabelCollectionImageFilter<TImage>
-{
-public:
-  /** Standard class typedefs. */
-  typedef ReconstructionLabelCollectionImageFilter Self;
-  typedef InPlaceLabelCollectionImageFilter<TImage>
-  Superclass;
-  typedef SmartPointer<Self>        Pointer;
-  typedef SmartPointer<const Self>  ConstPointer;
-
-  /** Some convenient typedefs. */
-  typedef TImage ImageType;
-  typedef typename ImageType::Pointer         ImagePointer;
-  typedef typename ImageType::ConstPointer    ImageConstPointer;
-  typedef typename ImageType::PixelType       PixelType;
-  typedef typename ImageType::IndexType       IndexType;
-  typedef typename ImageType::LabelObjectType LabelObjectType;
-  
-  typedef TMarkerImage MarkerImageType;
-  typedef typename MarkerImageType::Pointer         MarkerImagePointer;
-  typedef typename MarkerImageType::ConstPointer    MarkerImageConstPointer;
[…]

### 2007-09-18 itkReconstructionLabelMapFilter.h

@@ -1,0 +1,131 @@
+/*=========================================================================
+
+  Program:   Insight Segmentation & Registration Toolkit
+  Module:    $RCSfile: itkReconstructionLabelMapFilter.h,v $
+  Language:  C++
+  Date:      $Date: 2006/03/28 19:59:05 $
+  Version:   $Revision: 1.6 $
+
+  Copyright (c) Insight Software Consortium. All rights reserved.
+  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
+
+     This software is distributed WITHOUT ANY WARRANTY; without even 
+     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
+     PURPOSE.  See the above copyright notices for more information.
+
+=========================================================================*/
+#ifndef __itkReconstructionLabelMapFilter_h
+#define __itkReconstructionLabelMapFilter_h
+
+#include "itkInPlaceLabelMapFilter.h"
+
+namespace itk {
+/** \class ReconstructionLabelMapFilter
+ * \brief 
+ *
+ * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
+ */
+template<class TImage, class TMarkerImage>
+class ITK_EXPORT ReconstructionLabelMapFilter : 
+    public InPlaceLabelMapFilter<TImage>
+{
+public:
+  /** Standard class typedefs. */
+  typedef ReconstructionLabelMapFilter Self;
+  typedef InPlaceLabelMapFilter<TImage>
+  Superclass;
+  typedef SmartPointer<Self>        Pointer;
+  typedef SmartPointer<const Self>  ConstPointer;
+
+  /** Some convenient typedefs. */
+  typedef TImage ImageType;
+  typedef typename ImageType::Pointer         ImagePointer;
+  typedef typename ImageType::ConstPointer    ImageConstPointer;
+  typedef typename ImageType::PixelType       PixelType;
+  typedef typename ImageType::IndexType       IndexType;
+  typedef typename ImageType::LabelObjectType LabelObjectType;
+  
+  typedef TMarkerImage MarkerImageType;
+  typedef typename MarkerImageType::Pointer         MarkerImagePointer;
+  typedef typename MarkerImageType::ConstPointer    MarkerImageConstPointer;
+  typedef typename MarkerImageType::PixelType       MarkerImagePixelType;
+  
[…]

### 2007-09-18 itkShapeKeepNObjectsLabelCollectionImageFilter.h

@@ -1,134 +1,0 @@
-/*=========================================================================
-
-  Program:   Insight Segmentation & Registration Toolkit
-  Module:    $RCSfile: itkShapeKeepNObjectsLabelCollectionImageFilter.h,v $
-  Language:  C++
-  Date:      $Date: 2006/03/28 19:59:05 $
-  Version:   $Revision: 1.6 $
-
-  Copyright (c) Insight Software Consortium. All rights reserved.
-  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
-
-     This software is distributed WITHOUT ANY WARRANTY; without even 
-     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
-     PURPOSE.  See the above copyright notices for more information.
-
-=========================================================================*/
-#ifndef __itkShapeKeepNObjectsLabelCollectionImageFilter_h
-#define __itkShapeKeepNObjectsLabelCollectionImageFilter_h
-
-#include "itkInPlaceLabelCollectionImageFilter.h"
-
-namespace itk {
-/** \class ShapeKeepNObjectsLabelCollectionImageFilter
- * \brief keep N objects according to their shape attributes
- *
- * ShapeKeepNObjectsLabelCollectionImageFilter keep the N objects in a label collection image
- * with the highest (or lowest) attribute value. The attributes are the ones
- * of the ShapeLabelObject.
- *
- * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
- *
- * \sa ShapeLabelObject, BinaryShapeKeepNObjectsImageFilter, LabelStatisticsKeepNObjectsImageFilter
- * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
- */
-template<class TImage>
-class ITK_EXPORT ShapeKeepNObjectsLabelCollectionImageFilter : 
-    public InPlaceLabelCollectionImageFilter<TImage>
-{
-public:
-  /** Standard class typedefs. */
-  typedef ShapeKeepNObjectsLabelCollectionImageFilter Self;
-  typedef InPlaceLabelCollectionImageFilter<TImage>
-  Superclass;
-  typedef SmartPointer<Self>        Pointer;
-  typedef SmartPointer<const Self>  ConstPointer;
-
-  /** Some convenient typedefs. */
-  typedef TImage ImageType;
[…]

### 2007-09-18 itkShapeLabelCollectionImageFilter.h

@@ -1,174 +1,0 @@
-/*=========================================================================
-
-  Program:   Insight Segmentation & Registration Toolkit
-  Module:    $RCSfile: itkShapeLabelCollectionImageFilter.h,v $
-  Language:  C++
-  Date:      $Date: 2006/03/28 19:59:05 $
-  Version:   $Revision: 1.6 $
-
-  Copyright (c) Insight Software Consortium. All rights reserved.
-  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
-
-     This software is distributed WITHOUT ANY WARRANTY; without even 
-     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
-     PURPOSE.  See the above copyright notices for more information.
-
-=========================================================================*/
-#ifndef __itkShapeLabelCollectionImageFilter_h
-#define __itkShapeLabelCollectionImageFilter_h
-#include "itkLabelPerimeterEstimationCalculator.h"
-
-#include "itkInPlaceLabelCollectionImageFilter.h"
-
-#define PI 3.14159265358979323846
-
-namespace itk {
-/** \class ShapeLabelCollectionImageFilter
- * \brief The valuator class for the ShapeLabelObject
- *
- * ShapeLabelCollectionImageFilter can be used to set the attributes values
- * of the ShapeLabelObject in a LabelCollectionImage.
- *
- * ShapeLabelCollectionImageFilter take an optional parameter, used only to optimize
- * the computation time and the memory usage when the perimeter or the feret diameter
- * are used: the exact copy of the input LabelCollectionImage but stored in an Image.
- * It can be set with SetLabelImage(). It is cleared at the end of the computation, and
- * so must be reset before running Update() again. It is not part of the pipeline management
- * design, to let the subclasses of ShapeLabelCollectionImageFilter use the
- * pipeline desing to specify a really required input.
- *
- * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
- *
- * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
- */
-template<class TImage, class TLabelImage=Image< typename TImage::PixelType, TImage::ImageDimension > >
-class ITK_EXPORT ShapeLabelCollectionImageFilter : 
[…]

### 2007-09-18 itkShapeLabelMapFilter.h

@@ -1,0 +1,174 @@
+/*=========================================================================
+
+  Program:   Insight Segmentation & Registration Toolkit
+  Module:    $RCSfile: itkShapeLabelMapFilter.h,v $
+  Language:  C++
+  Date:      $Date: 2006/03/28 19:59:05 $
+  Version:   $Revision: 1.6 $
+
+  Copyright (c) Insight Software Consortium. All rights reserved.
+  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
+
+     This software is distributed WITHOUT ANY WARRANTY; without even 
+     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
+     PURPOSE.  See the above copyright notices for more information.
+
+=========================================================================*/
+#ifndef __itkShapeLabelMapFilter_h
+#define __itkShapeLabelMapFilter_h
+#include "itkLabelPerimeterEstimationCalculator.h"
+
+#include "itkInPlaceLabelMapFilter.h"
+
+#define PI 3.14159265358979323846
+
+namespace itk {
+/** \class ShapeLabelMapFilter
+ * \brief The valuator class for the ShapeLabelObject
+ *
+ * ShapeLabelMapFilter can be used to set the attributes values
+ * of the ShapeLabelObject in a LabelMap.
+ *
+ * ShapeLabelMapFilter take an optional parameter, used only to optimize
+ * the computation time and the memory usage when the perimeter or the feret diameter
+ * are used: the exact copy of the input LabelMap but stored in an Image.
+ * It can be set with SetLabelImage(). It is cleared at the end of the computation, and
+ * so must be reset before running Update() again. It is not part of the pipeline management
+ * design, to let the subclasses of ShapeLabelMapFilter use the
+ * pipeline desing to specify a really required input.
+ *
+ * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
+ *
+ * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
+ */
+template<class TImage, class TLabelImage=Image< typename TImage::PixelType, TImage::ImageDimension > >
+class ITK_EXPORT ShapeLabelMapFilter : 
+    public InPlaceLabelMapFilter<TImage>
+{
+public:
+  /** Standard class typedefs. */
[…]

### 2007-09-18 itkShapeLabelObject.h

@@ -211,7 +211,7 @@ public:
   /** Run-time type information (and related methods). */
   itkTypeMacro(ShapeLabelObject, LabelObject);
 
-  typedef LabelCollectionImage< Self > LabelCollectionImageType;
+  typedef LabelMap< Self > LabelMapType;
 
   itkStaticConstMacro(ImageDimension, unsigned int, VImageDimension);
 

### 2007-09-18 itkShapeOpeningLabelCollectionImageFilter.h

@@ -1,135 +1,0 @@
-/*=========================================================================
-
-  Program:   Insight Segmentation & Registration Toolkit
-  Module:    $RCSfile: itkShapeOpeningLabelCollectionImageFilter.h,v $
-  Language:  C++
-  Date:      $Date: 2006/03/28 19:59:05 $
-  Version:   $Revision: 1.6 $
-
-  Copyright (c) Insight Software Consortium. All rights reserved.
-  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
-
-     This software is distributed WITHOUT ANY WARRANTY; without even 
-     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
-     PURPOSE.  See the above copyright notices for more information.
-
-=========================================================================*/
-#ifndef __itkShapeOpeningLabelCollectionImageFilter_h
-#define __itkShapeOpeningLabelCollectionImageFilter_h
-
-#include "itkInPlaceLabelCollectionImageFilter.h"
-
-namespace itk {
-/** \class ShapeOpeningLabelCollectionImageFilter
- * \brief remove the objects according to the value of their shape attribute
- *
- * ShapeOpeningLabelCollectionImageFilter removes the objects in a label collection image
- * with an attribute value smaller or greater than a threshold called Lambda.
- * The attributes are the ones of the ShapeLabelObject.
- *
- * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
- *
- * \sa ShapeLabelObject, BinaryShapeOpeningImageFilter, LabelStatisticsOpeningImageFilter
- * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
- */
-template<class TImage>
-class ITK_EXPORT ShapeOpeningLabelCollectionImageFilter : 
-    public InPlaceLabelCollectionImageFilter<TImage>
-{
-public:
-  /** Standard class typedefs. */
-  typedef ShapeOpeningLabelCollectionImageFilter Self;
-  typedef InPlaceLabelCollectionImageFilter<TImage>
-  Superclass;
-  typedef SmartPointer<Self>        Pointer;
-  typedef SmartPointer<const Self>  ConstPointer;
-
-  /** Some convenient typedefs. */
-  typedef TImage ImageType;
[…]

### 2007-09-18 itkShapeRelabelImageFilter.h

@@ -19,11 +19,11 @@
 
 #include "itkImageToImageFilter.h"
 #include "itkShapeLabelObject.h"
-#include "itkLabelCollectionImage.h"
-#include "itkLabelImageToLabelCollectionImageFilter.h"
-#include "itkShapeLabelCollectionImageFilter.h"
-#include "itkShapeRelabelLabelCollectionImageFilter.h"
-#include "itkLabelCollectionImageToLabelImageFilter.h"
+#include "itkLabelMap.h"
+#include "itkLabelImageToLabelMapFilter.h"
+#include "itkShapeLabelMapFilter.h"
+#include "itkShapeRelabelLabelMapFilter.h"
+#include "itkLabelMapToLabelImageFilter.h"
 
 
 namespace itk {
@@ -72,12 +72,12 @@ public:
                       TInputImage::ImageDimension);
 
   typedef ShapeLabelObject<InputImagePixelType, ImageDimension> LabelObjectType;
-  typedef typename itk::LabelCollectionImage< LabelObjectType > LabelCollectionImageType;
-  typedef typename itk::LabelImageToLabelCollectionImageFilter< InputImageType, LabelCollectionImageType > LabelizerType;
-  typedef typename itk::ShapeLabelCollectionImageFilter< LabelCollectionImageType > LabelObjectValuatorType;
+  typedef typename itk::LabelMap< LabelObjectType > LabelMapType;
+  typedef typename itk::LabelImageToLabelMapFilter< InputImageType, LabelMapType > LabelizerType;
+  typedef typename itk::ShapeLabelMapFilter< LabelMapType > LabelObjectValuatorType;
   typedef typename LabelObjectType::AttributeType AttributeType;
-  typedef typename itk::ShapeRelabelLabelCollectionImageFilter< LabelCollectionImageType > RelabelType;
-  typedef typename itk::LabelCollectionImageToLabelImageFilter< LabelCollectionImageType, OutputImageType > BinarizerType;
+  typedef typename itk::ShapeRelabelLabelMapFilter< LabelMapType > RelabelType;
+  typedef typename itk::LabelMapToLabelImageFilter< LabelMapType, OutputImageType > BinarizerType;
 
   /** Standard New method. */
   itkNewMacro(Self);  

### 2007-09-18 itkShapeRelabelLabelCollectionImageFilter.h

@@ -1,125 +1,0 @@
-/*=========================================================================
-
-  Program:   Insight Segmentation & Registration Toolkit
-  Module:    $RCSfile: itkShapeRelabelLabelCollectionImageFilter.h,v $
-  Language:  C++
-  Date:      $Date: 2006/03/28 19:59:05 $
-  Version:   $Revision: 1.6 $
-
-  Copyright (c) Insight Software Consortium. All rights reserved.
-  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
-
-     This software is distributed WITHOUT ANY WARRANTY; without even 
-     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
-     PURPOSE.  See the above copyright notices for more information.
-
-=========================================================================*/
-#ifndef __itkShapeRelabelLabelCollectionImageFilter_h
-#define __itkShapeRelabelLabelCollectionImageFilter_h
-
-#include "itkInPlaceLabelCollectionImageFilter.h"
-
-namespace itk {
-/** \class ShapeRelabelLabelCollectionImageFilter
- * \brief relabel objects according to their shape attributes
- *
- * ShapeRelabelImageFilter relabel a label collection image according to the shape attributes of
- * the objects. The label produced are always consecutives.
- *
- * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
- *
- * \sa ShapeLabelObject, RelabelComponentImageFilter
- * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
- */
-template<class TImage >
-class ITK_EXPORT ShapeRelabelLabelCollectionImageFilter : 
-    public InPlaceLabelCollectionImageFilter<TImage>
-{
-public:
-  /** Standard class typedefs. */
-  typedef ShapeRelabelLabelCollectionImageFilter Self;
-  typedef InPlaceLabelCollectionImageFilter<TImage>
-  Superclass;
-  typedef SmartPointer<Self>        Pointer;
-  typedef SmartPointer<const Self>  ConstPointer;
-
-  /** Some convenient typedefs. */
-  typedef TImage ImageType;
-  typedef typename ImageType::Pointer         ImagePointer;
-  typedef typename ImageType::ConstPointer    ImageConstPointer;
[…]

### 2007-09-18 itkStatisticsKeepNObjectsLabelCollectionImageFilter.h

@@ -1,101 +1,0 @@
-/*=========================================================================
-
-  Program:   Insight Segmentation & Registration Toolkit
-  Module:    $RCSfile: itkStatisticsKeepNObjectsLabelCollectionImageFilter.h,v $
-  Language:  C++
-  Date:      $Date: 2006/03/28 19:59:05 $
-  Version:   $Revision: 1.6 $
-
-  Copyright (c) Insight Software Consortium. All rights reserved.
-  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
-
-     This software is distributed WITHOUT ANY WARRANTY; without even 
-     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
-     PURPOSE.  See the above copyright notices for more information.
-
-=========================================================================*/
-#ifndef __itkStatisticsKeepNObjectsLabelCollectionImageFilter_h
-#define __itkStatisticsKeepNObjectsLabelCollectionImageFilter_h
-
-#include "itkShapeKeepNObjectsLabelCollectionImageFilter.h"
-#include "itkStatisticsLabelObject.h"
-
-namespace itk {
-/** \class StatisticsKeepNObjectsLabelCollectionImageFilter
- * \brief keep N objects according to their statistics attributes
- *
- * StatisticsKeepNObjectsLabelCollectionImageFilter keep the N objects in a label collection image
- * with the highest (or lowest) attribute value. The attributes are the ones
- * of the StatisticsLabelObject.
- *
- * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
- *
- * \sa StatisticsLabelObject, BinaryStatisticsKeepNObjectsImageFilter, LabelShapeKeepNObjectsImageFilter
- * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
- */
-template<class TImage>
-class ITK_EXPORT StatisticsKeepNObjectsLabelCollectionImageFilter : 
-    public ShapeKeepNObjectsLabelCollectionImageFilter<TImage>
-{
-public:
-  /** Standard class typedefs. */
-  typedef StatisticsKeepNObjectsLabelCollectionImageFilter Self;
-  typedef ShapeKeepNObjectsLabelCollectionImageFilter<TImage>
-  Superclass;
-  typedef SmartPointer<Self>        Pointer;
[…]

### 2007-09-18 itkStatisticsLabelCollectionImageFilter.h

@@ -1,133 +1,0 @@
-/*=========================================================================
-
-  Program:   Insight Segmentation & Registration Toolkit
-  Module:    $RCSfile: itkStatisticsLabelCollectionImageFilter.h,v $
-  Language:  C++
-  Date:      $Date: 2006/03/28 19:59:05 $
-  Version:   $Revision: 1.6 $
-
-  Copyright (c) Insight Software Consortium. All rights reserved.
-  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
-
-     This software is distributed WITHOUT ANY WARRANTY; without even 
-     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
-     PURPOSE.  See the above copyright notices for more information.
-
-=========================================================================*/
-#ifndef __itkStatisticsLabelCollectionImageFilter_h
-#define __itkStatisticsLabelCollectionImageFilter_h
-
-#include "itkShapeLabelCollectionImageFilter.h"
-
-namespace itk {
-/** \class StatisticsLabelCollectionImageFilter
- * \brief The valuator class for the ShapeLabelObject
- *
- * StatisticsCollectionImageFilter can be used to set the attributes values
- * of the StatisticsLabelObject in a LabelCollectionImage.
- *
- * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
- *
- * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
- */
-template<class TImage, class TFeatureImage>
-class ITK_EXPORT StatisticsLabelCollectionImageFilter : 
-    public ShapeLabelCollectionImageFilter<TImage>
-{
-public:
-  /** Standard class typedefs. */
-  typedef StatisticsLabelCollectionImageFilter Self;
-  typedef ShapeLabelCollectionImageFilter<TImage>
-  Superclass;
-  typedef SmartPointer<Self>        Pointer;
-  typedef SmartPointer<const Self>  ConstPointer;
-
-  /** Some convenient typedefs. */
-  typedef TImage ImageType;
-  typedef typename ImageType::Pointer          ImagePointer;
-  typedef typename ImageType::ConstPointer     ImageConstPointer;
-  typedef typename ImageType::PixelType        PixelType;
-  typedef typename ImageType::IndexType        IndexType;
[…]

### 2007-09-18 itkStatisticsLabelMapFilter.h

@@ -1,0 +1,133 @@
+/*=========================================================================
+
+  Program:   Insight Segmentation & Registration Toolkit
+  Module:    $RCSfile: itkStatisticsLabelMapFilter.h,v $
+  Language:  C++
+  Date:      $Date: 2006/03/28 19:59:05 $
+  Version:   $Revision: 1.6 $
+
+  Copyright (c) Insight Software Consortium. All rights reserved.
+  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
+
+     This software is distributed WITHOUT ANY WARRANTY; without even 
+     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
+     PURPOSE.  See the above copyright notices for more information.
+
+=========================================================================*/
+#ifndef __itkStatisticsLabelMapFilter_h
+#define __itkStatisticsLabelMapFilter_h
+
+#include "itkShapeLabelMapFilter.h"
+
+namespace itk {
+/** \class StatisticsLabelMapFilter
+ * \brief The valuator class for the ShapeLabelObject
+ *
+ * StatisticsCollectionImageFilter can be used to set the attributes values
+ * of the StatisticsLabelObject in a LabelMap.
+ *
+ * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
+ *
+ * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
+ */
+template<class TImage, class TFeatureImage>
+class ITK_EXPORT StatisticsLabelMapFilter : 
+    public ShapeLabelMapFilter<TImage>
+{
+public:
+  /** Standard class typedefs. */
+  typedef StatisticsLabelMapFilter Self;
+  typedef ShapeLabelMapFilter<TImage>
+  Superclass;
+  typedef SmartPointer<Self>        Pointer;
+  typedef SmartPointer<const Self>  ConstPointer;
+
+  /** Some convenient typedefs. */
+  typedef TImage ImageType;
+  typedef typename ImageType::Pointer          ImagePointer;
+  typedef typename ImageType::ConstPointer     ImageConstPointer;
+  typedef typename ImageType::PixelType        PixelType;
+  typedef typename ImageType::IndexType        IndexType;
+  typedef typename ImageType::PointType        PointType;
[…]

### 2007-09-18 itkStatisticsLabelObject.h

@@ -263,7 +263,7 @@ public:
   /** Run-time type information (and related methods). */
   itkTypeMacro(StatisticsLabelObject, LabelObject);
 
-  typedef LabelCollectionImage< Self > LabelCollectionImageType;
+  typedef LabelMap< Self > LabelMapType;
 
   itkStaticConstMacro(ImageDimension, unsigned int, VImageDimension);
 

### 2007-09-18 itkStatisticsOpeningLabelCollectionImageFilter.h

@@ -1,104 +1,0 @@
-/*=========================================================================
-
-  Program:   Insight Segmentation & Registration Toolkit
-  Module:    $RCSfile: itkStatisticsOpeningLabelCollectionImageFilter.h,v $
-  Language:  C++
-  Date:      $Date: 2006/03/28 19:59:05 $
-  Version:   $Revision: 1.6 $
-
-  Copyright (c) Insight Software Consortium. All rights reserved.
-  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
-
-     This software is distributed WITHOUT ANY WARRANTY; without even 
-     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
-     PURPOSE.  See the above copyright notices for more information.
-
-=========================================================================*/
-#ifndef __itkStatisticsOpeningLabelCollectionImageFilter_h
-#define __itkStatisticsOpeningLabelCollectionImageFilter_h
-
-#include "itkShapeOpeningLabelCollectionImageFilter.h"
-#include "itkStatisticsLabelObject.h"
-
-namespace itk {
-/** \class StatisticsOpeningLabelCollectionImageFilter
- * \brief remove the objects according to the value of their statistics attribute
- *
- * StatisticsOpeningLabelCollectionImageFilter removes the objects in a lavbel collection image
- * with an attribute value smaller or greater than a threshold called Lambda.
- * The attributes are the ones of the StatisticsLabelObject.
- *
- * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
- *
- * \sa StatisticsLabelObject, BinaryStatisticsOpeningImageFilter, LabelShapeOpeningImageFilter
- * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
- */
-template<class TImage>
-class ITK_EXPORT StatisticsOpeningLabelCollectionImageFilter : 
-    public ShapeOpeningLabelCollectionImageFilter<TImage>
-{
-public:
-  /** Standard class typedefs. */
-  typedef StatisticsOpeningLabelCollectionImageFilter Self;
-  typedef ShapeOpeningLabelCollectionImageFilter<TImage>
-  Superclass;
-  typedef SmartPointer<Self>        Pointer;
-  typedef SmartPointer<const Self>  ConstPointer;
-
[…]

### 2007-09-18 itkStatisticsRelabelImageFilter.h

@@ -19,11 +19,11 @@
 
 #include "itkImageToImageFilter.h"
 #include "itkStatisticsLabelObject.h"
-#include "itkLabelCollectionImage.h"
-#include "itkLabelImageToLabelCollectionImageFilter.h"
-#include "itkStatisticsLabelCollectionImageFilter.h"
-#include "itkStatisticsRelabelLabelCollectionImageFilter.h"
-#include "itkLabelCollectionImageToLabelImageFilter.h"
+#include "itkLabelMap.h"
+#include "itkLabelImageToLabelMapFilter.h"
+#include "itkStatisticsLabelMapFilter.h"
+#include "itkStatisticsRelabelLabelMapFilter.h"
+#include "itkLabelMapToLabelImageFilter.h"
 
 
 namespace itk {
@@ -77,12 +77,12 @@ public:
                       TInputImage::ImageDimension);
 
   typedef StatisticsLabelObject<InputImagePixelType, ImageDimension> LabelObjectType;
-  typedef typename itk::LabelCollectionImage< LabelObjectType > LabelCollectionImageType;
-  typedef typename itk::LabelImageToLabelCollectionImageFilter< InputImageType, LabelCollectionImageType > LabelizerType;
-  typedef typename itk::StatisticsLabelCollectionImageFilter< LabelCollectionImageType, TFeatureImage > LabelObjectValuatorType;
+  typedef typename itk::LabelMap< LabelObjectType > LabelMapType;
+  typedef typename itk::LabelImageToLabelMapFilter< InputImageType, LabelMapType > LabelizerType;
+  typedef typename itk::StatisticsLabelMapFilter< LabelMapType, TFeatureImage > LabelObjectValuatorType;
   typedef typename LabelObjectType::AttributeType AttributeType;
-  typedef typename itk::StatisticsRelabelLabelCollectionImageFilter< LabelCollectionImageType > RelabelType;
-  typedef typename itk::LabelCollectionImageToLabelImageFilter< LabelCollectionImageType, OutputImageType > BinarizerType;
+  typedef typename itk::StatisticsRelabelLabelMapFilter< LabelMapType > RelabelType;
+  typedef typename itk::LabelMapToLabelImageFilter< LabelMapType, OutputImageType > BinarizerType;
 
   /** Standard New method. */
   itkNewMacro(Self);  

### 2007-09-18 itkStatisticsRelabelLabelCollectionImageFilter.h

@@ -1,102 +1,0 @@
-/*=========================================================================
-
-  Program:   Insight Segmentation & Registration Toolkit
-  Module:    $RCSfile: itkStatisticsRelabelLabelCollectionImageFilter.h,v $
-  Language:  C++
-  Date:      $Date: 2006/03/28 19:59:05 $
-  Version:   $Revision: 1.6 $
-
-  Copyright (c) Insight Software Consortium. All rights reserved.
-  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
-
-     This software is distributed WITHOUT ANY WARRANTY; without even 
-     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
-     PURPOSE.  See the above copyright notices for more information.
-
-=========================================================================*/
-#ifndef __itkStatisticsRelabelLabelCollectionImageFilter_h
-#define __itkStatisticsRelabelLabelCollectionImageFilter_h
-
-#include "itkShapeRelabelLabelCollectionImageFilter.h"
-#include "itkStatisticsLabelObject.h"
-
-namespace itk {
-/** \class StatisticsRelabelLabelCollectionImageFilter
- * \brief relabel objects according to their shape attributes
- *
- * StatisticsRelabelLabelCollectionImageFilter relabel a label collection image according to the statistics attributes of
- * the objects. The label produced are always consecutives.
- *
- * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
- *
- * \sa StatisticsLabelObject, RelabelComponentImageFilter
- * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
- */
-template<class TImage >
-class ITK_EXPORT StatisticsRelabelLabelCollectionImageFilter : 
-    public ShapeRelabelLabelCollectionImageFilter<TImage>
-{
-public:
-  /** Standard class typedefs. */
-  typedef StatisticsRelabelLabelCollectionImageFilter Self;
-  typedef ShapeRelabelLabelCollectionImageFilter<TImage>
-  Superclass;
-  typedef SmartPointer<Self>        Pointer;
-  typedef SmartPointer<const Self>  ConstPointer;
-
-  /** Some convenient typedefs. */
-  typedef TImage ImageType;
-  typedef typename ImageType::Pointer         ImagePointer;
[…]

### 2007-09-18 example.py
don't use the Object word alone, but always use LabelObject to be consistent with the rest of the contribution
darcs-hash:20070918095222-2fc9d-2f1f28a72294bb0e5871a9ba3d061a666939879e.gz

@@ -56,11 +56,11 @@ srelabel = itk.StatisticsRelabelLabelMapFilter[LabelMapType].New(skeep, Attribut
 # - the spot position
 # - the mean value in the nucleus in the spot zone
 print "nuclei", "x", "y", "mean"
-for nl in range(1, relabel.GetOutput().GetNumberOfObjects()+1):
+for nl in range(1, relabel.GetOutput().GetNumberOfLabelObjects()+1):
 	maskSpots.SetLabel(nl)
 	srelabel.UpdateLargestPossibleRegion()
 	labeCollection = srelabel.GetOutput()
-	for l in range(1, labeCollection.GetNumberOfObjects()+1):
+	for l in range(1, labeCollection.GetNumberOfLabelObjects()+1):
 		lo = labeCollection.GetLabelObject(l)
 		print nl, lo.GetCentroid()[0], lo.GetCentroid()[1], lo.GetMean()
 

### 2007-09-18 itkLabelMap.h

@@ -289,7 +289,7 @@ public:
   /**
    * Return the numbner of label objects in the image
    */
-  unsigned long GetNumberOfObjects() const;
+  unsigned long GetNumberOfLabelObjects() const;
   
   /**
    * Set/Get the background label
@@ -308,10 +308,10 @@ public:
    * Print all the objects stored in that collection - a convenient method
    * for prototyping.
    */
-  void PrintObjects(std::ostream& os) const;
-  void PrintObjects() const
+  void PrintLabelObjects(std::ostream& os) const;
+  void PrintLabelObjects() const
     {
-    this->PrintObjects( std::cerr );
+    this->PrintLabelObjects( std::cerr );
     }
 
 protected:

### 2007-09-18 article/Article.tex
a note about how to fix sources after the changes of the class names
darcs-hash:20070918095841-2fc9d-74591518f8642e30dec758a1caad59afc8b30bd3.gz

@@
 
+Note that some names have been changed in revision 3. To fix your sources, the following commands can be used in your source directory:
+\small \begin{verbatim}
+perl -e 's/LabelCollectionImage/LabelMap/g' -pi *
+perl -e 's/GetNumberOfObjects/GetNumberOfLabelObjects/g' -pi *
+perl -e 's/PrintObjects/PrintLabelObjects/g' -pi *
+\end{verbatim} \normalsize
+
 \section{Conclusion}

### 2007-09-18 article/Article.tex
labeled -> label
darcs-hash:20070918100057-2fc9d-1f475aa1b95dd6d137ebabc31de9d7016a3d3f67.gz

@@
 % the relevant document. 
-\title{Labeled object representation and manipulation with ITK}
+\title{Label object representation and manipulation with ITK}
 
@@
 objects for this task, a new set of classes have been developed to represent and
-manipulate the labeled images and the objects within them in ITK.
-Those new classes have been used to implement several labeled images
+manipulate the label images and the objects within them in ITK.
+Those new classes have been used to implement several label images
 manipulation based on object attributes, as well as the binary specialization of
@@
 producing an image of the same size with a single pixel value per object. This
-image is called a labeled image. There are several way to create this image. It
+image is called a label image. There are several way to create this image. It
 can be done by searching the connected components in a binary image, it can be
@@
 
-\subsection{Labeled image}
-
-A label image is an image which contains several labeled pixels. Often, the
+\subsection{Label image}
+
+A label image is an image which contains several label pixels. Often, the
 labels are representing some objects placed on a background, and so the label
@@
 and the other label in the image are considered as the background. A side effect
-of that is that a labeled image can be considered as a binary image, and so, it
-let us manipulate a single object in a labeled image.
+of that is that a label image can be considered as a binary image, and so, it
+let us manipulate a single object in a label image.
 
@@
 
-In ITK, the labeled and the binary images are implemented as a simple {\em
+In ITK, the label and the binary images are implemented as a simple {\em
 itk::Image}. The pixel types used are most of the time integral, signed or
@@
 
-The filter dedicated to the manipulation of labeled images have the word "Label"
+The filter dedicated to the manipulation of label images have the word "Label"
 somewhere in there name. Again, it seem to be a good practice which have been
@@
 
-The labeled images are often used the represent the connected components of an
+The label images are often used the represent the connected components of an
 image. In this contribution, another representation has been chosen.
@@
 The {\em itk::LabelMap} class is in charge of managing the
-collection of labeled
+collection of label
 objects of the image, as well as storing the metadata associated with the image
@@
 The {\em itk::LabelMap} is a templated class, which take a single
-parameter: the type of {\em labeled object} stored by that class. The dimension
-of the image is took from the {\em labeled object} class, and thus don't need to
+parameter: the type of {\em label object} stored by that class. The dimension
+of the image is took from the {\em label object} class, and thus don't need to
 be defined as template parameter of that class. The pixel type of the image
-also comes from the {\em labeled object} class.
+also comes from the {\em label object} class.
 
@@
 Several subclasses are provided with that contribution, to cover the most common
-usages of the labeled objects manipulation:
+usages of the label objects manipulation:
 \begin{itemize}
@@
   \item {\em itk::ShapeLabelObject} contains numerous attribute related to the
-shape of the labeled object. Computing the values of those attributes does not
+shape of the label object. Computing the values of those attributes does not
 require a feaure image.
   \item {\em itk::StatisticsLabelObject} contains numerous statistics about the
-grey values of a feature image in the same place than the labeled object.
+grey values of a feature image in the same place than the label object.
 Computing the values of those attributes {\em does} require a feature image.
@@
 The {\em itk::LabelMap} class provide some methods to fill the
-image "by hand", like the usual {\em SetPixel()} method. However, the most efficient way is to convert a labeled image or a binary
+image "by hand", like the usual {\em SetPixel()} method. However, the most efficient way is to convert a label image or a binary
 image stored in an {\em itk::Image} to a {\em itk::LabelMap}, by
@@
   \item The {\em itk::LabelMapToLabelImageFilter} class simply
-convert a {\em itk::LabelMap} to a labeled image stored in a {\em
+convert a {\em itk::LabelMap} to a label image stored in a {\em
 itk::Image}.
@@
 
-Because the objects are often get from a labeled image or from a binary image,
-those filters have been made for binary, and labeled images.
+Because the objects are often get from a label image or from a binary image,
+those filters have been made for binary, and label images.
 

### 2007-09-20 article/Article.tex
rename methods in the article
darcs-hash:20070920123233-2fc9d-a8b726f8f3759abc5199523b6182ba40bdfaa3b5.gz

@@
   LabelCollectionType::Pointer collection = shape->GetOutput();
-  for( int label=1; label<collection->GetNumberOfObjects(); label++ )
+  for( int label=1; label<collection->GetNumberOfLabelObjects(); label++ )
     {
@@
 
-for nl in range(1, relabel.GetOutput().GetNumberOfObjects()+1):
+for nl in range(1, relabel.GetOutput().GetNumberOfLabelObjects()+1):
   maskSpots.SetLabel(nl)
@@
 
-  for l in range(1, labeCollection.GetNumberOfObjects()+1):
+  for l in range(1, labeCollection.GetNumberOfLabelObjects()+1):
     lo = labeCollection.GetLabelObject(l)

### 2007-09-20 article/Article.tex
add the PhysicalSizeOnBorder attribute
darcs-hash:20070920143450-2fc9d-494b4be0990dbbb4c8e7a181769629bd3dc5c4a4.gz

@@
 
-The {\em itk::LabelObject} class represent the label obejcts. It has two main
+The {\em itk::LabelObject} class represent the label objects. It has two main
 features:
@@
   \item {\em SizeOnBorder} is the number of pixels in the objects which are on the border
-of the image. This attribute is particulary useful to remove the objects which are touching
+of the image. A pixel on several borders (a pixel in a corner) is counted only one time, so the
+size on border can't be greater than the size of the object.
+This attribute is particulary useful to remove the objects which are touching
 too much the border. Its type is {\em unsigned long}.
+  \item {\em PhysicalSizeOnBorder} is the physical size of the objects which are on the border
+of the image. In 2D, it is a distance, in 3D, a surface, etc. Contrary to the {\em PhysicalSize}
+attribute which is directly linked to the {\em Size}, this attribute is not directly
+linked to the {\em SizeOnBorder} attribute. This attribute is particulary useful to remove
+the objects which are touching too much the border. Its type is {\em double}.
   \item {\em FeretDiameter} is the diameter in physical units of the sphere which include

### 2007-09-20 itkShapeLabelObject.h

@@ -92,6 +92,19 @@ public:
 };
 
 template< class TLabelObject >
+class ITK_EXPORT PhysicalSizeOnBorderLabelObjectAccessor
+{
+public:
+  typedef TLabelObject LabelObjectType;
+  typedef double AttributeValueType;
+
+  inline const AttributeValueType operator()( const LabelObjectType * labelObject )
+    {
+    return labelObject->GetPhysicalSizeOnBorder();
+    }
+};
+
+template< class TLabelObject >
 class ITK_EXPORT CentroidLabelObjectAccessor
 {
 public:
@@ -233,12 +246,13 @@ public:
   static const AttributeType CENTROID=4;
   static const AttributeType REGION=5;
   static const AttributeType SIZE_ON_BORDER=6;
-  static const AttributeType FERET_DIAMETER=7;
-  static const AttributeType BINARY_PRINCIPAL_MOMENTS=8;
-  static const AttributeType BINARY_PRINCIPAL_AXES=9;
-  static const AttributeType BINARY_ELONGATION=10;
-  static const AttributeType PERIMETER=11;
-  static const AttributeType ROUNDNESS=12;
+  static const AttributeType PHYSICAL_SIZE_ON_BORDER=7;
+  static const AttributeType FERET_DIAMETER=8;
+  static const AttributeType BINARY_PRINCIPAL_MOMENTS=9;
+  static const AttributeType BINARY_PRINCIPAL_AXES=10;
+  static const AttributeType BINARY_ELONGATION=11;
+  static const AttributeType PERIMETER=12;
+  static const AttributeType ROUNDNESS=13;
 
   static AttributeType GetAttributeFromName( const std::string & s )
     {
@@ -269,6 +283,10 @@ public:
     else if( s == "SizeOnBorder" )
       {
       return SIZE_ON_BORDER;
+      }
+    else if( s == "PhysicalSizeOnBorder" )
+      {
+      return PHYSICAL_SIZE_ON_BORDER;
       }
     else if( s == "FeretDiameter" )
       {
@@ -321,6 +339,9 @@ public:
         break;
       case SIZE_ON_BORDER:
         return "SizeOnBorder";
+        break;
+      case PHYSICAL_SIZE_ON_BORDER:
+        return "PhysicalSizeOnBorder";
         break;
       case FERET_DIAMETER:
[…]

### 2007-09-20 itkAttributeLabelObject.h
the reconstruction filter only set a value to the objects
darcs-hash:20070920155007-2fc9d-195abbd3a388ccc382af2092ccd2ecfffa69dbf6.gz

@@ -36,6 +36,11 @@ public:
     {
     return labelObject->GetAttribute();
     }
+
+  inline void operator()( LabelObjectType * labelObject, AttributeValueType value )
+    {
+    labelObject->SetAttribute( value );
+    }
 };
 
 }

### 2007-09-20 itkBinaryReconstructionByDilationImageFilter.h

@@ -18,10 +18,11 @@
 #define __itkBinaryReconstructionByDilationImageFilter_h
 
 #include "itkImageToImageFilter.h"
-#include "itkLabelObject.h"
+#include "itkAttributeLabelObject.h"
 #include "itkLabelMap.h"
 #include "itkBinaryImageToLabelMapFilter.h"
-#include "itkReconstructionLabelMapFilter.h"
+#include "itkBinaryReconstructionLabelMapFilter.h"
+#include "itkAttributeOpeningLabelMapFilter.h"
 #include "itkLabelMapToBinaryImageFilter.h"
 
 
@@ -77,10 +78,11 @@ public:
   itkStaticConstMacro(ImageDimension, unsigned int,
                       TInputImage::ImageDimension);
 
-  typedef LabelObject<unsigned long, ImageDimension> LabelObjectType;
+  typedef AttributeLabelObject<unsigned long, ImageDimension, bool> LabelObjectType;
   typedef typename itk::LabelMap< LabelObjectType > LabelMapType;
   typedef typename itk::BinaryImageToLabelMapFilter< InputImageType, LabelMapType > LabelizerType;
-  typedef typename itk::ReconstructionLabelMapFilter< LabelMapType, InputImageType > ReconstructionType;
+  typedef typename itk::BinaryReconstructionLabelMapFilter< LabelMapType, InputImageType > ReconstructionType;
+  typedef typename itk::AttributeOpeningLabelMapFilter< LabelMapType > OpeningType;
   typedef typename itk::LabelMapToBinaryImageFilter< LabelMapType, OutputImageType > BinarizerType;
 
   /** Standard New method. */

### 2007-09-20 itkBinaryReconstructionByErosionImageFilter.h

@@ -18,11 +18,12 @@
 #define __itkBinaryReconstructionByErosionImageFilter_h
 
 #include "itkImageToImageFilter.h"
-#include "itkLabelObject.h"
+#include "itkAttributeLabelObject.h"
 #include "itkLabelMap.h"
 #include "itkBinaryNotImageFilter.h"
 #include "itkBinaryImageToLabelMapFilter.h"
-#include "itkReconstructionLabelMapFilter.h"
+#include "itkBinaryReconstructionLabelMapFilter.h"
+#include "itkAttributeOpeningLabelMapFilter.h"
 #include "itkLabelMapToMaskImageFilter.h"
 
 
@@ -77,10 +78,11 @@ public:
                       TInputImage::ImageDimension);
 
   typedef BinaryNotImageFilter< InputImageType > NotType;
-  typedef LabelObject<unsigned long, ImageDimension> LabelObjectType;
+  typedef AttributeLabelObject<unsigned long, ImageDimension, bool> LabelObjectType;
   typedef typename itk::LabelMap< LabelObjectType > LabelMapType;
   typedef typename itk::BinaryImageToLabelMapFilter< InputImageType, LabelMapType > LabelizerType;
-  typedef typename itk::ReconstructionLabelMapFilter< LabelMapType, InputImageType > ReconstructionType;
+  typedef typename itk::BinaryReconstructionLabelMapFilter< LabelMapType, InputImageType > ReconstructionType;
+  typedef typename itk::AttributeOpeningLabelMapFilter< LabelMapType > OpeningType;
   typedef typename itk::LabelMapToMaskImageFilter< LabelMapType, OutputImageType > BinarizerType;
 
   /** Standard New method. */

### 2007-09-20 itkBinaryReconstructionLabelMapFilter.h

@@ -1,7 +1,7 @@
 /*=========================================================================
 
   Program:   Insight Segmentation & Registration Toolkit
-  Module:    $RCSfile: itkReconstructionLabelMapFilter.h,v $
+  Module:    $RCSfile: itkBinaryReconstructionLabelMapFilter.h,v $
   Language:  C++
   Date:      $Date: 2006/03/28 19:59:05 $
   Version:   $Revision: 1.6 $
@@ -14,24 +14,26 @@
      PURPOSE.  See the above copyright notices for more information.
 
 =========================================================================*/
-#ifndef __itkReconstructionLabelMapFilter_h
-#define __itkReconstructionLabelMapFilter_h
+#ifndef __itkBinaryReconstructionLabelMapFilter_h
+#define __itkBinaryReconstructionLabelMapFilter_h
 
 #include "itkInPlaceLabelMapFilter.h"
+#include "itkAttributeLabelObject.h"
 
 namespace itk {
-/** \class ReconstructionLabelMapFilter
+/** \class BinaryReconstructionLabelMapFilter
  * \brief 
  *
  * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
  */
-template<class TImage, class TMarkerImage>
-class ITK_EXPORT ReconstructionLabelMapFilter : 
+template<class TImage, class TMarkerImage, class TAttributeAccessor=
+  typename Functor::AttributeLabelObjectAccessor< typename TImage::LabelObjectType > >
+class ITK_EXPORT BinaryReconstructionLabelMapFilter : 
     public InPlaceLabelMapFilter<TImage>
 {
 public:
   /** Standard class typedefs. */
-  typedef ReconstructionLabelMapFilter Self;
+  typedef BinaryReconstructionLabelMapFilter Self;
   typedef InPlaceLabelMapFilter<TImage>
   Superclass;
   typedef SmartPointer<Self>        Pointer;
@@ -50,6 +52,8 @@ public:
   typedef typename MarkerImageType::ConstPointer    MarkerImageConstPointer;
   typedef typename MarkerImageType::PixelType       MarkerImagePixelType;
   
+  typedef TAttributeAccessor AttributeAccessorType;
+
   /** ImageDimension constants */
   itkStaticConstMacro(ImageDimension, unsigned int,
                       TImage::ImageDimension);
@@ -58,7 +62,7 @@ public:
[…]

### 2007-09-21 itkLabelMapToRGBImageFilter.h
add a class to convert a label map to a color image - not tested yet
darcs-hash:20070921092220-2fc9d-d2e7d079ef4f411c69383ef48202825f0e91da76.gz

@@ -1,0 +1,98 @@
+/*=========================================================================
+
+  Program:   Insight Segmentation & Registration Toolkit
+  Module:    $RCSfile: itkLabelMapToRGBImageFilter.h,v $
+  Language:  C++
+  Date:      $Date: 2005/08/23 15:09:03 $
+  Version:   $Revision: 1.4 $
+
+  Copyright (c) Insight Software Consortium. All rights reserved.
+  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
+
+     This software is distributed WITHOUT ANY WARRANTY; without even 
+     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
+     PURPOSE.  See the above copyright notices for more information.
+
+=========================================================================*/
+#ifndef __itkLabelMapToRGBImageFilter_h
+#define __itkLabelMapToRGBImageFilter_h
+
+#include "itkLabelMapFilter.h"
+#include "itkLabelToRGBFunctor.h"
+
+
+namespace itk {
+
+/** \class LabelMapToRGBImageFilter
+ * \brief Convert a LabelMap to a colored image
+ *
+ * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
+ *
+ * \sa LabelMapToBinaryImageFilter, LabelMapMaskImageFilter
+ * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
+ */
+template<class TInputImage, class TOutputImage>
+class ITK_EXPORT LabelMapToRGBImageFilter : 
+    public LabelMapFilter<TInputImage, TOutputImage>
+{
+public:
+  /** Standard class typedefs. */
+  typedef LabelMapToRGBImageFilter Self;
+  typedef LabelMapFilter<TInputImage, TOutputImage>
+  Superclass;
+  typedef SmartPointer<Self>        Pointer;
+  typedef SmartPointer<const Self>  ConstPointer;
+
+  /** Some convenient typedefs. */
+  typedef TInputImage InputImageType;
+  typedef TOutputImage OutputImageType;
+  typedef typename InputImageType::Pointer         InputImagePointer;
+  typedef typename InputImageType::ConstPointer    InputImageConstPointer;
+  typedef typename InputImageType::RegionType      InputImageRegionType;
+  typedef typename InputImageType::PixelType       InputImagePixelType;
[…]

### 2007-09-21 article/Article.tex
the reconstruction filter only set a value to the objects
darcs-hash:20070920155007-2fc9d-195abbd3a388ccc382af2092ccd2ecfffa69dbf6.gz
rename LabelMapToMaskImageFilter to LabelMapMaskImageFilter
darcs-hash:20070921092354-2fc9d-9e8470b140b4051c6694686d1f026478a9032f52.gz

@@
 of the largest principal moment by the smallest principal moment. Its value is greater
-or equal to $1$· Its type si {\em double}.
+or equal to $1$. Its type si {\em double}.
 %   \item {\em Perimeter}
@@
 original image can also be restored by this filter.
-  \item The {\em itk::LabelMapToMaskImageFilter} class can be used
+  \item The {\em itk::LabelMapMaskImageFilter} class can be used
 to mask an image with the objects of the {\em itk::LabelMap}. With
@@
 
-The {\em itk::LabelMapToMaskImageFilter} class let the user mask
+The {\em itk::LabelMapMaskImageFilter} class let the user mask
 a part of an {\em itk::Image} with the objects of a {\em itk::LabelMap}.
@@
 #include "itkLabelImageToLabelMapFilter.h"
-#include "itkLabelMapToMaskImageFilter.h"
+#include "itkLabelMapMaskImageFilter.h"
 
@@
 \small \begin{verbatim}
-  typedef itk::LabelMapToMaskImageFilter< LabelMapType, ImageType > MaskType;
+  typedef itk::LabelMapMaskImageFilter< LabelMapType, ImageType > MaskType;
   MaskType::Pointer mask = MaskType::New();
@@
 \small \begin{verbatim}
-maskSpots = itk.LabelMapToMaskImageFilter.LI2IUC2.New(relabel, spots, Label=1,
+maskSpots = itk.LabelMapMaskImageFilter.LI2IUC2.New(relabel, spots, Label=1,
     Crop=True, CropBorder=2)
@@
 
-Note that some names have been changed in revision 3. To fix your sources, the following commands can be used in your source directory:
+Note that some names have been changed in revision 3. To fix your sources, the following commands can be used in your source directory (order is important):
 \small \begin{verbatim}
@@
 perl -e 's/PrintObjects/PrintLabelObjects/g' -pi *
+perl -e 's/LabelMapToMaskImageFilter/LabelMapMaskImageFilter/g' -pi *
 \end{verbatim} \normalsize

### 2007-09-21 example.py

@@ -40,7 +40,7 @@ itk.write(overlay, "nuclei-overlay.png")
 
 spots = itk.ImageFileReader[ImageType].New(FileName="images/spots.png")
 # mask the spot image to keep only the nucleus zone. The rest of the image is cropped, excepted a border of 2 pixels
-maskSpots = itk.LabelMapToMaskImageFilter[LabelMapType, ImageType].New(relabel, spots, Label=1, Crop=True, CropBorder=2)
+maskSpots = itk.LabelMapMaskImageFilter[LabelMapType, ImageType].New(relabel, spots, Label=1, Crop=True, CropBorder=2)
 th = itk.BinaryThresholdImageFilter[ImageType, ImageType].New(maskSpots, LowerThreshold=110)
 slabel = itk.BinaryImageToLabelMapFilter[ImageType, LabelMapType].New(th)
 sstats = itk.StatisticsLabelMapFilter[LabelMapType, ImageType].New(slabel, nuclei)

### 2007-09-21 itkBinaryReconstructionByErosionImageFilter.h

@@ -24,7 +24,7 @@
 #include "itkBinaryImageToLabelMapFilter.h"
 #include "itkBinaryReconstructionLabelMapFilter.h"
 #include "itkAttributeOpeningLabelMapFilter.h"
-#include "itkLabelMapToMaskImageFilter.h"
+#include "itkLabelMapMaskImageFilter.h"
 
 
 namespace itk {
@@ -83,7 +83,7 @@ public:
   typedef typename itk::BinaryImageToLabelMapFilter< InputImageType, LabelMapType > LabelizerType;
   typedef typename itk::BinaryReconstructionLabelMapFilter< LabelMapType, InputImageType > ReconstructionType;
   typedef typename itk::AttributeOpeningLabelMapFilter< LabelMapType > OpeningType;
-  typedef typename itk::LabelMapToMaskImageFilter< LabelMapType, OutputImageType > BinarizerType;
+  typedef typename itk::LabelMapMaskImageFilter< LabelMapType, OutputImageType > BinarizerType;
 
   /** Standard New method. */
   itkNewMacro(Self);  

### 2007-09-21 itkLabelMapMaskImageFilter.h

@@ -1,7 +1,7 @@
 /*=========================================================================
 
   Program:   Insight Segmentation & Registration Toolkit
-  Module:    $RCSfile: itkLabelMapToMaskImageFilter.h,v $
+  Module:    $RCSfile: itkLabelMapMaskImageFilter.h,v $
   Language:  C++
   Date:      $Date: 2005/08/23 15:09:03 $
   Version:   $Revision: 1.4 $
@@ -14,21 +14,21 @@
      PURPOSE.  See the above copyright notices for more information.
 
 =========================================================================*/
-#ifndef __itkLabelMapToMaskImageFilter_h
-#define __itkLabelMapToMaskImageFilter_h
+#ifndef __itkLabelMapMaskImageFilter_h
+#define __itkLabelMapMaskImageFilter_h
 
 #include "itkLabelMapFilter.h"
 #include "itkBarrier.h"
 
 namespace itk {
 
-/** \class LabelMapToMaskImageFilter
+/** \class LabelMapMaskImageFilter
  * \brief Mask and image with a LabelMap
  *
- * LabelMapToMaskImageFilter mask the content of an input image according
+ * LabelMapMaskImageFilter mask the content of an input image according
  * to the content of the input LabelMap. The masked pixel of the input image
  * are set to the BackgroundValue.
- * LabelMapToMaskImageFilter can keep the input image for one label only, with
+ * LabelMapMaskImageFilter can keep the input image for one label only, with
  * Negated = false (the default) or it can mask the input image for a single label, when
  * Negated equals true. In Both cases, the label is set with SetLabel(). 
  *
@@ -38,12 +38,12 @@ namespace itk {
  * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
  */
 template<class TInputImage, class TOutputImage>
-class ITK_EXPORT LabelMapToMaskImageFilter : 
+class ITK_EXPORT LabelMapMaskImageFilter : 
     public LabelMapFilter<TInputImage, TOutputImage>
 {
 public:
   /** Standard class typedefs. */
-  typedef LabelMapToMaskImageFilter Self;
+  typedef LabelMapMaskImageFilter Self;
   typedef LabelMapFilter<TInputImage, TOutputImage>
   Superclass;
   typedef SmartPointer<Self>        Pointer;
@@ -79,7 +79,7 @@ public:
   itkNewMacro(Self);  
 
[…]

### 2007-09-21 itkLabelMapToAttributeImageFilter.h

@@ -30,7 +30,7 @@ namespace itk {
  *
  * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
  *
- * \sa LabelMapToBinaryImageFilter, LabelMapToMaskImageFilter
+ * \sa LabelMapToBinaryImageFilter, LabelMapMaskImageFilter
  * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
  */
 template<class TInputImage, class TOutputImage, class TAttributeAccessor=

### 2007-09-21 itkLabelMapToBinaryImageFilter.h

@@ -32,7 +32,7 @@ namespace itk {
  *
  * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
  *
- * \sa LabelMapToLabelImageFilter, LabelMapToMaskImageFilter
+ * \sa LabelMapToLabelImageFilter, LabelMapMaskImageFilter
  * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
  */
 template<class TInputImage, class TOutputImage>

### 2007-09-21 itkLabelMapToLabelImageFilter.h

@@ -28,7 +28,7 @@ namespace itk {
  *
  * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
  *
- * \sa LabelMapToBinaryImageFilter, LabelMapToMaskImageFilter
+ * \sa LabelMapToBinaryImageFilter, LabelMapMaskImageFilter
  * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
  */
 template<class TInputImage, class TOutputImage>

### 2007-09-21 itkShapeLabelObject.h
better printing
darcs-hash:20070921092923-2fc9d-72f2b7f5e0af93def1f725c1ece4b28bbe5aa543.gz

@@ -655,7 +655,7 @@ protected:
     os << indent << "PhysicalSizeOnBorder: " << m_PhysicalSizeOnBorder << std::endl;
     os << indent << "FeretDiameter: " << m_FeretDiameter << std::endl;
     os << indent << "BinaryPrincipalMoments: " << m_BinaryPrincipalMoments << std::endl;
-    os << indent << "BinaryPrincipalAxes: " << m_BinaryPrincipalAxes << std::endl;
+    os << indent << "BinaryPrincipalAxes: " << std::endl << m_BinaryPrincipalAxes;
     os << indent << "BinaryElongation: " << m_BinaryElongation << std::endl;
     os << indent << "Perimeter: " << m_Perimeter << std::endl;
     os << indent << "Roundness: " << m_Roundness << std::endl;

### 2007-09-21 itkStatisticsLabelObject.h

@@ -743,9 +743,9 @@ protected:
     os << indent << "MaximumIndex: " << m_MaximumIndex << std::endl;
     os << indent << "MinimumIndex: " << m_MinimumIndex << std::endl;
     os << indent << "CenterOfGravity: " << m_CenterOfGravity << std::endl;
-    os << indent << "CentralMoments: " << m_CentralMoments << std::endl;
+    os << indent << "CentralMoments: " << std::endl << m_CentralMoments;
     os << indent << "PrincipalMoments: " << m_PrincipalMoments << std::endl;
-    os << indent << "PrincipalAxes: " << m_PrincipalAxes << std::endl;
+    os << indent << "PrincipalAxes: " << std::endl << m_PrincipalAxes;
     os << indent << "Skewness: " << m_Skewness << std::endl;
     os << indent << "Kurtosis: " << m_Kurtosis << std::endl;
     os << indent << "Elongation: " << m_Elongation << std::endl;

### 2007-09-21 itkStatisticsLabelObject.h
no more provide central moments
darcs-hash:20070921093623-2fc9d-8ef10ba770d827a97893c703a2ae596dc8d86358.gz

@@ -156,7 +156,7 @@ public:
 };
 
 
-template< class TLabelObject >
+/*template< class TLabelObject >
 class ITK_EXPORT CentralMomentsLabelObjectAccessor
 {
 public:
@@ -167,7 +167,7 @@ public:
     {
     return labelObject->GetCentralMoments();
     }
-};
+};*/
 
 template< class TLabelObject >
 class ITK_EXPORT PrincipalMomentsLabelObjectAccessor
@@ -294,7 +294,7 @@ public:
   static const AttributeType MAXIMUM_INDEX=107;
   static const AttributeType MINIMUM_INDEX=108;
   static const AttributeType CENTER_OF_GRAVITY=109;
-  static const AttributeType CENTRAL_MOMENTS=110;
+//  static const AttributeType CENTRAL_MOMENTS=110;
   static const AttributeType PRINCIPAL_MOMENTS=111;
   static const AttributeType PRINCIPAL_AXES=112;
   static const AttributeType KURTOSIS=113;
@@ -343,10 +343,10 @@ public:
       {
       return CENTER_OF_GRAVITY;
       }
-    else if( s == "CentralMoments" )
+/*    else if( s == "CentralMoments" )
       {
       return CENTRAL_MOMENTS;
-      }
+      }*/
     else if( s == "PrincipalMoments" )
       {
       return PRINCIPAL_MOMENTS;
@@ -405,9 +405,9 @@ public:
       case CENTER_OF_GRAVITY:
         return "CenterOfGravity";
         break;
-      case CENTRAL_MOMENTS:
+/*      case CENTRAL_MOMENTS:
         return "CentralMoments";
-        break;
+        break;*/
       case PRINCIPAL_MOMENTS:
         return "PrincipalMoments";
         break;
@@ -447,7 +447,7 @@ public:
     m_MaximumIndex = src->m_MaximumIndex;
     m_MinimumIndex = src->m_MinimumIndex;
     m_CenterOfGravity = src->m_CenterOfGravity;
-    m_CentralMoments = src->m_CentralMoments;
+//    m_CentralMoments = src->m_CentralMoments;
     m_PrincipalMoments = src->m_PrincipalMoments;
     m_PrincipalAxes = src->m_PrincipalAxes;
     m_Kurtosis = src->m_Kurtosis;
@@ -577,7 +577,7 @@ public:
 
 //   itkGetConstMacro( CentralMoments, MatrixType );
[…]

### 2007-09-24 article/Article.tex
fix type usage in python example
darcs-hash:20070921105546-2fc9d-49ae828b652d2952bf9d53c8e591d099f202522e.gz
update article
darcs-hash:20070924095227-2fc9d-4bf53cd90d05a78694941f7e0231533beb6ceafa.gz

@@
 Those new classes have been used to implement several label images
-manipulation based on object attributes, as well as the binary specialization of
-some mathematical morphology filter already included in ITK, and not related to
-the attribute of the objects. With those last filters, this contribution comes
-with 49 new classes, and should greatly enhance the binary mathematical
+manipulation based on object attributes, as well as the binary and label specialization of
+some mathematical morphology filters based on the morphological reconstruction. This contribution comes
+with 57 new classes, and should greatly enhance the binary mathematical
 morphology in ITK.
@@
 {\em Point< double >}.
-%   \item {\em CentralMoments}
-%   \item {\em PrincipalMoments}
-%   \item {\em PrincipalAxes}
   \item {\em Kurtosis} is the kurtosis of the pixel values in the objects. Its type is
@@
 shape or the position of the object.
-
-Finally, it has been chosen to develop a specific filter for the morphological
-reconstruction. It would have been possible to implement the reconstruction
-with the most common case (build the object collection, valuate the attributes
-filter the object, and rebuild the image), but in order to make it compatible
-with the {\em ShapeLabelObject} and {\em StatisticsLabelObject}, the reconstruction
-filter filters the collection directly, without setting an attribute in the objects
-\footnote{I'm not really pleased with that design though, and I'thinking about
-reimplementing it using the generic attributes. It would have no impact on the
-binary filters API.}.
 
@@
 The general view of the previous section show a very common way to use those
-classes. To make easier to use, some prebuilt classes have been made, to perform
+classes. To make them easier to use, some prebuilt classes have been made, to perform
 the mini-pipeline:
@@
 
+Also, when using the {\em itk::ShapeLabelObject} or the {\em itk::StatisticsLabelObject}
+class, we usually want them to be valuated. Some classes are provided to perform the
+mini-pipeline:
+\begin{itemize}
+  \item creation of the {\em itk::LabelMap} from an {\em
+itk::Image},
+  \item valuation of the attributes of the objects
+\end{itemize}
+with the {\em itk::ShapeLabelObject} or the {\em itk::StatisticsLabelObject}.
+
 Because the objects are often get from a label image or from a binary image,
@@
 \subsection{Binary filters}
+
+The filters to produce valuated attributes:
+
+\begin{itemize}
+  \item {\em itk::BinaryImageToShapeLabelMapFilter}
+  \item {\em itk::BinaryImageToStatisticsLabelMapFilter}
+\end{itemize}
+
+The filters to fully hide the usage of the label objects:
 
@@
 \subsection{Label filters}
+
+The filters to produce valuated attributes:
+
+\begin{itemize}
+  \item {\em itk::LabelImageToShapeLabelMapFilter}
+  \item {\em itk::LabelImageToStatisticsLabelMapFilter}
+\end{itemize}
+
+The filters to fully hide the usage of the label objects:
 
@@
 
-\section{Binary specialization of mathematical morphology filters}
+\section{Binary and label specialization of mathematical morphology filters}
+
+All the following filters are using a morphological reconstruction, implemented internally
+as an attribute opening with the {\em itk::AttributeLabelObject} class. Some binary filters
+are implemented:
 
@@
   \item {\em itk::BinaryReconstructionByErosionImageFilter}
+\end{itemize}
+
+and some label filters, useful when the label objects are connected, or when we
+want to avoid loosing the label by using a binary filter. Because the notion
+of reconstruction by erosion is difficult with labels, only a few filters
+are implemented:
+
+\begin{itemize}
+  \item {\em itk::LabelReconstructionByDilationImageFilter}
+%  \item {\em itk::LabelOpeningByReconstructionImageFilter}
 \end{itemize}
@@
 \small \begin{verbatim}
-maskSpots = itk.LabelMapMaskImageFilter.LI2IUC2.New(relabel, spots, Label=1,
+maskSpots = itk.LabelMapMaskImageFilter[LabelMapType, ImageType].New(relabel, spots, Label=1,
     Crop=True, CropBorder=2)

### 2007-09-24 article/Article.tex
minor corrections
darcs-hash:20070924101624-2fc9d-c9b5fca7687c82ce82841bee9f642f07a7fc9b80.gz

@@
 the computation of all the set of attributes much efficient. In the early stage of
-development, all the attributes were managed as in {\em AttributeLabelObject}, and
+development, all the attributes were managed as in {\em itk::AttributeLabelObject}, and
 a set of 8 classes made to manipulate a single attribute were provided, leading to a huge
@@
 constrained to be in the object, and thus can be outside if the object is not convex.
-Its type is {\em Point< double, ImageDimension >}. 
+Its type is {\em itk::Point< double, ImageDimension >}. 
   \item {\em Region} is the bounding box of the object given in the pixel coordinates.
 The physical coordinate can easily be computed from it. Its type is
-{\em ImageRegion< ImageDimension >}.
+{\em itk::ImageRegion< ImageDimension >}.
   \item {\em RegionElongation} is the ratio of the longest physical size of the region
@@
   \item {\em MinimumIndex} is the index position in the image where the first minimum was
-found. Its type is{\em Index< ImageDimension >}.
+found. Its type is{\em itk::Index< ImageDimension >}.
   \item {\em Maximum} is the maximum value in the feature image for the object. Its type is
@@
   \item {\em MaximumIndex} is the index position in the image where the first maximum was
-found. Its type is{\em Index< ImageDimension >}.
+found. Its type is{\em itk::Index< ImageDimension >}.
   \item {\em Mean} is the mean of the pixel values in the object. Its type is {\em double}.
@@
   \item {\em CenterOfGravity} is the center of gravity of the object. It type is
-{\em Point< double >}.
+{\em itk::Point< double >}.
   \item {\em Kurtosis} is the kurtosis of the pixel values in the objects. Its type is
@@
 
-The {\em AttributeLabelObject} let the user specify the type of the attribute
+The {\em itk::AttributeLabelObject} let the user specify the type of the attribute
 he wants to use, and thus is the good choice to implement a new attribute.
@@
 \end{verbatim} \normalsize
-then we can read the attribute values we're interested in. {\em BinaryImageToLabelMapFilter}
+then we can read the attribute values we're interested in. {\em itk::BinaryImageToLabelMapFilter}
 produces consecutives labels, so a simple {for} loop will do the job.
@@
 
-Lets begin with the usual {\em imports}.
+Lets begin with the usual {\em import}s.
 \small \begin{verbatim}
@@
 \small \begin{verbatim}
-otsu = itk.OtsuThresholdImageFilter[ImageType, ImageType].New(nuclei,
-    OutsideValue=255, InsideValue=0)
+otsu = itk.OtsuThresholdImageFilter[ImageType, ImageType].New(nuclei, OutsideValue=255,
+    InsideValue=0)
 \end{verbatim} \normalsize
@@
 \small \begin{verbatim}
-label = itk.LabelImageToLabelMapFilter[ImageType, LabelMapType]
-    .New(mask)
+label = itk.LabelImageToLabelMapFilter[ImageType, LabelMapType].New(mask)
 \end{verbatim} \normalsize
@@
 \small \begin{verbatim}
-stats = itk.StatisticsLabelMapFilter[LabelMapType, ImageType]
-    .New(label, nuclei)
+stats = itk.StatisticsLabelMapFilter[LabelMapType, ImageType].New(label, nuclei)
 \end{verbatim} \normalsize
@@
 \small \begin{verbatim}
-size = itk.ShapeOpeningLabelMapFilter[LabelMapType].New(stats,
-    Attribute='Size', Lambda=100)
-border = itk.ShapeOpeningLabelMapFilter[LabelMapType].New(size,
-    Attribute='SizeOnBorder', Lambda=10, ReverseOrdering=True)
+size = itk.ShapeOpeningLabelMapFilter[LabelMapType].New(stats,Attribute='Size',
+    Lambda=100)
+border = itk.ShapeOpeningLabelMapFilter[LabelMapType].New(size, Attribute='SizeOnBorder',
+    Lambda=10, ReverseOrdering=True)
 \end{verbatim} \normalsize
@@
 \small \begin{verbatim}
-relabel = itk.StatisticsRelabelLabelMapFilter[LabelMapType]
-    .New(border, Attribute='Mean')
+relabel = itk.StatisticsRelabelLabelMapFilter[LabelMapType].New(border, Attribute='Mean')
 \end{verbatim} \normalsize
@@
 \small \begin{verbatim}
-labelNuclei = itk.LabelMapToLabelImageFilter[LabelMapType,
-    ImageType].New(relabel)
+labelNuclei = itk.LabelMapToLabelImageFilter[LabelMapType, ImageType].New(relabel)
 overlay = itk.LabelOverlayImageFilter[ImageType, ImageType, RGBImageType].New(nuclei,
@@
 \small \begin{verbatim}
-slabel = itk.BinaryImageToLabelMapFilter[ImageType, LabelMapType]
-    .New(th)
-sstats = itk.StatisticsLabelMapFilter[LabelMapType, ImageType]
-    .New(slabel, nuclei)
+slabel = itk.BinaryImageToLabelMapFilter[ImageType, LabelMapType].New(th)
+sstats = itk.StatisticsLabelMapFilter[LabelMapType, ImageType].New(slabel, nuclei)
 \end{verbatim} \normalsize
@@
 \small \begin{verbatim}
-skeep = itk.ShapeKeepNObjectsLabelMapFilter[LabelMapType].New(
-    sstats, Attribute='Size', NumberOfObjects=4)
+skeep = itk.ShapeKeepNObjectsLabelMapFilter[LabelMapType].New(sstats, Attribute='Size',
+    NumberOfObjects=4)
 \end{verbatim} \normalsize
@@
 \small \begin{verbatim}
-srelabel = itk.StatisticsRelabelLabelMapFilter[LabelMapType].New(
-    skeep, Attribute='Size')
+srelabel = itk.StatisticsRelabelLabelMapFilter[LabelMapType].New(skeep, Attribute='Size')
 \end{verbatim} \normalsize
@@
 
-The {\em BinaryImageToLabelMapFilter} class is a slight modification of the
-Richard Beare's {\em ConnectedComponentImageFilter}, and thus, has not been threaded.
+The {\em itk::BinaryImageToLabelMapFilter} class is a slight modification of the
+Richard Beare's {\em itk::ConnectedComponentImageFilter}, and thus, has not been threaded.
 It should however be possible to increase its performance that way.
 
-The classical thread architecture is used when the input image is an {\em Image}: the image
+The classical thread architecture is used when the input image is an {\em itk::Image}: the image
 is splitted in several regions (one per thread), and each thread work on its own region.
 
-Because the {\em LabelMap} image is not an array of pixels, it can't be splitted
+Because the {\em itk::LabelMap} image is not an array of pixels, it can't be splitted
 that way. Instead, several threads are created, and try to take an object in the collection.
 If they get one, they process that object individually, and try to get another one when the
-object is processed. If no object can be get, the thread ends. A {\em FastMutexLock} is used
+object is processed. If no object can be get, the thread ends. A {\em itk::FastMutexLock} is used
 to ensure that only one thread take an object at a time.
@@
 For the developer, the usage of the threading support is made very simple, by subclassing
-{\em LabelMapFilter}, or {\em InPlaceLabelMapFilter}, and implementing
+{\em itk::LabelMapFilter}, or {\em itk::InPlaceLabelMapFilter}, and implementing
 the method {\em virtual void ThreadedGenerateData( LabelObjectType * labelObject )} in the
@@
 
-All the filters which are taking a {\em LabelMap} as input, and are producing a {\em LabelMap} as output, are implemented as a subclass of {\em InPlaceLabelMapFilter} and
+All the filters which are taking a {\em itk::LabelMap} as input, and are producing a {\em itk::LabelMap} as output, are implemented as a subclass of {\em InPlaceLabelMapFilter} and
 thus are running in place by default.
@@
 
-It may be useful to implement the most commonly used opening, keep N objects and relabel transforms in a more efficient way, by using an {\em AttributeLabelObject} instead of a {\em ShapeLabelObject} or a {\em StatisticsLabelObject}.
-
-The {\em BinaryImageToLabelMapFilter} class should be threaded to get the best of that filter on multiprocessors systems.
+It may be useful to implement the most commonly used opening, keep N objects and relabel transforms in a more efficient way, by using an {\em itk::AttributeLabelObject} instead of a {\em itk::ShapeLabelObject} or a {\em itk::StatisticsLabelObject}.
+
+The {\em itk::BinaryImageToLabelMapFilter} class should be threaded to get the best of that filter on multiprocessors systems.
 
@@
 
-Finally, all the binary and label filters should be implemented as a subclass of {\em InPlaceImageFilter}.
+Finally, all the binary and label filters should be implemented as a subclass of {\em itk::InPlaceImageFilter}.
 
@@
 \section{Acknowledgments}
-I thank Richard Beare for his suggestion to use the run length encoding to represent the binary objects, and Julien Jomier for his help for the choice to {\em not} use the {\em itk::SpatialObject} class as base class of the {\em itk::LabelObejct} class.
+I thank Richard Beare for his suggestion to use the run length encoding to represent the binary objects, and Julien Jomier for his help for the choice to {\em not} use the {\em itk::SpatialObject} class as base class of the {\em itk::LabelObject} class.
 

### 2007-10-01 article/Article.tex
fix wrong copy/papste
darcs-hash:20071001080634-2fc9d-b93493559e938f1e215dd110f314cc0f390de703.gz

@@
   opening->SetLambda( atof(argv[8]) );
-  keep->SetInPlace( false );
+  opening->SetInPlace( false );
 
@@
   relabel->SetInput( labelCollection );
-  keep->SetInPlace( false );
+  relabel->SetInPlace( false );
 \end{verbatim} \normalsize

### 2007-10-01 article/Article.tex
a few words about the LabelMapOvelayImageFilter and LabelMapToRGBImageFilter classes
darcs-hash:20071001085036-2fc9d-ea7bdff0c10daa257cee41b0f0787ac3066c87d0.gz

@@
 \subfigure[All the objects with perimeter smaller than 100 removed]{\includegraphics[scale=.7]{cthead1-label2-perimeter-greater-than-100}}
-\caption{Some example of opening with different attribute and parameters.}
+\caption{Some example of opening with different attribute and parameters.
+Note that the labels are kept unchanged in the output image.}
 \end{center}
@@
 , or the non-masked zone padded by a user defined number of pixels.
-  \item Finally, {\em itk::LabelMapToAttributeImageFilter} produce
+  \item The {\em itk::LabelMapToAttributeImageFilter} produce
 an {\em itk::Image} with the value of the attribute of the objects of the {\em
@@
 of the attribute values in the image.
+  \item The {\em LabelMapToRGBImageFilter} produce a color {\em itk::Image} with
+{\em itk::RGBPixel} as pixel type. The label objects are in color, as in
+Figure~\ref{fig:labelImage}. This class is mostly useful for a quick visual
+validation without going outside ITK.
+  \item Finally, the {\em LabelMapOvelayImageFilter} produce a color {\em itk::Image} with
+{\em itk::RGBPixel} as pixel type. The label objects are in color on top of a grayscale
+image, as in Figure~\ref{fig:nucleiOverlay}. This class is mostly useful for a quick visual
+validation without going outside ITK.
 \end{itemize}
@@
 \caption{The segmented nuclei. The too small objects and the ones on the border have been excluded.}
-\label{fig:overseg}
+\label{fig:nucleiOverlay}
 \end{center}

### 2007-10-08 article/Article.tex
remove wrong references to UseBackground
darcs-hash:20071008073850-2fc9d-45424469a1ff9c2bf724fca61662f1bb850cc80d.gz

@@
   relabel->SetBackgroundValue( atoi(argv[4]) );
-  relabel->SetUseBackground( atoi(argv[5]) );
   relabel->SetReverseOrdering( atoi(argv[6]) );
@@
   i2l->SetInput( reader->GetOutput() );
-  i2l->SetUseBackground( true );
 \end{verbatim} \normalsize

### 2007-10-08 article/Article.tex
a few words about the removed UseBackground feature
darcs-hash:20071008075908-2fc9d-a1bc1709f2acd93b2167f8bdc1293bb16b7c1ba4.gz

@@
 
-The {\em itk::LabelMap} class is in charge of managing the
-collection of label
+The {\em itk::LabelMap} class is in charge of managing the collection of label
 objects of the image, as well as storing the metadata associated with the image
-like
-the spacing, the physical position - all the metadata found in {\em itk::Image}.
+like the spacing, the physical position - all the metadata found in {\em
+itk::Image}. It has been chosen, to simplify the implementation and the tests,
+and because the feature is rarely useful in practice, to not implement the
+conditional background in the {\em itk::LabelMap} class\footnote{The classes
+before the {\em revision 4} were implemented with the conditional background
+feature. All the related code has been removed bitween revision 3 and revision
+4.}. All the images represented by a {\em itk::LabelMap} object have a
+background. If the user want to manipulate such an image with no background,
+he/she has to avoid the background label, for example by using a larger label
+type.
 

### 2007-10-17 itkShapeLabelObject.h
init centroid value
darcs-hash:20071017121921-2fc9d-1d61d01107c30908f12b4b7e369e25745a7760ed.gz

@@ -628,6 +628,7 @@ protected:
     {
     m_Size = 0;
     m_PhysicalSize = 0;
+    m_Centroid.Fill(0);
     m_RegionElongation = 0;
     m_SizeRegionRatio = 0;
     m_SizeOnBorder = false;

### 2007-10-17 itkChangeRegionLabelMapFilter.h
enhance docstrings
darcs-hash:20071017125532-2fc9d-739a6331044c83a22075eb27c76e7b47c674197b.gz

@@ -34,7 +34,7 @@ namespace itk
  *
  * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
  *
- * \sa LabelMapToBinaryImageFilter, LabelMapToLabelImageFilter
+ * \sa LabelMapMaskImageFilter
  * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
  */
 template <class TInputImage>
@@ -95,12 +95,8 @@ public:
 
   virtual void ThreadedGenerateData( LabelObjectType * labelObject );
   
-  /** LabelMapMaskImageFilter needs the entire input be
-   * available. Thus, it needs to provide an implementation of
-   * GenerateInputRequestedRegion(). */
   void GenerateInputRequestedRegion() ;
 
-  /** LabelMapMaskImageFilter will produce the entire output. */
   void EnlargeOutputRequestedRegion(DataObject *itkNotUsed(output));
 
   virtual void GenerateOutputInformation();

### 2007-10-17 itkCropLabelMapFilter.h

@@ -26,15 +26,19 @@ namespace itk
 {
   
 /** \class CropLabelMapFilter
- * \brief Set the region from a reference image
+ * \brief Crop a LabelMap image
  *
- * Change the region of a label map. If the output can't contain some lines of
+ * Crop a label map. If the output can't contain some lines of
  * the objects, they are truncated, or remove. All the objects fully outside the
  * output region are removed.
  *
+ * The SetCropSize() method can be used to set the crop size of the lower and
+ * the upper boundaries in a single call.
+ * By default, the filter doesn't crop anything.
+ *
  * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
  *
- * \sa LabelMapToBinaryImageFilter, LabelMapToLabelImageFilter
+ * \sa PadLabelMapFilter
  * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
  */
 template <class TInputImage>

### 2007-10-17 itkPadLabelMapFilter.h

@@ -26,15 +26,17 @@ namespace itk
 {
   
 /** \class PadLabelMapFilter
- * \brief Set the region from a reference image
+ * \brief Pad a LabelMap image
  *
- * Change the region of a label map. If the output can't contain some lines of
- * the objects, they are truncated, or remove. All the objects fully outside the
- * output region are removed.
+ * Pad a label map.
+ *
+ * The SetPadSize() method can be used to set the pad size of the lower and
+ * the upper boundaries in a single call.
+ * By default, the filter doesn't pad anything.
  *
  * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
  *
- * \sa LabelMapToBinaryImageFilter, LabelMapToLabelImageFilter
+ * \sa CropLabelMapFilter
  * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
  */
 template <class TInputImage>

### 2007-10-17 itkRegionFromReferenceLabelMapFilter.h

@@ -28,13 +28,14 @@ namespace itk
 /** \class RegionFromReferenceLabelMapFilter
  * \brief Set the region from a reference image
  *
- * Change the region of a label map. If the output can't contain some lines of
- * the objects, they are truncated, or remove. All the objects fully outside the
- * output region are removed.
+ * Change the region of a label map to be the same than the one of a reference image.
+ * This filter implement the same feature than its superclass, but with the input region
+ * well integrated in the pipeline architecture.
+ * If the output can't contain some lines of the objects, they are truncated, or remove.
+ * All the objects fully outside the output region are removed.
  *
  * \author Gaëtan Lehmann. Biologie du Développement et de la Reproduction, INRA de Jouy-en-Josas, France.
  *
- * \sa LabelMapToBinaryImageFilter, LabelMapToLabelImageFilter
  * \ingroup ImageEnhancement  MathematicalMorphologyImageFilters
  */
 template <class TInputImage>
@@ -85,10 +86,7 @@ public:
 
   typedef ImageBase< ImageDimension >    ReferenceImageType;
 
-  /** Copy the output information from another Image.  By default,
-   *  the information is specified with the SetOutputSpacing, Origin,
-   *  and Direction methods. UseReferenceImage must be On and a
-   *  Reference image must be present to override the defaul behavior.*/
+  /** Copy the output information from another Image. */
   void SetReferenceImage ( const ReferenceImageType *image )
     {
     itkDebugMacro("setting input ReferenceImage to " << image);
@@ -106,7 +104,7 @@ public:
      this->SetInput( input );
      }
 
-   /** Set the marker image */
+   /** Set the reference image */
   void SetInput2(const ReferenceImageType *input)
      {
      this->SetReferenceImage( input );

### 2007-10-17 article/Article.tex
fix number of new classes
darcs-hash:20071017121855-2fc9d-973d89bdf576c3c1e1ea580d14d673744eb89df7.gz
a few words about the new classes
darcs-hash:20071017130413-2fc9d-7937580424e1be5848eb56c083dfff058783c979.gz

@@
 some mathematical morphology filters based on the morphological reconstruction. This contribution comes
-with 57 new classes, and should greatly enhance the binary mathematical
+with 61 new classes, and should greatly enhance the binary mathematical
 morphology in ITK.
@@
 with the lowest attribute values in the first labels.
+
+  \item The region covered by the {\em itk::LabelMap} can be changed with
+{\em itk::ChangeRegionLabelMapFilter} and its subclasses ({\em itk::CropLabelMapFilter},
+{\em itk::PadLabelMapFilter} and {\em RegionFromReferenceLabelMapFilter}).
+
 \end{itemize}

### 2008-03-27 article/Article.tex
a few fixes for the next revision
darcs-hash:20080327100449-2fc9d-25b7c5252c4f251af1f41f02587d3872d9abd848.gz

--- 2007-10-08 article/Article.tex
@@
 Richard Beare has recently introduced a new filter to efficiently labelize the
-connected component with ITK, and has also proposed to use the run-length
-encoding used in that filter to implement some of the most useful binary
+connected components with ITK, and has also proposed to use the {\em run-length
+encoding} used in that filter to implement some of the most useful binary
 mathematical morphology operators: the opening by attribute.
@@
 some mathematical morphology filters based on the morphological reconstruction. This contribution comes
-with 57 new classes, and should greatly enhance the binary mathematical
+with 65 new classes, and should greatly enhance the binary mathematical
 morphology in ITK.
@@
 producing an image of the same size with a single pixel value per object. This
-image is called a label image. There are several way to create this image. It
+image is called a label image. There are several way to create such image. It
 can be done by searching the connected components in a binary image, it can be
@@
 a thresholding of a grayscale image, the objects too small or too beg to be of interest
-can be removed that way.
+can be removed that way. The class {\em AttributeSelectionLabelMapFilter} and its subclass
+{\em LabelSelectionLabelMapFilter} can be used to remove some objects based on their attribute
+value, even if the attribute type has no ordering property.
 
@@
 with the lowest attribute values in the first labels.
+
+  \item The region covered by the {\em itk::LabelMap} can be changed with
+{\em itk::ChangeRegionLabelMapFilter} and its subclasses ({\em itk::CropLabelMapFilter},
+{\em itk::PadLabelMapFilter}, {\em RegionFromReferenceLabelMapFilter} and {\em itk::AutoCropLabelMapFilter}).
+
 \end{itemize}

### 2008-03-27 itkLabelSelectionLabelMapFilter.h

@@ -88,7 +88,7 @@ public:
     return this->GetAttributeSet();
     }
     
-  void SetAttributeSet( const AttributeSetType & set )
+  void SetLabelSet( const AttributeSetType & set )
     {
     this->SetAttributeSet( set );
     }

### 2008-07-30 article/Article.tex
enhance the doc
darcs-hash:20080730153525-2fc9d-9059f6b64151af09695bbadbddb8aa3a08bcf670.gz

@@
 \small \begin{verbatim}
-  typedef itk::AttributeLabelObject< unsigned long, dim, double > LOType;
-  typedef itk::LabelMap< LOType > LCIType;
+  typedef itk::AttributeLabelObject< unsigned long, dim, double > LabelObjectType;
+  typedef itk::LabelMap< LabelObjectType > LabelMapType;
 \end{verbatim} \normalsize
@@
 \small \begin{verbatim}
-  typedef itk::LabelImageToLabelMapFilter< IType, LCIType > I2LType;
+  typedef itk::LabelImageToLabelMapFilter< IType, LabelMapType > I2LType;
   I2LType::Pointer i2l = I2LType::New();
@@
 \small \begin{verbatim}
-  LCIType::LabelObjectContainerType::const_iterator it;
-  LCIType::Pointer labelCollection = i2l->GetOutput();
-  const LCIType::LabelObjectContainerType & labelObjectContainer = labelCollection->GetLabelObjectContainer();
+  LabelMapType::LabelObjectContainerType::const_iterator it;
+  LabelMapType::Pointer labelMap = i2l->GetOutput();
+  const LabelMapType::LabelObjectContainerType & labelObjectContainer = labelMap->GetLabelObjectContainer();
 \end{verbatim} \normalsize
@@
     const PType & label = it->first;
-    LOType * labelObject = it->second;
+    LabelObjectType * labelObject = it->second;
 \end{verbatim} \normalsize
@@
 \small \begin{verbatim}
-    LOType::LineContainerType::const_iterator lit;
-    LOType::LineContainerType lineContainer = labelObject->GetLineContainer();
+    LabelObjectType::LineContainerType::const_iterator lit;
+    LabelObjectType::LineContainerType lineContainer = labelObject->GetLineContainer();
 
@@
       {
-      const LCIType::IndexType & firstIdx = lit->GetIndex();
+      const LabelMapType::IndexType & firstIdx = lit->GetIndex();
       const unsigned long & length = lit->GetLength();
@@
       long endIdx0 = firstIdx[0] + length;
-      for( LCIType::IndexType idx = firstIdx; idx[0]<endIdx0; idx[0]++)
+      for( LabelMapType::IndexType idx = firstIdx; idx[0]<endIdx0; idx[0]++)
         {
@@
 \small \begin{verbatim}
-  typedef itk::AttributeKeepNObjectsLabelMapFilter< LCIType > KeepType;
+  typedef itk::AttributeKeepNObjectsLabelMapFilter< LabelMapType > KeepType;
   KeepType::Pointer keep = KeepType::New();
-  keep->SetInput( labelCollection );
+  keep->SetInput( labelMap );
   keep->SetReverseOrdering( true );
@@
 
-  typedef itk::AttributeOpeningLabelMapFilter< LCIType > OpeningType;
+  typedef itk::AttributeOpeningLabelMapFilter< LabelMapType > OpeningType;
   OpeningType::Pointer opening = OpeningType::New();
-  opening->SetInput( labelCollection );
+  opening->SetInput( labelMap );
   opening->SetLambda( atof(argv[8]) );
@@
 
-  typedef itk::AttributeRelabelLabelMapFilter< LCIType > RelabelType;
+  typedef itk::AttributeRelabelLabelMapFilter< LabelMapType > RelabelType;
   RelabelType::Pointer relabel = RelabelType::New();
-  relabel->SetInput( labelCollection );
+  relabel->SetInput( labelMap );
   relabel->SetInPlace( false );
@@
 \small \begin{verbatim}
-  typedef itk::LabelMapToAttributeImageFilter< LCIType, IType > A2IType;
+  typedef itk::LabelMapToAttributeImageFilter< LabelMapType, IType > A2IType;
   A2IType::Pointer a2i = A2IType::New();
-  a2i->SetInput( labelCollection );
+  a2i->SetInput( labelMap );
 \end{verbatim} \normalsize
@@
 \small \begin{verbatim}
-  typedef itk::LabelMapToLabelImageFilter< LCIType, IType > L2IType;
+  typedef itk::LabelMapToLabelImageFilter< LabelMapType, IType > L2IType;
   L2IType::Pointer l2i = L2IType::New();
@@
   writer->Update();
+
+  return 0;
+}
+\end{verbatim} \normalsize
+
+\subsubsection{Custom attribute accessor}
+
+This example shows how to use the LabelMap classes to remove all the
+object with a bounding size smaller (or greater) than a given value
+on the z axis.
+The attribute we are interested is already computed by {\em ShapeLabelMapFilter}
+and stored in {\em ShapeLabelObject}. It is not usable as is however, because it
+is part of a multicomponent attribute: {\em Region}.
+
+To be able to use it with the standard classes, we have to provide an accessor
+which can be used by the opening filter.
+
+The source code is available in the file {\em simple\_generic\_attribute.cxx}.
+
+First include the classes we'll use
+\small \begin{verbatim}
+#include "itkImageFileReader.h"
+#include "itkImageFileWriter.h"
+#include "itkSimpleFilterWatcher.h"
+
+#include "itkLabelImageToShapeLabelMapFilter.h"
+#include "itkAttributeOpeningLabelMapFilter.h"
+#include "itkLabelMapToLabelImageFilter.h"
+\end{verbatim} \normalsize
+Now we can declare the custom accessor type, which will be used by the opening
+filter.
+\small \begin{verbatim}
+template< class TLabelObject >
+class ITK_EXPORT LastDimesionRegionSizeObjectAccessor
+{
+public:
+\end{verbatim} \normalsize
+The declaration of {\em AttributeValueType} is mandatory. It is used internally
+in the opening filter to define the type of the lambda value.
+{\em AttributeValueType} should be the same as the type returned by the operator()
+method.
+\small \begin{verbatim}
+  typedef unsigned long AttributeValueType;
+\end{verbatim} \normalsize
+{\em operator()} is the core of the accessor. It takes a label object as parameter,
+and return the attribute of interest. Some computations can be done inside the accessor
+method, but they should be as fast as possible, because {\em operator()} may be called
+many time by some filters. If an attribute value takes time to compute, it should rather be computed once
+for all and stored in a new attribute. In that case, there is no computation at all, only
+an access to a value hidden in a multicomponent attribute, so things are very fast.
+\small \begin{verbatim}
+  inline const AttributeValueType operator()( const TLabelObject * labelObject )
+    {
+    return labelObject->GetRegion().GetSize()[TLabelObject::ImageDimension-1];
+    }
+};
+\end{verbatim} \normalsize
+Now the main program. First the usual validation of the number of arguments.
+\small \begin{verbatim}
+int main(int argc, char * argv[])
+{
+
+  if( argc != 6 )
+    {
+    std::cerr << "usage: " << argv[0] << " input output bg lambda reverse" << std::endl;
+    // std::cerr << "  : " << std::endl;
+    exit(1);
+    }
+\end{verbatim} \normalsize
+Let's declare the dimension used, and the type of the input image
+\small \begin{verbatim}
+  const int dim = 3;
+  typedef unsigned char PType;
+  typedef itk::Image< PType, dim > IType;
+\end{verbatim} \normalsize
+We read the input image.
+\small \begin{verbatim}
+  typedef itk::ImageFileReader< IType > ReaderType;
+  ReaderType::Pointer reader = ReaderType::New();
+  reader->SetFileName( argv[1] );
+\end{verbatim} \normalsize
+And convert it to a {\em LabelMap}, with the shape attributes computed.
+We use the default label object type provided by {\em LabelImageToShapeLabelMapFilter}.
+\small \begin{verbatim}
+  typedef itk::LabelImageToShapeLabelMapFilter< IType > I2LType;
+  I2LType::Pointer i2l = I2LType::New();
+  i2l->SetInput( reader->GetOutput() );
+  i2l->SetBackgroundValue( atoi(argv[3]) );
+\end{verbatim} \normalsize
+The opening filter is declared with our custom accessor type as second
+template argument, so it will be able to user our custom attribute to make
+the opening.
+\small \begin{verbatim}
+  typedef LastDimesionRegionSizeObjectAccessor< I2LType::LabelObjectType > AccessorType;
+  typedef itk::AttributeOpeningLabelMapFilter< I2LType::OutputImageType, AccessorType > OpeningType;
+  OpeningType::Pointer opening = OpeningType::New();
+  opening->SetInput( i2l->GetOutput() );
+  opening->SetLambda( atof(argv[4]) );
+  opening->SetReverseOrdering( atof(argv[5]) );
+  itk::SimpleFilterWatcher watcher(opening, "filter");
+\end{verbatim} \normalsize
+The label map is then converted back to an label image.
+\small \begin{verbatim}
+  typedef itk::LabelMapToLabelImageFilter< I2LType::OutputImageType, IType > L2IType;
+  L2IType::Pointer l2i = L2IType::New();
+  l2i->SetInput( opening->GetOutput() );
+\end{verbatim} \normalsize
+Write the result to the disk.
+\small \begin{verbatim}
+  typedef itk::ImageFileWriter< IType > WriterType;
+  WriterType::Pointer writer = WriterType::New();
+  writer->SetInput( l2i->GetOutput() );
+  writer->SetFileName( argv[2] );
+  writer->Update();
+\end{verbatim} \normalsize
+Finally, print all the label objects after the opening, to check everything has been done right.
+\small \begin{verbatim}
+  opening->GetOutput()->PrintLabelObjects();
+  std::cout << "Number of objects after the opening: " << opening->GetOutput()->GetNumberOfLabelObjects() << std::endl;
 
@@
   typedef itk::ShapeLabelObject< LabelType, dim > LabelObjectType;
-  typedef itk::LabelMap< LabelObjectType > LabelCollectionType;
+  typedef itk::LabelMap< LabelObjectType > LabelMapType;
 
@@
 \small \begin{verbatim}
-  typedef itk::BinaryImageToLabelMapFilter< ImageType, LabelCollectionType > ConverterType;
+  typedef itk::BinaryImageToLabelMapFilter< ImageType, LabelMapType > ConverterType;
   ConverterType::Pointer converter = ConverterType::New();
@@
 \small \begin{verbatim}
-  typedef itk::ShapeLabelMapFilter< LabelCollectionType > ShapeFilterType;
+  typedef itk::ShapeLabelMapFilter< LabelMapType > ShapeFilterType;
   ShapeFilterType::Pointer shape = ShapeFilterType::New();
@@
 \small \begin{verbatim}
-  LabelCollectionType::Pointer collection = shape->GetOutput();
-  for( int label=1; label<collection->GetNumberOfLabelObjects(); label++ )
-    {
-    LabelObjectType::Pointer labelObject = collection->GetLabelObject( label );
+  LabelMapType::Pointer labelMap = converter->GetOutput();
+  for( unsigned int label=1; label<=labelMap->GetNumberOfLabelObjects(); label++ )
+    {
+    // we don't need a SmartPointer of the label object here, because the reference is kept in
+    // in the label map.
+    const LabelObjectType * labelObject = labelMap->GetLabelObject( label );
     std::cout << label << "\t" << labelObject->GetPhysicalSize() << "\t" << labelObject->GetCentroid() << std::endl;
@@
 Some of them however, are not (easily) threadable (the {\em KeepNObjects} and {\em Relabel}
-filters), are shouldn't get any performance improvement in a threaded version
+filters), or shouldn't get any performance improvement in a threaded version
 (the {\em Opening} filters).
@@
 The {\em itk::BinaryImageToLabelMapFilter} class is a slight modification of the
-Richard Beare's {\em itk::ConnectedComponentImageFilter}, and thus, has not been threaded.
-It should however be possible to increase its performance that way.
+Richard Beare's {\em itk::ConnectedComponentImageFilter}, and have also been threaded
+to get the best of the performances on a multicore system.
 
@@
 All the classes provided with that article, excepted the most generic ones made
-to help the developer to implement some new features, can be used with WrapITK,
+to help the developer to implement some new features, can be used with both stable and unstable WrapITK,
 and have been fully tested with python.

### 2008-07-31 itkStatisticsLabelObject.h
add the histogram as attribute
darcs-hash:20080731135648-2fc9d-32da3ddd642ae3ddce19d894d4242ffb92123e43.gz

@@ -18,6 +18,7 @@
 #define __itkStatisticsLabelObject_h
 
 #include "itkShapeLabelObject.h"
+#include "itkHistogram.h"
 
 namespace itk
 {
@@ -234,6 +235,19 @@ public:
     }
 };
 
+template< class TLabelObject >
+class ITK_EXPORT HistogramLabelObjectAccessor
+{
+public:
+  typedef TLabelObject LabelObjectType;
+  typedef typename LabelObjectType::HistogramType * AttributeValueType;
+
+  inline const AttributeValueType operator()( const LabelObjectType * labelObject )
+    {
+    return labelObject->GetHistogram();
+    }
+};
+
 }
 
 
@@ -283,6 +297,8 @@ public:
 
   typedef Vector< double, ImageDimension > VectorType;
 
+  typedef typename itk::Statistics::Histogram< double > HistogramType;
+
   typedef typename Superclass::AttributeType AttributeType;
   static const AttributeType MINIMUM=100;
   static const AttributeType MAXIMUM=101;
@@ -300,6 +316,7 @@ public:
   static const AttributeType KURTOSIS=113;
   static const AttributeType SKEWNESS=114;
   static const AttributeType ELONGATION=115;
+  static const AttributeType HISTOGRAM=116;
 
   static AttributeType GetAttributeFromName( const std::string & s )
     {
@@ -367,6 +384,10 @@ public:
       {
       return ELONGATION;
       }
+    else if( s == "Histogram" )
+      {
+      return HISTOGRAM;
+      }
     // can't recognize the namespace
     return Superclass::GetAttributeFromName( s );
     }
@@ -423,6 +444,9 @@ public:
       case ELONGATION:
         return "Elongation";
         break;
+      case HISTOGRAM:
+        return "Histogram";
+        break;
       }
       // can't recognize the namespace
       return Superclass::GetNameFromAttribute( a );
@@ -453,6 +477,7 @@ public:
     m_Kurtosis = src->m_Kurtosis;
     m_Skewness = src->m_Skewness;
     m_Elongation = src->m_Elongation;
+    m_Histogram = src->m_Histogram;
     }
 
 //   itkGetConstMacro( Minimum, double );
@@ -647,6 +672,18 @@ public:
     m_Elongation = v;
     }
 
+//   itkGetConstMacro( Histogram, double );
+//   itkSetMacro( Histogram, double );
[…]

### 2008-07-31 article/Article.tex
add a description for the new attributes
darcs-hash:20080731141228-2fc9d-4bb1959dcde9867b9c106b69c5a7bfff0de6456f.gz

@@
 of the largest principal moment by the smallest principal moment. Its value is greater
-or equal to $1$. Its type si {\em double}.
+or equal to $1$. Its type is {\em double}.
+  \item {\em EquivalentRadius} is the equivalent radius of the hypersphere of the same size
+than the label object. The value depends on the image spacing. Its type is {\em double}.
+  \item {\em EquivalentPerimeter} is the equivalent perimeter of the hypersphere of the same size
+than the label object. The value depends on the image spacing. Its type is {\em double}.
+  \item {\em EquivalentEllipsoidPerimeter} is the size of the ellipsoid of the same size
+and the same ratio on all the axes than the label object. The value depends on the image
+spacing. Its type is {\em itk::Vector< double, ImageDimension >}.
 %   \item {\em Perimeter}
@@
 or equal to $1$· Its type si {\em double}.
+  \item {\em Histogram} is the histogram of the pixels covered by the label object
+in the feature image. Its type is {\em itk::Histogram< double > *}.
 \end{itemize}

### 2008-08-04 article/Article.tex
fix computation of binary moments
darcs-hash:20080801131030-2fc9d-0fa0418b325eb53b2b771d477c6ba9b587275049.gz
fix the shamefully wrong equation and implement the most factorized formula for a bit much efficiency
darcs-hash:20080801133141-2fc9d-bf10214d99a93dc016bff59da14d0b7f5817cd5d.gz
enhance the doc a bit
darcs-hash:20080804104219-2fc9d-ea151a7d52f97f0072f55a9e1e8a539a3721ecb6.gz

@@
 
-The filter which are mainpulating binary images are often prefixed with the word
-"Binary", to differenciate the grayscale version which don't have a prefix. It
+The filters which are manipulating binary images are often prefixed with the word
+"Binary", to differenciate the grayscale versions which don't have a prefix. It
 seem to be a quite good practice which have been kept in that article.
@@
 
-The label images are often used the represent the connected components of an
+The label images are often used to represent the connected components of an
 image. In this contribution, another representation has been chosen.
@@
 
-The image is a collection of those objects, which also store some values of the image, like its size, its spacing, etc.
+The image is a collection of those objects, and it also store some values of the image,
+like its size, its spacing, etc.
 
@@
 
-No attribute are stored in this class, which can thus be seen as the base class
+No attribute -- excepted the label -- are stored in this class, which can thus be seen as the base class
 for the objects with attributes, or which can be used when no attributes
@@
 
-The {\em itk::LabelObject} class is templated and takes to required template parameters:
-\begin{itemize}
-  \item the type of the label,
+The {\em itk::LabelObject} class is templated and takes two required template parameters:
+\begin{itemize}
+  \item the type of the label;
   \item the dimension of the image.
@@
 shape of the label object. Computing the values of those attributes does not
-require a feaure image.
+require a feature image.
   \item {\em itk::StatisticsLabelObject} contains numerous statistics about the
@@
 created to reduce the number of filters made to manipulate the attributes, and to make
-the computation of all the set of attributes much efficient. In the early stage of
+the computation of all the set of attributes much efficient\footnote{In the early stage of
 development, all the attributes were managed as in {\em itk::AttributeLabelObject}, and
 a set of 8 classes made to manipulate a single attribute were provided, leading to a huge
-number of classes.
+number of classes.}.
 
@@
 
+The position in the images are given in index position when the position is the exact position
+of a pixel (for example, the position of the maximum value in the feature image) or in physical
+position when the position is given at a subpixel resolution (for example, the centroid). In
+both case, the position can easily be converted to the other representation with the 
+{\em itk::LabelMap::TransformPhysicalPointToIndex()} and {\em itk::LabelMap::TransformIndexToPhysicalPoint()}
+methods.
+
 Both {\em itk::ShapeLabelObject} and {\em itk::StatisticsLabelObject} are templated classes.
 They take the same template parameters than the {\em itk::LabelObject} class.
-The 2 first template parameters of the {\em itk::AttributeLabelObject} class or the same
-than the {\em itk::LabelObject} class. The third one is the attribute type.
+The two first template parameters of the {\em itk::AttributeLabelObject} class or the same
+than the ones of the{\em itk::LabelObject} class. The third one is the attribute type.
 
@@
 {\em double}
-  \item {\em CenterOfGravity} is the center of gravity of the object. It type is
+  \item {\em CenterOfGravity} is the center of gravity of the object. Its type is
 {\em itk::Point< double >}.
@@
 attributes of the {\em itk::ShapeLabelObject}s, 
-  \item and {\em itk::ShapeLabelMapFilter} to fill the attributes of the {\em
+  \item and {\em itk::StatisticsLabelMapFilter} to fill the attributes of the {\em
 itk::StatisticsLabelObject}s.
@@
 opening is often a very efficient way to enhance a segmentation. For example, after
-a thresholding of a grayscale image, the objects too small or too beg to be of interest
+a thresholding of a grayscale image, the objects too small or too big to be of interest
 can be removed that way. The class {\em AttributeSelectionLabelMapFilter} and its subclass
@@
 
-  \item The objects can be relabel, with the {\em
+  \item The objects can be relabeled, with the {\em
 RelabelLabelMapFilter} classes. The order of the label is dependant
@@
   \underset{L \in O}\sum \left( l_L.p_i.p_j \right)                & \text{if $i > 0$ and $j > 0$}, \\
-  \underset{L \in O}\sum \left( l_L.p_i.\underset{p \in L}\sum p_0 \right)  & \text{if $i > 0$ and $j = 0$}, \\
-  \underset{L \in O}\sum \left( l_L.p_j.\underset{p \in L}\sum p_0 \right)  & \text{if $i = 0$ and $j > 0$}, \\
+  \underset{L \in O}\sum \left( p_i.\underset{p \in L}\sum p_0 \right)  & \text{if $i > 0$ and $j = 0$}, \\
+  \underset{L \in O}\sum \left( p_j.\underset{p \in L}\sum p_0 \right)  & \text{if $i = 0$ and $j > 0$}, \\
   \underset{L \in O}\sum \underset{p \in L}\sum p_0^2            & \text{if $i = j = 0$}.
@@
 \sum_{p \in L} p_0^2  & = & \sum_{i_0=0}^{l_L-1} ( o_0 + s_0 i_0 )^2 \\ \nonumber
-                      & = & \sum_{i_0=0}^{l_L-1} ( o_0^2 + s_0^2 i_0^2 + 2 o_0 i_0) \\ \nonumber
-                      & = & l_L.o_0^2 + s_0^2\sum_{i_0=0}^{l_L-1} i_0^2 + 2 o_0 \sum_{i_0=0}^{l_L-1} i_0 \\ \nonumber
-                      & = & l_L.o_0^2 + s_0^2 \left( \frac{(l_L-1)l_L(2l_L-1)}{6} \right) + 2 o_0 \left( \frac{(l_L-1)l_L}{2} \right) \\ \nonumber
-                      & = & l_L\left( o_0^2 + (l_L-1)\left(\frac{s_0^2(2l_L-1)}{6}  + o_0 \right) \right)
+                      & = & \sum_{i_0=0}^{l_L-1} ( o_0^2 + s_0^2 i_0^2 + 2 o_0 s_0 i_0) \\ \nonumber
+                      & = & l_L.o_0^2 + s_0^2\sum_{i_0=0}^{l_L-1} i_0^2 + 2 o_0 s_0 \sum_{i_0=0}^{l_L-1} i_0 \\ \nonumber
+                      & = & l_L.o_0^2 + s_0^2 \left( \frac{(l_L-1)l_L(2l_L-1)}{6} \right) + 2 o_0 s_0 \left( \frac{(l_L-1)l_L}{2} \right) \\ \nonumber
+                      & = & l_L\left( o_0^2 + s_0 (l_L-1)\left(\frac{s_0(2l_L-1)}{6}  + o_0 \right) \right)
 \end{eqnarray}
@@
   \underset{L \in O}\sum \left( l_L.p_i.p_j \right)                & \text{if $i > 0$ and $j > 0$}, \\
-  \underset{L \in O}\sum \left( p_i.l_L^2 \left( o_0 + \frac{s_0(l_L-1)}{2} \right) \right) & \text{if $i > 0$ and $j = 0$}, \\
-  \underset{L \in O}\sum \left( p_j.l_L^2 \left( o_0 + \frac{s_0(l_L-1)}{2} \right) \right) & \text{if $i = 0$ and $j > 0$}, \\
-  \underset{L \in O}\sum \left( l_L\left( o_0^2 + (l_L-1)\left(\frac{s_0^2(2l_L-1)}{6}  + o_0 \right) \right) \right)            & \text{if $i = j = 0$}.
+  \underset{L \in O}\sum \left( p_i.l_L \left( o_0 + \frac{s_0(l_L-1)}{2} \right) \right) & \text{if $i > 0$ and $j = 0$}, \\
+  \underset{L \in O}\sum \left( p_j.l_L \left( o_0 + \frac{s_0(l_L-1)}{2} \right) \right) & \text{if $i = 0$ and $j > 0$}, \\
+  \underset{L \in O}\sum \left( l_L\left( o_0^2 + s_0 (l_L-1)\left(\frac{s_0(2l_L-1)}{6}  + o_0 \right) \right) \right)            & \text{if $i = j = 0$}.
            \end{cases}
@@
 then we can read the attribute values we're interested in. {\em itk::BinaryImageToLabelMapFilter}
-produces consecutives labels, so a simple {for} loop will do the job.
+produces consecutives labels, so a simple {\em for} loop will do the job.
 \small \begin{verbatim}
@@
 \end{verbatim} \normalsize
-Then declare the type we will use, as is {\em c++}.
+Then declare the type we will use, as in {\em C++}.
 \small \begin{verbatim}
@@
 \end{verbatim} \normalsize
-And now switch to the label collection representation
-\small \begin{verbatim}
-label = itk.LabelImageToLabelMapFilter[ImageType, LabelMapType].New(mask)
-\end{verbatim} \normalsize
-compute the attribute values
-\small \begin{verbatim}
-stats = itk.StatisticsLabelMapFilter[LabelMapType, ImageType].New(label, nuclei)
+And now switch to the label map representation, and compute the attribute values
+\small \begin{verbatim}
+stats = itk.LabelImageToStatisticsLabelMapFilter[ImageType, ImageType, LabelMapType].New(mask,
+    nuclei)
 \end{verbatim} \normalsize
@@
 \small \begin{verbatim}
-labelNuclei = itk.LabelMapToLabelImageFilter[LabelMapType, ImageType].New(relabel)
-overlay = itk.LabelOverlayImageFilter[ImageType, ImageType, RGBImageType].New(nuclei,
-    labelNuclei, UseBackground=True)
+overlay = itk.LabelMapOverlayImageFilter[LabelMapType, ImageType, RGBImageType].New(relabel,
+    nuclei)
 itk.write(overlay, "nuclei-overlay.png")
@@
 \end{verbatim} \normalsize
-Now swith to the label collection representation, and compute the attribute values. This time, the input image is not a label image, but a binary one.
-\small \begin{verbatim}
-slabel = itk.BinaryImageToLabelMapFilter[ImageType, LabelMapType].New(th)
-sstats = itk.StatisticsLabelMapFilter[LabelMapType, ImageType].New(slabel, nuclei)
-\end{verbatim} \normalsize
-we know there are for spots in the nubleus, so keep the 4 biggest spots. The other attribute are also usable - we may have chosen to keep the 4 brightest spots for example.
+Now swith to the label map representation, and compute the attribute values. This time, the input image is not a label image, but a binary one.
+\small \begin{verbatim}
+sstats = itk.BinaryImageToStatisticsLabelMapFilter[ImageType, ImageType, LabelMapType].New(th,
+    nuclei)
+\end{verbatim} \normalsize
+we know there are 4 spots in the nubleus, so keep the 4 biggest spots. The other attributes are also usable - we may have chosen to keep the 4 brightest spots for example.
 \small \begin{verbatim}
@@
 
-The {\em itk::BinaryImageToLabelMapFilter} class should be threaded to get the best of that filter on multiprocessors systems.
-
 The converters from/to image are provided, but it may be useful to  have the converters from/to other objects representations:

### 2008-08-04 example.py

@@ -23,18 +23,15 @@ otsu = itk.OtsuThresholdImageFilter[ImageType, ImageType].New(nuclei, OutsideVal
 maurer = itk.SignedMaurerDistanceMapImageFilter[ImageType, DistanceImageType].New(otsu)
 watershed = itk.MorphologicalWatershedImageFilter[DistanceImageType, ImageType].New(maurer, Level=60, MarkWatershedLine=False)
 mask = itk.MaskImageFilter[ImageType, ImageType, ImageType].New(watershed, otsu)
-# now switch to the label collection representation
-label = itk.LabelImageToLabelMapFilter[ImageType, LabelMapType].New(mask)
-# compute the attribute values, including the perimeter and the Feret diameter
-stats = itk.StatisticsLabelMapFilter[LabelMapType, ImageType].New(label, nuclei, ComputePerimeter=True, ComputeFeretDiameter=True)
+# now switch to the label map representation and compute the attribute values, including the perimeter and the Feret diameter
+stats = itk.LabelImageToStatisticsLabelMapFilter[ImageType, ImageType, LabelMapType].New(mask, nuclei)
 # drop the objects too small to be a nucleus, and the ones on the border
 size = itk.ShapeOpeningLabelMapFilter[LabelMapType].New(stats, Attribute='Size', Lambda=100)
 border = itk.ShapeOpeningLabelMapFilter[LabelMapType].New(size, Attribute='SizeOnBorder', Lambda=10, ReverseOrdering=True)
 # reoder the labels. The objects with the highest mean are the first ones.
 relabel = itk.StatisticsRelabelLabelMapFilter[LabelMapType].New(border, Attribute='Mean')
 # for visual validation
-labelNuclei = itk.LabelMapToLabelImageFilter[LabelMapType, ImageType].New(relabel)
-overlay = itk.LabelOverlayImageFilter[ImageType, ImageType, RGBImageType].New(nuclei, labelNuclei, UseBackground=True)
+overlay = itk.LabelMapOverlayImageFilter[LabelMapType, ImageType, RGBImageType].New(relabel, nuclei)
 itk.write(overlay, "nuclei-overlay.png")
 
 
@@ -42,9 +39,8 @@ spots = itk.ImageFileReader[ImageType].New(FileName="images/spots.png")
[…]

### 2009-07-01 article/Article.tex
add the contribution of a single pixel to the central moment computation as done by Dirk Padfield in http://insight-journal.com/download/viewpdf/301/4/download, but with taking spacing into account
Ignore-this: cfe8218dfdb1a0aeaa06dc05eedcd1bc

darcs-hash:20090701150858-2fc9d-47f310f489ed1b001fdc9b856b8efcb6f48d6d86.gz

@@
 
+A constant must be added when both elements of the second order moment are 
+the same. This constant represents the normalized second order central moment of a pixel. This is required 
+because the measurements are based on discrete pixels rather than continuous values. The normalized 
+second order central moment of a pixel with unit length of a binary image can be found as:
+
+$M_{000} = \int_{0}^{\delta_{x}}\int_{0}^{\delta_{y}}\int_{0}^{\delta_{z}}dzdydx = \delta_{x}\delta_{y}\delta_{z} = \Delta$
+
+$M_{100} = \int_{0}^{\delta{x}}\int_{0}^{\delta{y}}\int_{0}^{\delta{z}}x dzdydx = \delta_{y}\delta_{z}\left[\frac{x^2}{2}\right]_{0}^{\delta{x}} = \frac{\delta_{x}\Delta}{2}$
+
+$M_{110} = \int_{0}^{\delta{x}}\int_{0}^{\delta{y}}\int_{0}^{\delta{z}}xy dzdydx = \delta_{z}\left[\frac{x^2}{2}\right]_{0}^{\delta{x}}\left[\frac{y^2}{2}\right]_{0}^{\delta{y}} = \frac{\delta_{x}\delta_{y}\Delta}{4}$
+
+$M_{200} = \int_{0}^{\delta{x}}\int_{0}^{\delta{y}}\int_{0}^{\delta{z}}x^{2} dzdydx = \delta_{y}\delta_{z}\left[\frac{x^3}{3}\right]_{0}^{\delta{x}} = \frac{\delta_{x}^{2}\Delta}{3}$
+
+$\bar{x} = \frac{M_{100}}{M_{000}} = \frac{\frac{\delta_{x}\Delta}{2}}{\Delta} = \frac{\delta_{x}}{2}$
+$\bar{y} = \frac{M_{010}}{M_{000}} = \frac{\frac{\delta_{y}\Delta}{2}}{\Delta} = \frac{\delta_{y}}{2}$
+
+$\mu'_{110} = \frac{M_{110}}{M_{000}} - \bar{x}\bar{y} = \frac{\frac{\delta_{x}\delta_{y}\Delta}{4}}{\Delta} - \frac{\delta_{x}}{2}*\frac{\delta_{y}}{2} = \frac{\delta_{x}\delta_{y}}{4} - \frac{\delta_{x}\delta_{y}}{4} = 0$
+
+$\mu'_{200} = \frac{M_{200}}{M_{000}} - \bar{x}^{2} = \frac{\frac{\delta_{x}^{2}\Delta}{3}}{\Delta} - (\frac{\delta_{x}}{2})^{2} = \frac{\delta_{x}^{2}}{3} - \frac{\delta_{x}^{2}}{4} = \frac{\delta_{x}^{2}}{12}$
+
+Thus, the second order cross moment is 0, and the second order moment is 12 . A straightforward analysis 
+holds for other dimensions. This explains why it is necessary to add a scalar 1 
+12 to each normalized second 
+order central moment when the indices are the same dimension and it is not necessary to add anything for 
+normalized second order central moments consisting of cross moments.
+
 \subsection{Roundness}
